### 2015-01-01 paper/paper.tex
Outline of active resonator paper

\documentclass[11pt]{amsart}
\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
%\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
%\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{epstopdf}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}

\title{Working Title: Improving Dark Matter Axion Searches with Active Resonators}
\author{G. Rybka, A. Malagon, L. McBride, K. Patel}
\date{}                                           % Activate to display a given date or no date

%runnning list of figures we need in the paper:
%plot of snr vs Q for signal sent in on resonance; with and without delay line
%plot of snr vs Q for a measurement made one peak away from tallest peak
%plot of S_11 with and without delay line
%plot of snr vs Q for the new delay line in the transition region
% all of the above needs to be done with the new couplings as we changed the coupling coefficients
% after shipping the demo delay line back. Ask Lisa what those coupling coefficients are.
% perhaps change the coupling coefficients and see where the sweet spot is for snr improvement?
%

\begin{document}
\maketitle

\section{Introduction} %remove the sections later, just labeling them now for organizational purposes

\subsection{Axions, Dark Matter, and Microwave Cavities}

\subsection{Technological Limitations, Overcoming them with Active Resonators}

\section{Schematic}

PUT IN SCHEMATIC PLOT

\section{Theory}

\subsection{Derive multiplicative factor to gain}

\begin{align}
\text{three port S matrix}
\end{align}

\begin{align}
\text{multiplicative factor}
\end{align}

\subsection{Literature Review}

MENTION ARMSTRONG, MARK JONES
SHOULD WE MENTION DISAGREEMENT BETWEEN ISAKAWA and ITALIAN?

\section{SNR and Bandwidth}

\begin{align}
\text{SNR expression}
\end{align}

\begin{align}
\text{FIGURE OF MERIT, ACCOUNTING FOR REDUCTION IN BW}
\end{align}

\section{Measurements}

\subsection{Results}

\begin{figure}[htbp]
\centering
\includegraphics[width=\textwidth]{summary_plots}
\caption{}
\label{fig:summary_plots}
\end{figure}

\subsection{Comparison with Simulation}

\section{Discussion}

\section{Wild Speculation}

\section{Bibliography}

\end{document}

### 2015-01-02 paper/arxiv_withoutexp/submitted/2014_ouroboros.tex
copied over original text from arxiv paper

%% ****** Start of file apstemplate.tex ****** %
%%
%%
%%   This file is part of the APS files in the REVTeX 4 distribution.
%%   Version 4.1r of REVTeX, August 2010
%%
%%
%%   Copyright (c) 2001, 2009, 2010 The American Physical Society.
%%
%%   See the REVTeX 4 README file for restrictions and more information.
%%
%
% This is a template for producing manuscripts for use with REVTEX 4.0
% Copy this file to another name and then work on that file.
% That way, you always have this original template file to use.
%
% Group addresses by affiliation; use superscriptaddress for long
% author lists, or if there are many overlapping affiliations.
% For Phys. Rev. appearance, change preprint to twocolumn.
% Choose pra, prb, prc, prd, pre, prl, prstab, prstper, or rmp for journal
%  Add 'draft' option to mark overfull boxes with black boxes
%  Add 'showpacs' option to make PACS codes appear
%  Add 'showkeys' option to make keywords appear
%\documentclass[aps,prl,preprint,groupedaddress]{revtex4-1}
\documentclass[aps,prl,twocolumn,groupedaddress]{revtex4-1}
%\documentclass[aps,prl,preprint,superscriptaddress]{revtex4-1}
%\documentclass[aps,prl,reprint,groupedaddress]{revtex4-1}

% You should use BibTeX and apsrev.bst for references
% Choosing a journal automatically selects the correct APS
% BibTeX style file (bst file), so only uncomment the line
% below if necessary.
%\bibliographystyle{apsrev4-1}

\usepackage{graphicx}
\begin{document}

% Use the \preprint command to place your local institutional report
% number in the upper righthand corner of the title page in preprint mode.
% Multiple \preprint commands are allowed.
% Use the 'preprintnumbers' class option to override journal defaults
% to display numbers if necessary
%\preprint{}

%Title of paper
\title{Improving Dark Matter Axion Searches with Active Resonators}

% repeat the \author .. \affiliation  etc. as needed
% \email, \thanks, \homepage, \altaffiliation all apply to the current
% author. Explanatory text should go in the []'s, actual e-mail
% address or url should go in the {}'s for \email and \homepage.
% Please use the appropriate macro foreach each type of information

% \affiliation command applies to all authors since the last
% \affiliation command. The \affiliation command should follow the
% other information
% \affiliation can be followed by \email, \homepage, \thanks as well.
\author{Gray Rybka}
\email[]{grybka@uw.edu}
\affiliation{University of Washington}
%\homepage[]{Your web page}
%\thanks{}
%\altaffiliation{}

%Collaboration name if desired (requires use of superscriptaddress
%option in \documentclass). \noaffiliation is required (may also be
%used with the \author command).
%\collaboration can be followed by \email, \homepage, \thanks as well.
%\collaboration{}
%\noaffiliation

\date{\today}

\begin{abstract}
Axions are a well motivated candidate for dark matter.  The most sensitive experiments searching for dark matter axions rely on the coupling of axions to the electromagnetic resonances of a microwave cavity immersed in a strong magnetic field.  The sensitivity of the experiment is proportional to the $Q$ of the resonance that is coupled to axions.
To date, the resonators used in axion searches have all been passive, with $Q$s limited by power loss in the cavity walls.  I propose the use of active feedback resonators to increase the $Q$ of microwave cavity axion dark matter experiments by several orders of magnitude.
This should allow experiments to significantly increase the rate at which they can test potential axion masses and couplings.
\end{abstract}

% insert suggested PACS numbers in braces on next line
\pacs{}
% insert suggested keywords - APS authors don't need to do this
%\keywords{}

%\maketitle must follow title, authors, abstract, \pacs, and \keywords
\maketitle

% body of paper here - Use proper section commands
% References should be done using the \cite, \ref, and \label commands
The axion is a hypothetical particle that is both a candidate for dark matter and a result of the Peccei-Quinn solution to the strong CP problem~\cite{Peccei,Peccei_2,PhysRevLett.40.223,PhysRevLett.40.279,Preskill1983127,Abbott1983,ipser-sikivie}.
Axions with masses below $10^{-3}$ eV are particularly interesting because they could be produced in sufficient quantities to account for dark matter~\cite{Turner199067}.
For axions in this mass range the coupling between axions and photons, despite being exceptionally weak, provides the best chance of directly observing axion dark matter.

The most sensitive dark matter axion searches to date have been of the ``microwave cavity" type.
These experiments rely on the conversion of axions from the local dark matter halo into photons in a strong magnetic field.
This conversion is resonantly enhanced when the resonant frequency of the microwave cavity is equal to the frequency of the photons produced from the axion conversion~\cite{PhysRevLett.51.1415}.
Operation of these experiments involves slowly tuning the resonant frequency of the microwave cavity to explore different potential axion masses and searching for an excess of power deposited from dark matter axion conversion.
Microwave cavity experiments have been demonstrated to have the sensitivity required to detect optimistically coupled dark matter axions over a small mass range, but as of yet, axions have not been detected in a microwave cavity experiment~\cite{PhysRevLett.104.041301}.

The signal power in microwave cavity experiments is proportional to a number of factors, including the local density of dark matter, the strength of the magnetic field, the volume of the cavity, and the resonant quality factor $Q$ of the resonance being used.
The primary background is the thermal noise from the physical temperature of the cavity and the electronic noise from the first stage amplifier.  
The figure of merit for a microwave cavity experiment is the instantaneous axion signal to noise ratio (SNR).
Experiments with a larger SNR can be sensitive to more pessimistic axion photon couplings for a given frequency tuning speed or tune more quickly for a given axion photon coupling sensitivity.

Increasing the cavity $Q$ is one way to increase SNR in a microwave cavity experiment; the speed at which the cavity frequency can be tuned while remaining sensitive to a given axion photon coupling is linearly proportional to $Q$~\cite{Peng2000569}.
The presence of a strong magnetic field precludes the use of high-$Q$ superconducting cavities in these experiments, so the cavities are usually made of or coated with copper.
Loaded $Q$s of $10^5$ at 1 GHz have been achieved with copper cavities in axion experiments~\cite{Peng2000569}.  Higher frequency cavities typically have smaller $Q$s.

I present here a means of artificially increasing the $Q$ of the cavity resonance using active feedback in order to improve sensitivity to dark matter axions and increase the speed at which different axion masses can be tested.

\begin{figure}
\includegraphics[width=7cm]{experiment_schematic.eps}
\caption{\label{fig:experiment_schematic} Schematic of active feedback resonator for an axion experiment}
\end{figure}

\begin{figure}
\includegraphics[width=6cm]{equivalent_circuit.eps}
\caption{\label{fig:equiv_circuit} Equivalent circuit to axion photon conversion in microwave cavity with active regeneration}
\end{figure}

\begin{figure}
\includegraphics[width=6cm]{amplitude_definitions.eps}
\caption{\label{fig:amplitude_defs} Microwave cavity represented as three port device.}
\end{figure}

The use of active feedback resonators is a well established technique used in regenerative receivers~\cite{armstrong1914wireless}.
It involves connecting positive feedback to a resonator at the appropriate phase and amplification such that the power lost each oscillation to the output and damping effects is nearly completely replaced.  
This has the effect of increasing the $Q$ of the system.

A schematic of a microwave cavity axion experiment with active feedback is shown in Fig.~\ref{fig:experiment_schematic}.   Power from axion to photon conversion exits the cavity via a strongly coupled antenna, some of which is sent to a detector.  The remainder of the power is amplified, phase shifted, and then fed back into the cavity via a weakly coupled antenna.  A filter may also be needed to select the desired mode.

To calculate the effect of the active feedback, I will use the equivalent circuit to the cavity-amplifier system shown in Fig.~\ref{fig:equiv_circuit}.  The cavity resonant mode is equivalent to an $LRC$ circuit with an unloaded $Q$ of $Q_0$ and the coupled antennas are equivalent to transformers with couplings $Q_{e1}$ and $Q_{e2}~$\cite{Montgomery:1948}.  $G$ is the combined gain of the amplifier and power divider.  There is also a phase shift between the two antennas around the loop, which will be denoted as $\delta$.  The coupling between the electromagnetic resonance in the cavity and dark matter axions is equivalent to a third antenna with coupling $Q_{e3}$.  The passive loaded $Q$ of the resonator is $Q_L=\left(Q_0^{-1}+Q_{e1}^{-1}+Q_{e2}^{-1}+Q_{e3}^{-1}\right)^{-1}$.

I can now treat the cavity as a three port device using amplitudes defined in Fig.~\ref{fig:amplitude_defs} with an $S$ matrix of
\begin{equation}
S_{\mathrm{cavity}}=
\left( \begin{array}{ccc}
		\frac{2Q_L}{Q_{e1}}-1 & \frac{2Q_L}{\sqrt{Q_{e1}Q_{e2}}} & \frac{2Q_L}{\sqrt{Q_{e1}Q_{e3}}}  \\
		\frac{2Q_L}{\sqrt{Q_{e1}Q_{e2}}} & 1-\frac{2Q_L}{Q_{e2}} & \frac{2Q_L}{\sqrt{Q_{e2}Q_{e3}}}  \\
		\frac{2Q_L}{\sqrt{Q_{e1}Q_{e3}}} &  \frac{2Q_L}{\sqrt{Q_{e2}Q_{e3}}} &  1-\frac{2Q_L}{Q_{e3}} \\
		\end{array}\right)
\end{equation}
    assuming the resonant frequency of the cavity has been tuned to the axion frequency.

The output amplitude $b_1$ can be determined with the cavity $S$ matrix
\begin{equation}
\left(\begin{array}{c}
b_1\\
b_2\\
b_3\\
\end{array}\right)
=
S_{\mathrm{cavity}}\left(\begin{array}{c}
a_1\\
a_2\\
a_3\\
\end{array}\right),
\end{equation}
the effect of the amplifier and phase shifter
\begin{equation}
a_2=\sqrt{G}b_1e^{i\delta},
\end{equation}
and $a_1=0$.   I will take $\delta$ to have been chosen to be an integral multiple of $2\pi$.  This gives
\begin{equation}
b_1=\frac{2MQ_L}{\sqrt{Q_{e1}Q_{e3}}} a_3
\end{equation}
where I define $M$ to be the apparent multiplier to the $Q$ of the system
\begin{equation}
M=\left(1-2Q_L\sqrt{\frac{G}{Q_{e1}Q_{e2}}}\right)^{-1}.
\end{equation}
Note that for a passive resonator $M=1$ and that systems with $M<0$ will oscillate regardless of the presence of an axion signal.

I note that from the signal power derived in Refs.~\cite{Cavity_idea_2,PhysRevLett.80.2043},
\begin{equation}
\frac{|a_3^2|}{Q_{e3}}=\frac{1}{4}g_{a\gamma\gamma}^2VB_0^2\rho_aC\frac{1}{m_a}
\end{equation}
where $V$ is the volume of the microwave cavity, $B_0$ is the magnetic field strength, $\rho_a$ is the density of dark matter axions, $C$ is a mode dependent form factor of order 1, and $m_a$ is the axion mass.  
$g_{a\gamma\gamma}$ is the axion-photon coupling strength, defined as $g_{a\gamma\gamma}=\frac{\alpha g_\gamma}{\pi f_a}$ where $\alpha$ is the fine structure constant, $f_a$ is the axion decay constant and $g_\gamma$ is an order unity model dependent factor.

 The power measured at the output of the system is thus
\begin{equation}
\label{eqn:rawsig}
P_{\mathrm{signal}}=\frac{M^2Q_L^2}{Q_{e1}}g_{a\gamma\gamma}^2VB_0^2\rho_a\frac{1}{m_a}
\end{equation}

For a fixed $M$, this power is maximized when the first antenna is critically coupled so that $Q_{e1}=2Q_{L}$.  It is also important to note that for the isothermal halo model of dark matter axions,  the characteristic width of the axion signal is expected to correspond of a $Q$ of $10^6$ \cite{Cavity_idea}.   Experiments with a bandwidth smaller than the axion signal width sample only a subset of axions.  Thus the conservative estimate for signal power is

\begin{equation}
\label{eqn:sig}
P_{\mathrm{signal}}=\frac{M}{2}\min\left(MQ_L,10^6\right)g_{a\gamma\gamma}^2VB_0^2\rho_a\frac{1}{m_a},
\end{equation}

though it could be larger in models where the axion dark matter is unusually cold.

The thermal noise from the physical temperature of the cavity and electronic noise of the amplifier are also magnified by the active feedback.
The noise in an active feedback resonator, $T_n$ is minimized when
\begin{equation}
\frac{1}{Q_{e1}}=\frac{G}{Q_{e2}}
\end{equation} 
and has been calculated and measured in Ref.~\cite{noise_temp_afr} to be
\begin{equation}
T_n=\frac{MQ_L}{Q_{0}}T_{\mathrm{cav}}+\frac{G}{G-1}\frac{MQ_L}{Q_{0}}T_{\mathrm{amp}}
\end{equation}
where $T_{\mathrm{cav}}$ is the physical temperature of the cavity and $T_{\mathrm{amp}}$ is the noise temperature of the amplifier.   For a system with a gain $G\gg1$, a critically coupled antenna, and the conditions $Q_{e2},Q_{e3}\ll Q_{e1}$, this becomes
\begin{equation}
T_n\approx\frac{M}{2}\left(T_{\mathrm{cav}}+T_{\mathrm{amp}}\right).
\end{equation}

The noise bandwidth will be chosen to be the axion bandwidth for experiments with $MQ<10^6$, while experiments with higher $Q$ will use their full bandwidth.  This makes the noise power

\begin{equation}
\label{eqn:noise}
P_{\mathrm{noise}}=k_B\frac{M}{2}\left(T_{\mathrm{cav}}+T_{\mathrm{amp}}\right)\frac{f_0}{\max\left(MQ_L,10^6\right)}
\end{equation}

where $k_B$ is the Boltzmann constant and $f_0$ is the resonant frequency of the cavity.

Combining equations \ref{eqn:sig} and \ref{eqn:noise} the signal to noise of an active resonator microwave cavity experiment will be
\begin{equation}
\mathrm{SNR}=M Q_L\frac{g_{a\gamma\gamma}VB_0^2\rho_aC}{k_B f_0 m_a\left(T_{\mathrm{cav}}+T_{\mathrm{amp}}\right)}
\end{equation}

Thus, despite the magnification of the noise level, the SNR of the system is proportional to $MQ_L$.  The sensitivity and scan speed of a microwave cavity dark matter axion experiment will scale with $M$.

Values of $M$ have been reported as high as $10^4$ yielding $Q$s of $7\times10^7$ in active feedback resonators~\cite{:/content/aip/journal/rsi/84/8/10.1063/1.4817537} used for other purposes, but that were operated at frequencies that could be relevant to dark matter axion searches.
This would suggest existing experiments could increase their SNR by several orders of magnitude by implementing active feedback.

The ADMX experiment is within an order of magnitude of the sensitivity necessary to be sensitive to pessimistically coupled axion dark matter.  The addition of active feedback, along with other planned upgrades, should allow it to to be sensitive to pessimistically coupled axion dark matter even in models where axions constitute a very small fraction of the dark matter.  The use of active feedback will also allow future experiments to operate at higher frequencies, where previous microwave cavity experiments have not had the sensitivity necessary to detect axion dark matter with a reasonable scan speed.

This work was supported in part by the U.S. Department of Energy under contract DE-SC0009800.

% If you have acknowledgments, this puts in the proper section head.
%\begin{acknowledgments}
% put your acknowledgments here.
%\end{acknowledgments}

% Create the reference section using BibTeX:
\bibliography{2014_ouroboros}

\end{document}
%
% ****** End of file apstemplate.tex ******

### 2015-03-24 paper/paper.tex
Thermal Noise Analysis Reference

@@
-\documentclass[11pt]{amsart}
-\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
+\documentclass[aps,prl,twocolumn,groupedaddress]{revtex4-1}
+
+%\documentclass[11pt]{amsart}
+%\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
 %\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
@@
 \usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{epstopdf}
-\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}
+%\usepackage{amssymb}
+%\usepackage{epstopdf}
+%\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}
+\begin{document}
 
-\title{Working Title: Improving Dark Matter Axion Searches with Active Resonators}
-\author{G. Rybka, A. Malagon, L. McBride, K. Patel}
+\title{Improving Dark Matter Axion Searches with Active Resonators}
+\author{G. Rybka, A. Malagon, L. McBride, K. Patel, Jacob?}
+\email[]{grybka@uw.edu}
+\affiliation{University of Washington}
 \date{}                                           % Activate to display a given date or no date
@@
 
-\begin{document}
+\date{\today}
+
+%copied directly from Gray's original arxiv paper
+\begin{abstract}
+Axions are a well motivated candidate for dark matter.
+The most sensitive experiments searching for dark matter axions rely on the coupling of axions to the electromagnetic resonances of a microwave cavity immersed in a strong magnetic field.
+The sensitivity of the experiment is proportional to the $Q$ of the resonance that is coupled to axions.
+To date, the resonators used in axion searches have all been passive, with $Q$s limited by power loss in the cavity walls.
+I propose the use of active feedback resonators to increase the $Q$ of microwave cavity axion dark matter experiments by several orders of magnitude.
+This should allow experiments to significantly increase the rate at which they can test potential axion masses and couplings.
+%this is too bold a claim; realistically we can only get to 10^6 before signal power plateaus.
+\end{abstract}
+
+\pacs{}
+
 \maketitle
 
-\section{Introduction} %remove the sections later, just labeling them now for organizational purposes
+\section{Introduction} 
+%copied directly from Gray's original arxiv paper.
+
+The axion is a hypothetical particle that is both a candidate for dark matter and a result of the Peccei-Quinn solution to the strong CP problem~\cite{Peccei,Peccei_2,PhysRevLett.40.223,PhysRevLett.40.279,Preskill1983127,Abbott1983,ipser-sikivie}.
+Axions with masses below $10^{-3}$ eV are particularly interesting because they could be produced in sufficient quantities to account for 
+%cold
+dark matter~\cite{Turner199067}.
+For axions in this mass range the coupling between axions and photons
+%say two photon coupling?
+, despite being exceptionally weak, provides the best chance of directly observing axion dark matter.
+
+The most sensitive dark matter axion searches to date have been of the ``microwave cavity" type.
+%somehow the assumption that axions form all of the dark matter halo is lost...
+These experiments rely on the conversion of axions from the local dark matter halo into photons in a strong magnetic field.
+This conversion is resonantly enhanced when the resonant frequency of the microwave cavity is equal to the frequency of the photons produced from the axion conversion~\cite{PhysRevLett.51.1415}.
+%again, the missing information is that axions are non-relativistic, better way to say it is that the energy deposited into the electromagnetic field excites a resonant mode of the cavity.
+this might be a good time to bring in the energy dispersion.
+Operation of these experiments involves slowly tuning the resonant frequency of the microwave cavity to explore different potential axion masses and searching for an excess of power deposited from dark matter axion conversion.
+Microwave cavity experiments have been demonstrated to have the sensitivity required to detect optimistically coupled dark matter axions over a small mass range,
+%maybe say explicitly from 2-4 microeV
+but as of yet, axions have not been detected in a microwave cavity experiment~\cite{PhysRevLett.104.041301}.
+
+The signal power in microwave cavity experiments is proportional to a number of factors, including the local density of dark matter, the strength of the magnetic field, the volume of the cavity, and the resonant
+%loaded
+quality factor $Q$ of the resonance being used:
+%give equation
+\begin{align}
+P_{sig} = g_{a\gamma\gamma}^2B_{ext}^2VC\frac{\rho_a}{m_a}\text{max}(Q_{loaded},Q_a)
+\end{align}
+The primary background is the thermal noise from the physical temperature of the cavity and the electronic noise from the first stage amplifier.  
+The figure of merit for a microwave cavity experiment is the instantaneous axion signal to noise ratio (SNR).
+%why emphasize instanteneous?
+Experiments with a larger SNR can be sensitive to more pessimistic axion photon couplings for a given frequency tuning speed or tune more quickly for a given axion photon coupling sensitivity.
+
+Increasing the cavity $Q$ is one way to increase SNR in a microwave cavity experiment; the speed at which the cavity frequency can be tuned while remaining sensitive to a given axion photon coupling is linearly proportional to $Q$~\cite{Peng2000569}.
+The presence of a strong magnetic field precludes the use of high-$Q$ superconducting cavities in these experiments, so the cavities are usually made of or coated with copper.
+%add, ``...although R&D is being done with superconducting thing films on the walls...''
+Loaded $Q$s of $10^5$ at 1 GHz have been achieved with copper cavities in axion experiments~\cite{Peng2000569}.  Higher frequency cavities typically have smaller $Q$s.
+%mention anomalous skin depth limit, or scaling of Q with frequency as f^-2/3?
+%The quality factor for a passive resonator depends solely on the frequency, geometry, and material of the resonator.
+For a cylindrical copper cavity the Q scales as $Q \propto f^{-2/3}$....skin depth.
+
+I present here a means of artificially increasing the $Q$ of the cavity resonance using active feedback in order to improve sensitivity to dark matter axions and increase the speed at which different axion masses can be tested.
 
@@
 
-PUT IN SCHEMATIC PLOT
+\begin{figure}
+\includegraphics[width=7cm]{figs/experiment_schematic.eps}
+\caption{\label{fig:experiment_schematic} Schematic of active feedback resonator for an axion experiment}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=6cm]{figs/equivalent_circuit.eps}
+\caption{\label{fig:equiv_circuit} Equivalent circuit to axion photon conversion in microwave cavity with active regeneration}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=6cm]{figs/amplitude_definitions.eps}
+\caption{\label{fig:amplitude_defs} Microwave cavity represented as three port device.}
+\end{figure}
+
+The use of active feedback resonators is a well established technique used in regenerative receivers~\cite{armstrong1914wireless}.
+It involves connecting positive feedback to a resonator at the appropriate phase and amplification such that the power lost each oscillation to the output and damping effects is nearly completely replaced.
+This has the effect of increasing the $Q$ of the system.
+%perhaps say here that it will also amplify the noise of the system. However we show that the SNR improves square-rootishly with multiplier.
+A schematic of a microwave cavity axion experiment with active feedback is shown in Fig.~\ref{fig:experiment_schematic}.
+Power from axion to photon conversion exits the cavity via a strongly coupled antenna, some of which is sent to a detector.
+The remainder of the power is amplified, phase shifted, and then fed back into the cavity via a weakly coupled antenna.
+A filter may also be needed to select the desired mode.
 
@@
 \subsection{Derive multiplicative factor to gain}
+%We can derive the increase in Q and noise using an equivalent circuit model of the cavity and feedback system.
+%We represent the cavity as an RLC circuit, with impedance transformers representing the coupling ports from the cavity to the external system.
+%An amplifier with voltage gain $\sqrt{G_a}$ and equivalent noise temperature $T_a$ is placed in the feedback loop along with a phase shifter.
+%The closed loop gain of the system, assuming no loss in the phase shifter, is then $\sqrt{G_l} = S_{12}\sqrt{G}$. When 
+To calculate the effect of the active feedback, I will use the equivalent circuit to the cavity-amplifier system shown in Fig.~\ref{fig:equiv_circuit}.
+The cavity resonant mode is equivalent to an $LRC$ circuit with an unloaded $Q$ of $Q_0$ and the coupled antennas are equivalent to transformers with couplings $Q_{e1}$ and $Q_{e2}~$\cite{Montgomery:1948}.
+$G$ is the combined gain of the amplifier and power divider.
+There is also a phase shift between the two antennas around the loop, which will be denoted as $\delta$.
+The coupling between the electromagnetic resonance in the cavity and dark matter axions is equivalent to a third antenna with coupling $Q_{e3}$.
+The passive loaded $Q$ of the resonator is $Q_L=\left(Q_0^{-1}+Q_{e1}^{-1}+Q_{e2}^{-1}+Q_{e3}^{-1}\right)^{-1}$.
 
-\begin{align}
-\text{three port S matrix}
-\end{align}
+I can now treat the cavity as a three port device using amplitudes defined in Fig.~\ref{fig:amplitude_defs} with an $S$ matrix of
+\begin{equation}
+S_{\mathrm{cavity}}=
+\left( \begin{array}{ccc}
+		\frac{2Q_L}{Q_{e1}}-1 & \frac{2Q_L}{\sqrt{Q_{e1}Q_{e2}}} & \frac{2Q_L}{\sqrt{Q_{e1}Q_{e3}}}  \\
+		\frac{2Q_L}{\sqrt{Q_{e1}Q_{e2}}} & 1-\frac{2Q_L}{Q_{e2}} & \frac{2Q_L}{\sqrt{Q_{e2}Q_{e3}}}  \\
+		\frac{2Q_L}{\sqrt{Q_{e1}Q_{e3}}} &  \frac{2Q_L}{\sqrt{Q_{e2}Q_{e3}}} &  1-\frac{2Q_L}{Q_{e3}} \\
+		\end{array}\right)
+\end{equation}
+    assuming the resonant frequency of the cavity has been tuned to the axion frequency.
 
-\begin{align}
-\text{multiplicative factor}
-\end{align}
+The output amplitude $b_1$ can be determined with the cavity $S$ matrix
+\begin{equation}
+\left(\begin{array}{c}
+b_1\\
+b_2\\
+b_3\\
+\end{array}\right)
+=
+S_{\mathrm{cavity}}\left(\begin{array}{c}
+a_1\\
+a_2\\
+a_3\\
+\end{array}\right),
+\end{equation}
+the effect of the amplifier and phase shifter
+\begin{equation}
+a_2=\sqrt{G}b_1e^{i\delta},
+\end{equation}
+and $a_1=0$.   I will take $\delta$ to have been chosen to be an integral multiple of $2\pi$.  This gives
+\begin{equation}
+b_1=\frac{2MQ_L}{\sqrt{Q_{e1}Q_{e3}}} a_3
+\end{equation}
+where I define $M$ to be the apparent multiplier to the $Q$ of the system
+\begin{equation}
+M=\left(1-2Q_L\sqrt{\frac{G}{Q_{e1}Q_{e2}}}\right)^{-1}.
+\end{equation}
+Note that for a passive resonator $M=1$ and that systems with $M<0$ will oscillate regardless of the presence of an axion signal. 
+%should that be M>1?
+I note that from the signal power derived in Refs.~\cite{Cavity_idea_2,PhysRevLett.80.2043},
+\begin{equation}
+\frac{|a_3^2|}{Q_{e3}}=g_{a\gamma\gamma}^2VB_0^2\rho_aC\frac{1}{m_a}
+\end{equation}
+%remove this it doesn't make any sense to discuss amplitude of signal before entering the cavity.
+where $V$ is the volume of the microwave cavity, $B_0$ is the magnetic field strength, $\rho_a$ is the density of dark matter axions, $C$ is a mode dependent form factor of order 1, and $m_a$ is the axion mass.
+$g_{a\gamma\gamma}$ is the axion-photon coupling strength, defined as $g_{a\gamma\gamma}=\frac{\alpha g_\gamma}{\pi f_a}$ where $\alpha$ is the fine structure constant, $f_a$ is the axion decay constant and $g_\gamma$ is an order unity model dependent factor.
 
-\subsection{Literature Review}
+ The power measured at the output of the system is thus
+\begin{equation}
+\label{eqn:rawsig}
+P_{\mathrm{signal}}=\frac{M^2Q_L^2}{Q_{e1}}g_{a\gamma\gamma}^2VB_0^2\rho_aC\frac{1}{m_a}
+\end{equation}
+
+It is important to note that for the isothermal halo model of dark matter axions,  the characteristic width of the axion signal is expected to correspond of a $Q$ of $10^6$ \cite{Cavity_idea}.
+Experiments with a bandwidth smaller than the axion signal width sample only a subset of axions.
+Thus the conservative estimate for signal power is
+
+\begin{equation}
+\label{eqn:sig}
+P_{\mathrm{signal}}=\frac{M}{2}\min\left(MQ_L,10^6\right)g_{a\gamma\gamma}^2VB_0^2\rho_aC\frac{1}{m_a},
+\end{equation}
+
+though it could be larger in models where the axion dark matter is unusually cold.
+%I feel like this way of presenting it is misleading. It's implying we may very well have colder dark matter and could enhance our sensitivity,
+%but the reality is that we just don't know, so have to stick to the isothermal model.
+The thermal noise from the physical temperature of the cavity and electronic noise of the amplifier are also magnified by the active feedback.
+
+%\section{Theory copied from Ipython Notebook Writeup}
+%Referencing the image above, we use the following notation: $N_0$ is the cavity thermal noise power, $N_b$ is the amplifier noise power traveling away from the amplifier, and $N_a$ is the noise power traveling towards the amplifier (referenced to the input of the amplifier).
+I use lower case to denote the respective voltages, so $n_0$ is the cavity voltage noise, and $|n_0|^2 = N_0$, etc.
+$\sqrt{G}$ is the voltage gain of the amplifier, with the effective gain of the circuit is given by $\sqrt{G}S_{23}$.
+The relationship between the input amplitudes $a$ and output amplitudes $b$ is given by the S parameter matrix:
+%
+%$$
+%S = \left(\begin{array}{ccc}
+%-1 + 2Q_L/Q_{00} & 2 Q_L/\sqrt{Q_{00}Q_{1}} & 2Q_L/\sqrt{Q_{00} Q_2} \\
+%2 Q_L/\sqrt{Q_{00}Q_{1}} & -1 + 2Q_L/Q_{1} & 2Q_L/\sqrt{Q_{1} Q_2} \\
+%2 Q_L/\sqrt{Q_{00}Q_{2}} & 2Q_L/\sqrt{Q_{1} Q_2} & -1 + 2Q_L/Q_{2} \\
+%\end{array}\right)
+%$$
+%
+%(NOTE: there is a typo in the afr_noise paper by Ishikawa and co. - their $S_{13}$ entry is wrong.)
+%
+%My understanding of the notation here is that $Q_{00}$ is the unloaded Q of the cavity, $Q_L$ is the loaded Q of the cavity, $Q_1$ and $Q_2$ are quality factors parameterizing the coupling ports, and $Q_0$ is the active Q (unloaded).
+%
+%TODO: is the S parameter matrix In the language of coupling coefficients, $\beta_1 = \sqrt{\frac{Q_{00}}{Q_1}}$ and $\beta_2 = \sqrt{\frac{Q_{00}}{Q_2}}$.
+%
+%The relationship between the active Q and the other quality factors is given by:
+%
+%\begin{align}
+%\frac{1}{Q_0} = \frac{1}{Q_L} - 2\sqrt{\frac{G}{Q_1 Q_2}}.
+%\end{align}
+%
+%Physically, the above equation tells us that a loaded cavity quality factor will be further modified by the introduction of gain, which will act as a negative resistance. When 
+%
+%$$
+%\sqrt{G} = \frac{\sqrt{Q_1 Q_2}}{2 Q_L}
+%$$
+%
+%then the active quality factor goes to infinity, and the circuit becomes an oscillator. The equation above is the same as the condition that $S_{23}\sqrt{G} = 1$.
+%
+%Now that we've established our notation, we want to know what the output power would look like.
+If we take the output from port 1 ($b_1$) as the voltage we will be listening to, then $b_1$ has the form:
+%
+%$$
+%b_1(t)= S_{21} n_0 + S_{22} n_b + S_{23} \sqrt{G} \big(b_1(t- t_0) + n_a \big)
+%$$
+%
+%Note that we $b_1$ is evaluated at two different times in this equation - once at the current time $t$ but also at $t-t_0$, where $t_0 = L/c$ is the time it takes for a wave at port 1 to traverse the circuit's length $L$.
+%
+%The time-averaged power we expect then is:
+%
+%$$
+%<|b_1(t)|^2> + |S_{23}|^2 G <|b_1(t-t_0)|^2> - 2 S_{23} \sqrt{G} < b_1^*(t)b_1(t-t_0)> = |S_{21}|^2 N_0 + |S_{22}|^2 N_b + |S_{23}|^2 G N_a.
+%$$
+%
+%where we assumed that there is no correlation between the various noise sources, e.g. $<n_0 n_b> = 0$.
+%
+%Let us assume a steady state solution such that $<|b(t)|^2> = <|b(t-t_0)|^2>$. The autocorrelation of the two $b_1(t)$ terms is given by (NOTE: ask Gray again about how this was gotten):
+%
+%$$
+%<b_1^*(t)b_1(t-t_0)> = <|b_1(t)|^2> e^{-\omega t_0/Q}
+%$$
+%
+%I drop the subscript $1$ on $b(t)$ for simplicity and denote it by $b_{noise}$. We can rewrite the output power (CHECK: hopefully my transform to frequency space is not sketchy) as
+%
+%$$
+%<|b_{noise}(\omega)|^2> = \frac{|S_{21}|^2 N_0 + |S_{22}|^2 N_b + |S_{23}|^2 G N_a}{1 + |S_{23}|^2 G - 2S_{23}\sqrt{G}e^{-\omega t_0/Q}}.
+%$$
+%
+%Finally, we can parametrize any additional phase shift in the circuit by rewriting $\sqrt{G} \rightarrow \sqrt{G}e^{i\theta}$, so
+%
+%$$
+%<|b_{noise}(\omega)|^2> = \frac{|S_{21}|^2 N_0 + |S_{22}|^2 N_b + |S_{23}|^2 G N_a}{1 + |S_{23}|^2 G - 2S_{23}\sqrt{G}e^{-\omega t_0/Q - i\theta}}.
+%$$
+%
+%Note that we've derived the output noise power in the case of noise signal, but the output power when a signal is injected into the system (ie $a_0 = \sqrt{\beta_0} p$) would only be modified to be:
+%
+%$$
+%<|b_{signal}(\omega)|^2> =\frac{|S_{21}|^2 \beta_0 P}{1 + |S_{23}|^2 G - 2S_{23}\sqrt{G}e^{-\omega t_0/Q - i\theta}}
+%$$
+%
+%so the SNR would be:
+%
+%$$
+%SNR = \frac{<|b_{signal}(\omega)|^2>}{<|b_{noise}(\omega)|^2>} = \frac{|S_{21}|^2 \beta_0 P}{|S_{21}|^2 N_0 + |S_{22}|^2 N_b + |S_{23}|^2 G N_a}
+%$$
+%
+%... this doesn't make any sense. Not sure what I did wrong here.
+%
+%A different approach would be to recognize that the active Q ($Q_0$) gains by one factor of the multiplier:
+%
+%$$
+%Q_0 = Q_L(1 - \sqrt{G_l})^{-1}
+%$$
+%
+%where $G_l$ is the loop gain ($\sqrt{G_l} = S_{23}\sqrt{G}$).
+%
+%Then notice that the real gain, (not just through one pass), is given by
+%
+%$A = n_{cav} + A\sqrt{G_l}$ so $A = n_{cav}/(1-\sqrt{G_l})$.
+%
+%so if that's the voltage all around gain, then the power gain (all throughout) is $P = N_{cav}/(1-\sqrt{G_l})^2$.
+%
+%Therefore, for $t_0 = 0$,
+%
+%$$
+%SNR = \frac{P_{in} ( 1- \sqrt{G_l})^2}{(1-\sqrt{G_l})^2 (T_{cav} + G_l T_a)} = \frac{P_{in}}{(T_{cav} + G_l T_a)}
+%$$
+%
+%and for $t_0 = 2.5$ $\mu$seconds,
+%
+%$$
+%SNR = \frac{P_{in} ( 1 + G_l)}{(1-\sqrt{G_l})^2 (T_{cav} + G_l T_a)}
+%$$
+%
+%In any case, for typical experimental parameters, we can plot the noise vs Q for different delay times, which correspond to our measurement configurations with and without the delay line in.
+See below.
+
+\section{Literature Review}
 
@@
 \section{SNR and Bandwidth}
-
+The SNR is given by the ratio of the signal power to the fluctuations in the noise power.
+We assume that we measure the signal for time $\tau$ with a frequency resolution equal to the width of the axion signal, $B_a$:
 \begin{align}
-\text{SNR expression}
+SNR = \frac{P_{sig}}{\delta P_{noise}} = \frac{P_{sig}}{T_{noise}B_a}\sqrt{B_a \tau}
 \end{align}
@@
 \centering
-\includegraphics[width=\textwidth]{summary_plots}
+\includegraphics[width=\textwidth]{figs/summary_plots}
 \caption{}
@@
 \section{Discussion}
+Values of $M$ have been reported as high as $10^4$ yielding $Q$s of $7\times10^7$ in active feedback resonators~\cite{:/content/aip/journal/rsi/84/8/10.1063/1.4817537} used for other purposes, but that were operated at frequencies that could be relevant to dark matter axion searches.
+This would suggest existing experiments could increase their SNR by several orders of magnitude by implementing active feedback.
+
+The ADMX experiment is within an order of magnitude of the sensitivity necessary to be sensitive to pessimistically coupled axion dark matter.
+The addition of active feedback, along with other planned upgrades, should allow it to to be sensitive to pessimistically coupled axion dark matter even in models where axions constitute a very small fraction of the dark matter.
+The use of active feedback will also allow future experiments to operate at higher frequencies, where previous microwave cavity experiments have not had the sensitivity necessary to detect axion dark matter with a reasonable scan speed.
+
+This work was supported in part by the U.S. Department of Energy under contract DE-SC0009800.
 
@@
 
-\section{Bibliography}
+\bibliography{2014_ouroboros}
 

### 2015-03-30 paper/paper.tex
Wrote out expression for signal and noise power fully

@@
 \title{Improving Dark Matter Axion Searches with Active Resonators}
-\author{G. Rybka, A. Malagon, L. McBride, K. Patel, Jacob?}
+\author{G. Rybka, A. Malagon, L. McBride, K. Patel}
 \email[]{grybka@uw.edu}
@@
 \begin{align}
-P_{sig} = g_{a\gamma\gamma}^2B_{ext}^2VC\frac{\rho_a}{m_a}\text{max}(Q_{loaded},Q_a)
+P_{sig} = \eta g_{a\gamma\gamma}^2B_{ext}^2VC\frac{\rho_a}{m_a}\text{min}(Q_{loaded},Q_a)
 \end{align}
@@
 
-\subsection{Axions, Dark Matter, and Microwave Cavities}
-
-\subsection{Technological Limitations, Overcoming them with Active Resonators}
-
-\section{Schematic}
+\section{Theory of Method}
 
@@
 
-\section{Theory}
-
-\subsection{Derive multiplicative factor to gain}
 %We can derive the increase in Q and noise using an equivalent circuit model of the cavity and feedback system.
@@
 The cavity resonant mode is equivalent to an $LRC$ circuit with an unloaded $Q$ of $Q_0$ and the coupled antennas are equivalent to transformers with couplings $Q_{e1}$ and $Q_{e2}~$\cite{Montgomery:1948}.
+These external quality factors can be defined in terms of the unloaded Q and the coupling coefficients $\beta_1$ and $\beta_2$, which represent respectively the fraction of power lost out of port 1 or port 2 compared to the power lost to the walls: $Q_{e1} = Q_0/\beta_1$ and $Q_{e2} = Q_0/\beta_2$.
 $G$ is the combined gain of the amplifier and power divider.
@@
 
-I can now treat the cavity as a three port device using amplitudes defined in Fig.~\ref{fig:amplitude_defs} with an $S$ matrix of
+The cavity is fully characterized by the scattering matrix S and the noise amplitudes $c_1$ and $c_2$ radiated by the cavity into cold matched loads.
+Element $S_{21}$ is equal to the voltage amplification factor.
+
+Let us look at the amplitude of the wave at the output of port 2, assuming that all components are impedance matched and that isolators are placed at the ports to prevent reflected waves.
+If port 2 is critically coupled, then the noise wave at its output is equal to $c_2^2 =kT_{cav}B$, where B is the bandwidth of the detector.(G is the voltage gain of the amplifier and n_a the noise wave associated with it.)
+
+The time averaged noise power of the output is then
 \begin{equation}
-S_{\mathrm{cavity}}=
-\left( \begin{array}{ccc}
-		\frac{2Q_L}{Q_{e1}}-1 & \frac{2Q_L}{\sqrt{Q_{e1}Q_{e2}}} & \frac{2Q_L}{\sqrt{Q_{e1}Q_{e3}}}  \\
-		\frac{2Q_L}{\sqrt{Q_{e1}Q_{e2}}} & 1-\frac{2Q_L}{Q_{e2}} & \frac{2Q_L}{\sqrt{Q_{e2}Q_{e3}}}  \\
-		\frac{2Q_L}{\sqrt{Q_{e1}Q_{e3}}} &  \frac{2Q_L}{\sqrt{Q_{e2}Q_{e3}}} &  1-\frac{2Q_L}{Q_{e3}} \\
-		\end{array}\right)
+P_n = <|(c_2(t) + n_a(t)) + (c_2(t-t_1)+n_a(t-t_1))GS_{21} + (c_2(t-2t_1)+n_a(t-2t_1))G^2S_{21}^2 + \ldots|^2>
 \end{equation}
+The amplifier noise $n_a$ and the thermal noise from the cavity $c_2$ are independent, hence $<c_2n_a> = 0$, and also in the steady state $<c_2(t)>^2 = \bar{c_2}$ is independent of time, so
+
+\begin{equation}
+P_n = (\bar{c_2}^2 + \bar{n_a}^2)\frac{1}{1 - G^2|S_{21}|^2} + \text{cross-terms} \\
+\end{equation}
+where the cross-terms hold the information about the coherence of the noise between feedback rounds.
+Any signal entering the cavity undergoes exponential decay, so the expectation value of the cross terms goes as $<(c_2(t-nt_1)c_2(t-mt_1)> = \bar{c_2}^2e^(-(|n-m|)t_1/\tau)$, where $\tau = Q_L/\omega_0$ is the coherence time of the cavity.
+One can see that when the roundtrip time around the feedback loop is much larger than the coherence time, $t_1 \gg \tau$, the cross terms are exponentially suppressed and the feedback loop and amplifier enhance the original noise temperature of the cavity by a factor:
+\begin{equation}
+T_n = T_{cav}[1+\frac{T_a}{T_{cav}\frac{1}{1-G^2|S_{21}|^2}
+\end{equation}
+
+The analysis is slightly different for the signal power.
+We treat the axion-converted signal as a continuous source with amplitude $e_a$.
+Then the signal power observed at the output of port 2 (with the feedback loop is
+\begin{equation}
+P_s = <|e_a(t) + e_a(t-t_1)GS_{21} + e_a(t-2t_1)G^2S_{21}^2 + \ldots|^2>
+\end{equation}
+
+and as long as \omega t_1 is a multiple of $2\pi$, $e_a(t-nt_1) = e_a(t)$.
+
+Therefore the time averaged signal power is
+\begin{equation}
+P_s = \bar{e_a}^2\frac{1}{(1 - GS_{21})^2}
+\end{equation}
+
+This implies that the enhanced SNR from the feedback loop will be greater than the passive SNR, $SNR_0$, (assuming the same integration time and axion bandwidth) in the limit where the roundtrip time is much longer than the coherence time of the cavity,
+
+\begin{equation}
+SNR_{e}/SNR_{0} =\frac{(1-G^2|S_{21}|^2}{(1-GS_{21})^2} = 1 + \frac{2GS_{21}}{1-GS_{21}}
+\end{equation}
+In most cases we can achieve loaded Q's of only an order of magnitude below the axion linewidth, so we need a combined feedback of $GS_{21} = .8$ to improve the Q by an order of magnitude.
+
+When $t_1 \approx \tau$ we can no longer ignore the cross terms and end up with a noise power of
+
+\begin{equation}
+P_n = (\bar{c_2}^2 + \bar{n_a}^2)\frac{1}{1 - G^2|S_{21}|^2}\frac{1}{1-2e^{-t/\tau}GS_{21}}
+\end{equation}
+
+As well, the enhanced Q (again assuming a phase shift of $2\pi$), is given by \cite{ref:frenchpaper}
+\begin{equation}
+Q_e = Q_L\frac{1}{1-GS_{21}}
+\end{equation}
+you can see this by noting that the Q is a measure of how much a signal builds up; since the signal builds up by 
+$Q_{unloaded} = \omega U / P_{walls}$.
+Similarly
+$Q_{e1} = \omega U / P_{port1}$ and $Q_{e2} = \omega U / P_{port2}$.
+Therefore the loaded passive Q is $Q_L^{-1} = P_{total lost}/\omega U =  = Q_{e1}^{-1} + Q_{e2}^{-2} + Q_{unloaded}^{-1}$.
+Then with the feedback loop some power is regained, so 
+$Q_e^{-1} = 1/\omega U (P_{port1} + P_{port2} + P_{walls} - P_{feedback}) = Q_L
+%% I can now treat the cavity as a three port device using amplitudes defined in Fig.~\ref{fig:amplitude_defs} with an $S$ matrix of
+%% \begin{equation}
+%% S = \left( \begin{array}{ccc}
+%%   -1 + 2 \beta_1 (1 + \beta_1 + \beta_2)^{-1} & 2\sqrt{\beta_1\beta_2}(1 + \beta_1 + \beta_2)^{-1} \\
+%%   2\sqrt{\beta_1\beta_2}(1 + \beta_1 + \beta_2)^{-1} &   -1 + 2 \beta_2 (1 + \beta_1 + \beta_2)^{-1} \\
+%%   \end{array}\right)
+%% \end{equation}
+
+%% \begin{equation}
+%% S_{\mathrm{cavity}}=
+%% \left( \begin{array}{ccc}
+%% 		\frac{2Q_L}{Q_{e1}}-1 & \frac{2Q_L}{\sqrt{Q_{e1}Q_{e2}}} & \frac{2Q_L}{\sqrt{Q_{e1}Q_{e3}}}  \\
+%% 		\frac{2Q_L}{\sqrt{Q_{e1}Q_{e2}}} & 1-\frac{2Q_L}{Q_{e2}} & \frac{2Q_L}{\sqrt{Q_{e2}Q_{e3}}}  \\
+%% 		\frac{2Q_L}{\sqrt{Q_{e1}Q_{e3}}} &  \frac{2Q_L}{\sqrt{Q_{e2}Q_{e3}}} &  1-\frac{2Q_L}{Q_{e3}} \\
+%% 		\end{array}\right)
+%% \end{equation}
     assuming the resonant frequency of the cavity has been tuned to the axion frequency.
 
-The output amplitude $b_1$ can be determined with the cavity $S$ matrix
-\begin{equation}
-\left(\begin{array}{c}
-b_1\\
-b_2\\
-b_3\\
-\end{array}\right)
-=
-S_{\mathrm{cavity}}\left(\begin{array}{c}
-a_1\\
-a_2\\
-a_3\\
-\end{array}\right),
-\end{equation}
-the effect of the amplifier and phase shifter
-\begin{equation}
-a_2=\sqrt{G}b_1e^{i\delta},
-\end{equation}
-and $a_1=0$.   I will take $\delta$ to have been chosen to be an integral multiple of $2\pi$.  This gives
-\begin{equation}
-b_1=\frac{2MQ_L}{\sqrt{Q_{e1}Q_{e3}}} a_3
-\end{equation}
-where I define $M$ to be the apparent multiplier to the $Q$ of the system
-\begin{equation}
-M=\left(1-2Q_L\sqrt{\frac{G}{Q_{e1}Q_{e2}}}\right)^{-1}.
-\end{equation}
+%% The output amplitude $b_1$ can be determined with the cavity $S$ matrix
+%% \begin{equation}
+%% \left(\begin{array}{c}
+%% b_1\\
+%% b_2\\
+%% b_3\\
+%% \end{array}\right)
+%% =
+%% S_{\mathrm{cavity}}\left(\begin{array}{c}
+%% a_1\\
+%% a_2\\
+%% a_3\\
+%% \end{array}\right),
+%% \end{equation}
+%% the effect of the amplifier and phase shifter
+%% \begin{equation}
+%% a_2=\sqrt{G}b_1e^{i\delta},
+%% \end{equation}
+%% and $a_1=0$.   I will take $\delta$ to have been chosen to be an integral multiple of $2\pi$.  This gives
+%% \begin{equation}
+%% b_1=\frac{2MQ_L}{\sqrt{Q_{e1}Q_{e3}}} a_3
+%% \end{equation}
+%% where I define $M$ to be the apparent multiplier to the $Q$ of the system
+%% \begin{equation}
+%% M=\left(1-2Q_L\sqrt{\frac{G}{Q_{e1}Q_{e2}}}\right)^{-1}.
+%% \end{equation}
+
+so that the enhanced cavity Q has a maximum value of 
+$Q_e = \frac{Q_0}{1 + \beta_1 + \beta_2 - 2G\sqrt{\beta_1 \beta_2}}$
+
 Note that for a passive resonator $M=1$ and that systems with $M<0$ will oscillate regardless of the presence of an axion signal. 
@@
 %but the reality is that we just don't know, so have to stick to the isothermal model.
-The thermal noise from the physical temperature of the cavity and electronic noise of the amplifier are also magnified by the active feedback.
+%% The thermal noise from the physical temperature of the cavity and electronic noise of the amplifier are also magnified by the active feedback.
 
-%\section{Theory copied from Ipython Notebook Writeup}
-%Referencing the image above, we use the following notation: $N_0$ is the cavity thermal noise power, $N_b$ is the amplifier noise power traveling away from the amplifier, and $N_a$ is the noise power traveling towards the amplifier (referenced to the input of the amplifier).
-I use lower case to denote the respective voltages, so $n_0$ is the cavity voltage noise, and $|n_0|^2 = N_0$, etc.
-$\sqrt{G}$ is the voltage gain of the amplifier, with the effective gain of the circuit is given by $\sqrt{G}S_{23}$.
-The relationship between the input amplitudes $a$ and output amplitudes $b$ is given by the S parameter matrix:
-%
-%$$
-%S = \left(\begin{array}{ccc}
-%-1 + 2Q_L/Q_{00} & 2 Q_L/\sqrt{Q_{00}Q_{1}} & 2Q_L/\sqrt{Q_{00} Q_2} \\
-%2 Q_L/\sqrt{Q_{00}Q_{1}} & -1 + 2Q_L/Q_{1} & 2Q_L/\sqrt{Q_{1} Q_2} \\
-%2 Q_L/\sqrt{Q_{00}Q_{2}} & 2Q_L/\sqrt{Q_{1} Q_2} & -1 + 2Q_L/Q_{2} \\
-%\end{array}\right)
-%$$
-%
-%(NOTE: there is a typo in the afr_noise paper by Ishikawa and co. - their $S_{13}$ entry is wrong.)
-%
-%My understanding of the notation here is that $Q_{00}$ is the unloaded Q of the cavity, $Q_L$ is the loaded Q of the cavity, $Q_1$ and $Q_2$ are quality factors parameterizing the coupling ports, and $Q_0$ is the active Q (unloaded).
-%
-%TODO: is the S parameter matrix In the language of coupling coefficients, $\beta_1 = \sqrt{\frac{Q_{00}}{Q_1}}$ and $\beta_2 = \sqrt{\frac{Q_{00}}{Q_2}}$.
-%
-%The relationship between the active Q and the other quality factors is given by:
-%
-%\begin{align}
-%\frac{1}{Q_0} = \frac{1}{Q_L} - 2\sqrt{\frac{G}{Q_1 Q_2}}.
-%\end{align}
-%
-%Physically, the above equation tells us that a loaded cavity quality factor will be further modified by the introduction of gain, which will act as a negative resistance. When 
-%
-%$$
-%\sqrt{G} = \frac{\sqrt{Q_1 Q_2}}{2 Q_L}
-%$$
-%
-%then the active quality factor goes to infinity, and the circuit becomes an oscillator. The equation above is the same as the condition that $S_{23}\sqrt{G} = 1$.
-%
-%Now that we've established our notation, we want to know what the output power would look like.
-If we take the output from port 1 ($b_1$) as the voltage we will be listening to, then $b_1$ has the form:
-%
-%$$
-%b_1(t)= S_{21} n_0 + S_{22} n_b + S_{23} \sqrt{G} \big(b_1(t- t_0) + n_a \big)
-%$$
-%
-%Note that we $b_1$ is evaluated at two different times in this equation - once at the current time $t$ but also at $t-t_0$, where $t_0 = L/c$ is the time it takes for a wave at port 1 to traverse the circuit's length $L$.
-%
-%The time-averaged power we expect then is:
-%
-%$$
-%<|b_1(t)|^2> + |S_{23}|^2 G <|b_1(t-t_0)|^2> - 2 S_{23} \sqrt{G} < b_1^*(t)b_1(t-t_0)> = |S_{21}|^2 N_0 + |S_{22}|^2 N_b + |S_{23}|^2 G N_a.
-%$$
-%
-%where we assumed that there is no correlation between the various noise sources, e.g. $<n_0 n_b> = 0$.
-%
-%Let us assume a steady state solution such that $<|b(t)|^2> = <|b(t-t_0)|^2>$. The autocorrelation of the two $b_1(t)$ terms is given by (NOTE: ask Gray again about how this was gotten):
-%
-%$$
-%<b_1^*(t)b_1(t-t_0)> = <|b_1(t)|^2> e^{-\omega t_0/Q}
-%$$
-%
-%I drop the subscript $1$ on $b(t)$ for simplicity and denote it by $b_{noise}$. We can rewrite the output power (CHECK: hopefully my transform to frequency space is not sketchy) as
-%
-%$$
-%<|b_{noise}(\omega)|^2> = \frac{|S_{21}|^2 N_0 + |S_{22}|^2 N_b + |S_{23}|^2 G N_a}{1 + |S_{23}|^2 G - 2S_{23}\sqrt{G}e^{-\omega t_0/Q}}.
-%$$
-%
-%Finally, we can parametrize any additional phase shift in the circuit by rewriting $\sqrt{G} \rightarrow \sqrt{G}e^{i\theta}$, so
-%
-%$$
-%<|b_{noise}(\omega)|^2> = \frac{|S_{21}|^2 N_0 + |S_{22}|^2 N_b + |S_{23}|^2 G N_a}{1 + |S_{23}|^2 G - 2S_{23}\sqrt{G}e^{-\omega t_0/Q - i\theta}}.
-%$$
-%
-%Note that we've derived the output noise power in the case of noise signal, but the output power when a signal is injected into the system (ie $a_0 = \sqrt{\beta_0} p$) would only be modified to be:
-%
-%$$
-%<|b_{signal}(\omega)|^2> =\frac{|S_{21}|^2 \beta_0 P}{1 + |S_{23}|^2 G - 2S_{23}\sqrt{G}e^{-\omega t_0/Q - i\theta}}
-%$$
-%
-%so the SNR would be:
-%
-%$$
-%SNR = \frac{<|b_{signal}(\omega)|^2>}{<|b_{noise}(\omega)|^2>} = \frac{|S_{21}|^2 \beta_0 P}{|S_{21}|^2 N_0 + |S_{22}|^2 N_b + |S_{23}|^2 G N_a}
-%$$
-%
-%... this doesn't make any sense. Not sure what I did wrong here.
-%
+%% The effective noise temperature of the cavity plus feedback loop is given by
+
+%% \begin{equation}
+%% T_n = T_{cav} Q_e/Q_c (1+\beta_2 T_a/T_{cav}G^2Q_c/Q_0)
+%% \end{equation}
+
 %A different approach would be to recognize that the active Q ($Q_0$) gains by one factor of the multiplier:
@@
 
-\subsection{Comparison with Simulation}
-
 \section{Discussion}
@@
 
-\section{Wild Speculation}
-
 \bibliography{2014_ouroboros}

### 2015-03-30 paper/paper.tex
Wrote some thoughts in conclusion, brought out bib file from zip

@@
 %why emphasize instanteneous?
+The SNR is given by the ratio of the signal power to the fluctuations in the noise power.
+We assume that we measure the signal for time $\tau$ with a frequency resolution equal to the width of the axion signal, $B_a$:
+\begin{align}
+SNR = \frac{P_{sig}}{\delta P_{noise}} = \frac{P_{sig}}{T_{noise}B_a}\sqrt{B_a \tau}
+\end{align}
+
 Experiments with a larger SNR can be sensitive to more pessimistic axion photon couplings for a given frequency tuning speed or tune more quickly for a given axion photon coupling sensitivity.
@@
 
-This implies that the enhanced SNR from the feedback loop will be greater than the passive SNR, $SNR_0$, (assuming the same integration time and axion bandwidth) in the limit where the roundtrip time is much longer than the coherence time of the cavity,
+This implies that the enhanced SNR from the feedback loop will be greater than the passive SNR, $SNR_0$, (assuming the same integration time and axion bandwidth) in the limit where the roundtrip time is much longer than the coherence time of the cavity, (need to add extra factor because axion signal will additionally be enhanced by Q).
 
 \begin{equation}
-SNR_{e}/SNR_{0} =\frac{(1-G^2|S_{21}|^2}{(1-GS_{21})^2} = 1 + \frac{2GS_{21}}{1-GS_{21}}
+SNR_{e}/SNR_{0} =P_{s, enhanced}/P_{s,original}\frac{(1-G^2|S_{21}|^2}{(1-GS_{21})^2} = 1/(1-GS_{21})(1 + \frac{2GS_{21}}{1-GS_{21}}
 \end{equation}
@@
 \end{equation}
+
+One subtlety is that if there is only phase shifter for multiple frequencies within the feedback loop, one will not be able to hold the requirement that $\omega t = 2\pi$ when the roundtrip travel time $t$ is long; that is to say, interference fringes will begin to be observed within the bandwidth of the cavity when tis of the order $t \approx \pi Q_e / \omega_0$, so in order to avoid this effect, one would want a delay which longer than the coherence time of the cavity, but not too long so as to avoid deconstructive interference among frequencies slightly off resonance.
+Another solution would be to multiplex the signal and give each frequency a slightly different phase shift so that all the frequencies in the cavity bandwidth receive a 2$\pi$ phase shift around the loop.
 
@@
 Then with the feedback loop some power is regained, so 
-$Q_e^{-1} = 1/\omega U (P_{port1} + P_{port2} + P_{walls} - P_{feedback}) = Q_L
+$Q_e^{-1} = 1/\omega U (P_{port1} + P_{port2} + P_{walls} - P_{feedback}) = Q_L$
 %% I can now treat the cavity as a three port device using amplitudes defined in Fig.~\ref{fig:amplitude_defs} with an $S$ matrix of
@@
 %should that be M>1?
-I note that from the signal power derived in Refs.~\cite{Cavity_idea_2,PhysRevLett.80.2043},
-\begin{equation}
-\frac{|a_3^2|}{Q_{e3}}=g_{a\gamma\gamma}^2VB_0^2\rho_aC\frac{1}{m_a}
-\end{equation}
-%remove this it doesn't make any sense to discuss amplitude of signal before entering the cavity.
-where $V$ is the volume of the microwave cavity, $B_0$ is the magnetic field strength, $\rho_a$ is the density of dark matter axions, $C$ is a mode dependent form factor of order 1, and $m_a$ is the axion mass.
-$g_{a\gamma\gamma}$ is the axion-photon coupling strength, defined as $g_{a\gamma\gamma}=\frac{\alpha g_\gamma}{\pi f_a}$ where $\alpha$ is the fine structure constant, $f_a$ is the axion decay constant and $g_\gamma$ is an order unity model dependent factor.
+%% I note that from the signal power derived in Refs.~\cite{Cavity_idea_2,PhysRevLett.80.2043},
+%% \begin{equation}
+%% \frac{|a_3^2|}{Q_{e3}}=g_{a\gamma\gamma}^2VB_0^2\rho_aC\frac{1}{m_a}
+%% \end{equation}
+%% %remove this it doesn't make any sense to discuss amplitude of signal before entering the cavity.
+%% where $V$ is the volume of the microwave cavity, $B_0$ is the magnetic field strength, $\rho_a$ is the density of dark matter axions, $C$ is a mode dependent form factor of order 1, and $m_a$ is the axion mass.
+%% $g_{a\gamma\gamma}$ is the axion-photon coupling strength, defined as $g_{a\gamma\gamma}=\frac{\alpha g_\gamma}{\pi f_a}$ where $\alpha$ is the fine structure constant, $f_a$ is the axion decay constant and $g_\gamma$ is an order unity model dependent factor.
 
- The power measured at the output of the system is thus
-\begin{equation}
-\label{eqn:rawsig}
-P_{\mathrm{signal}}=\frac{M^2Q_L^2}{Q_{e1}}g_{a\gamma\gamma}^2VB_0^2\rho_aC\frac{1}{m_a}
-\end{equation}
+%%  The power measured at the output of the system is thus
+%% \begin{equation}
+%% \label{eqn:rawsig}
+%% P_{\mathrm{signal}}=\frac{M^2Q_L^2}{Q_{e1}}g_{a\gamma\gamma}^2VB_0^2\rho_aC\frac{1}{m_a}
+%% \end{equation}
 
@@
 
-\section{Literature Review}
+\section{Experimental Study}
+In order to experimentally confirm the results of the analysis presented above, a microwave cavity with feedback loop was built and tested, as illustrated in Figure x.
+The enhanced cavity Q was varied by varying the attenuation in the loop and the output spectrum measured on a spectrum analyzer.
+A test tone was injected into a third port to measure the signal to noise ratio for various values of the enhanced Q.
+The phase was adjusted to provide maximum power output.
 
-MENTION ARMSTRONG, MARK JONES
-SHOULD WE MENTION DISAGREEMENT BETWEEN ISAKAWA and ITALIAN?
+\begin{tabular}{|c|c|}
+\hline
+Parameters & Values \\ \hline
+$f_0$ & 2.256$\times 10^9$ Hz \\
+$Q_L$ & 1000 \\
+$Q_0$ & ? \\
+$\beta_1$ & ? \\
+$\beta_2$ & ? \\
+$T_{cav}$ & 300 K \\
+$T_{amp}$ & 300 K \\
+$G_a$ & ? dB \\
+Averaging Time & (what is 25 avgs in secs?) \\
+Time Delay & 2.4 $\mu$s \\
+Bandwidth & ? wrote it down on a napkin somewhere? \\
+\hline
+\end{tabular}
 
-\section{SNR and Bandwidth}
-The SNR is given by the ratio of the signal power to the fluctuations in the noise power.
-We assume that we measure the signal for time $\tau$ with a frequency resolution equal to the width of the axion signal, $B_a$:
-\begin{align}
-SNR = \frac{P_{sig}}{\delta P_{noise}} = \frac{P_{sig}}{T_{noise}B_a}\sqrt{B_a \tau}
-\end{align}
-
-\begin{align}
-\text{FIGURE OF MERIT, ACCOUNTING FOR REDUCTION IN BW}
-\end{align}
-
-\section{Measurements}
-
-\subsection{Results}
-
+As we injected a constant test tone and don't have a signal which scales with the enhanced Q, we expect only to observe an improvement in SNR of a factor of M.
+The experiment was made with and without a delay line whose delay of $2.4\mu$seconds was a factor of 100 greater than the coherence time of the cavity.
+The improvement in SNR vs.
+enhanced Q is shown in Figure xx, for the delay line in and for no delay line.
+The improvement scales as expected for both cases.
 \begin{figure}[htbp]
@@
 \section{Discussion}
-Values of $M$ have been reported as high as $10^4$ yielding $Q$s of $7\times10^7$ in active feedback resonators~\cite{:/content/aip/journal/rsi/84/8/10.1063/1.4817537} used for other purposes, but that were operated at frequencies that could be relevant to dark matter axion searches.
-This would suggest existing experiments could increase their SNR by several orders of magnitude by implementing active feedback.
+
+We see in this prototype that with a very low Q cavity one can enhance the Q by a factor of more than a thousand, and see a signal to noise improvement of a factor of 10.
+This is extremely encouraging as a proof of principle, and shows that one can get to Q's comparable with the axion linewidth with the simple techniqure of active feedback.
+This will increase the scan rate of microwave cavity experiments roughly by a factor of 3 and is simpler than research currently under way to improve the Q by making superconducting films on the walls of copper cavities.
+The active feedback technique becomes increasingly important for high-frequency axion experiments, as the passive limit for the Q scales as $f^{-1/3}$.
+
+Delay lines with time delays longer than a few microseconds are difficult to make with analog technology; at 1 GHz and Q's of 100,000, we would need a delay of ten microseconds.
+Digital delay lines using FPGAs would be the natural way to implement the necessary delays.
+
+%% Values of $M$ have been reported as high as $10^4$ yielding $Q$s of $7\times10^7$ in active feedback resonators~\cite{:/content/aip/journal/rsi/84/8/10.1063/1.4817537} used for other purposes, but that were operated at frequencies that could be relevant to dark matter axion searches.
+%% This would suggest existing experiments could increase their SNR by several orders of magnitude by implementing active feedback.
 
@@
 
-This work was supported in part by the U.S. Department of Energy under contract DE-SC0009800.
+This work was supported in part by the U.S. Department of Energy under contract DE-SC0009800. A.M. would like to thank Ben Brubaker for helpful discussions.
 

### 2015-04-04 paper/paper.tex
Added Gertsenshtein, Tetu, Brida to bib file, jotted down thoughts about gain instability
Noise_Curves notebook showing theoretical SNR enhancement

@@
 \documentclass[aps,prl,twocolumn,groupedaddress]{revtex4-1}
-
 %\documentclass[11pt]{amsart}
@@
 Let us look at the amplitude of the wave at the output of port 2, assuming that all components are impedance matched and that isolators are placed at the ports to prevent reflected waves.
-If port 2 is critically coupled, then the noise wave at its output is equal to $c_2^2 =kT_{cav}B$, where B is the bandwidth of the detector.(G is the voltage gain of the amplifier and n_a the noise wave associated with it.)
+If port 2 is critically coupled, then the noise wave at its output is equal to $c_2^2 =kT_{cav}B$, where B is the bandwidth of the detector.(G is the voltage gain of the amplifier and $n_a$ the noise wave associated with it.) We can add the noise of the cavity and the amplifier to get the system noise wave, $n(t) = c_2(t)+n_a(t)$.
 
@@
 \begin{equation}
-P_n = <|(c_2(t) + n_a(t)) + (c_2(t-t_1)+n_a(t-t_1))GS_{21} + (c_2(t-2t_1)+n_a(t-2t_1))G^2S_{21}^2 + \ldots|^2>
+P_n = \langle |n(t) + n(t-t_1)GS_{21} + (c_2(t-2t_1)+n_a(t-2t_1))G^2S_{21}^2 + \ldots|^2 \rangle
 \end{equation}
@@
 \begin{equation}
-P_n = (\bar{c_2}^2 + \bar{n_a}^2)\frac{1}{1 - G^2|S_{21}|^2} + \text{cross-terms} \\
+P_n = (\bar{c}_2^2 + \bar{n}_a^2)\frac{1}{1 - G^2|S_{21}|^2} + \text{cross-terms} \\
 \end{equation}
@@
 \begin{equation}
-T_n = T_{cav}[1+\frac{T_a}{T_{cav}\frac{1}{1-G^2|S_{21}|^2}
+T_n = T_{sys}\frac{1}{1-G^2|S_{21}|^2}
 \end{equation}
@@
 \begin{equation}
-P_s = <|e_a(t) + e_a(t-t_1)GS_{21} + e_a(t-2t_1)G^2S_{21}^2 + \ldots|^2>
+P_s = \langle |e_a(t) + e_a(t-t_1)GS_{21} + e_a(t-2t_1)G^2S_{21}^2 + \ldots|^2 \rangle
 \end{equation}
 
-and as long as \omega t_1 is a multiple of $2\pi$, $e_a(t-nt_1) = e_a(t)$.
+and as long as $\omega t_1$ is a multiple of $2\pi$, $e_a(t-nt_1) = e_a(t)$.
 
@@
 \begin{equation}
-P_s = \bar{e_a}^2\frac{1}{(1 - GS_{21})^2}
+P_s = \bar{e}_a^2\frac{1}{(1 - GS_{21})^2}
 \end{equation}
@@
 
-\begin{equation}
-SNR_{e}/SNR_{0} =P_{s, enhanced}/P_{s,original}\frac{(1-G^2|S_{21}|^2}{(1-GS_{21})^2} = 1/(1-GS_{21})(1 + \frac{2GS_{21}}{1-GS_{21}}
-\end{equation}
+\begin{align}
+\frac{SNR_{e}}{SNR_{0}} &=\frac{P_{s, enhanced}}{P_{s,original}}\frac{T_o}{T_e} = \frac{Q_e}{Q_o}\frac{1-G^2|S_{21}|^2}{(1-GS_{21})^2} 
+\\ &= \frac{1}{1-GS_{21}}\bigg(1 + \frac{2GS_{21}}{1-GS_{21}}\bigg)
+\end{align}
 In most cases we can achieve loaded Q's of only an order of magnitude below the axion linewidth, so we need a combined feedback of $GS_{21} = .8$ to improve the Q by an order of magnitude.
@@
 \begin{equation}
-P_n = (\bar{c_2}^2 + \bar{n_a}^2)\frac{1}{1 - G^2|S_{21}|^2}\frac{1}{1-2e^{-t/\tau}GS_{21}}
+P_n = (\bar{c}_2^2 + \bar{n}_a^2)\frac{1}{1 - G^2|S_{21}|^2}\frac{1}{1-2e^{-t/\tau}GS_{21}}
 \end{equation}
@@
 
+The SNR will plateau once we can no longer assume that the signal persists indefinitely - that is to say, when we include the $Q$ of the signal in our description of the signal power, we get that the
 As well, the enhanced Q (again assuming a phase shift of $2\pi$), is given by \cite{ref:frenchpaper}
@@
 This is extremely encouraging as a proof of principle, and shows that one can get to Q's comparable with the axion linewidth with the simple techniqure of active feedback.
+The main sources of systematic noise would come from gain instability in the circuit; in this experiment no noise additional to that expected was observed (or tested).
 This will increase the scan rate of microwave cavity experiments roughly by a factor of 3 and is simpler than research currently under way to improve the Q by making superconducting films on the walls of copper cavities.
@@
 
-\bibliography{2014_ouroboros}
+\bibliography{2015_ouroboros}
 

### 2015-04-16 ipython_notebooks/hello.tex

% PyX 0.12.1 texdebug file
% mode: tex
% date: Sat Apr 11 17:50:30 2015
\scrollmode
\raiseerror%
\def\PyX{P\kern-.3em\lower.5ex\hbox{Y}\kern-.18em X}%
\gdef\PyXBoxHAlign{0}%
\newbox\PyXBox%
\newbox\PyXBoxHAligned%
\newdimen\PyXDimenHAlignLT%
\newdimen\PyXDimenHAlignRT%
\gdef\PyXFlushHAlign{0}%
\def\PyXragged{%
\leftskip=0pt plus \PyXFlushHAlign fil%
\rightskip=0pt plus 1fil%
\advance\rightskip0pt plus -\PyXFlushHAlign fil%
\parfillskip=0pt%
\pretolerance=9999%
\tolerance=9999%
\parindent=0pt%
\hyphenpenalty=9999%
\exhyphenpenalty=9999}%
\newbox\PyXBoxVBox%
\newdimen\PyXDimenVBox%
\newbox\PyXBoxVAlign%
\newdimen\PyXDimenVAlign%
\newdimen\PyXDimenVShift%
\long\def\ProcessPyXBox#1#2{%
\setbox\PyXBox=\hbox{{#1}}%
\PyXDimenHAlignLT=\PyXBoxHAlign\wd\PyXBox%
\PyXDimenHAlignRT=\wd\PyXBox%
\advance\PyXDimenHAlignRT by -\PyXDimenHAlignLT%
\gdef\PyXBoxHAlign{0}%
\immediate\write16{PyXBox:page=#2,lt=\the\PyXDimenHAlignLT,rt=\the\PyXDimenHAlignRT,ht=\the\ht\PyXBox,dp=\the\dp\PyXBox:}%
\setbox\PyXBoxHAligned=\hbox{\kern-\PyXDimenHAlignLT\box\PyXBox}%
\ht\PyXBoxHAligned0pt%
{\count0=80\count1=121\count2=88\count3=#2\shipout\box\PyXBoxHAligned}}%
\def\PyXInput#1{\immediate\write16{PyXInputMarker:executeid=#1:}}%
\def\PyXMarker#1{\hskip0pt\special{PyX:marker #1}}%%
\PyXInput{1}%
% This automatically generated file is part of PyX (http://pyx.sourceforge.net/).
% \latexstylename="10pt"
% \latexclassname="article"
% \latexclassopt="10pt"
% \latexinit=""
\def\tiny{\font\pyxfont=cmr5\pyxfont\font\pyxfonttfa=cmr5\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr5\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi5\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi5\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy5\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy5\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\scriptsize{\font\pyxfont=cmr7\pyxfont\font\pyxfonttfa=cmr7\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr5\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi7\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi5\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy7\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy5\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\footnotesize{\font\pyxfont=cmr8\pyxfont\font\pyxfonttfa=cmr8\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr6\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi8\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi6\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy8\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy6\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\small{\font\pyxfont=cmr9\pyxfont\font\pyxfonttfa=cmr9\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr6\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi9\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi6\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy9\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy6\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\normalsize{\font\pyxfont=cmr10\pyxfont\font\pyxfonttfa=cmr10\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr7\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi10\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi7\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy7\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\large{\font\pyxfont=cmr12\pyxfont\font\pyxfonttfa=cmr12\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr8\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr6\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi8\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi6\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 12.0pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy8\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy6\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\Large{\font\pyxfont=cmr12 at 14.4pt\pyxfont\font\pyxfonttfa=cmr12 at 14.4pt\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr10\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr7\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12 at 14.4pt\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi10\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi7\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 14.4pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy10\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy7\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\LARGE{\font\pyxfont=cmr17\pyxfont\font\pyxfonttfa=cmr17\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr12\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr10\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12 at 17.28pt\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi12\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi10\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 17.28pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy10 at 12.0pt\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy10\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\huge{\font\pyxfont=cmr17 at 20.74pt\pyxfont\font\pyxfonttfa=cmr17 at 20.74pt\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr12 at 14.4pt\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr12\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12 at 20.74pt\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi12 at 14.4pt\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi12\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 20.74pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy10 at 14.4pt\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy10 at 12.0pt\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\Huge{\font\pyxfont=cmr17 at 24.88pt\pyxfont\font\pyxfonttfa=cmr17 at 24.88pt\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr17 at 20.74pt\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr17\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12 at 24.88pt\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi12 at 20.74pt\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi12 at 17.28pt\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 24.88pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy10 at 20.74pt\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy10 at 17.28pt\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
%
\PyXInput{2}%
\normalsize%
%
\PyXInput{3}%
\newdimen\linewidth\newdimen\textwidth%
%
\PyXInput{4}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{10^{-1}}}$}}\lower\PyXDimenVShift\box0%
}{1}%
\PyXInput{5}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{10^{0}}}$}}\lower\PyXDimenVShift\box0%
}{2}%
\PyXInput{6}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{10^{1}}}$}}\lower\PyXDimenVShift\box0%
}{3}%
\PyXInput{7}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{10^{2}}}$}}\lower\PyXDimenVShift\box0%
}{4}%
\PyXInput{8}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{5}%
\PyXInput{9}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{10^{4}}}$}}\lower\PyXDimenVShift\box0%
}{6}%
\PyXInput{10}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}axion SNR enhancement}}\lower\PyXDimenVShift\box0%
}{7}%
\PyXInput{11}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{0}$}}\lower\PyXDimenVShift\box0%
}{8}%
\PyXInput{12}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{0.25}$}}\lower\PyXDimenVShift\box0%
}{9}%
\PyXInput{13}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{0.5}$}}\lower\PyXDimenVShift\box0%
}{10}%
\PyXInput{14}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{0.75}$}}\lower\PyXDimenVShift\box0%
}{11}%
\PyXInput{15}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{1}$}}\lower\PyXDimenVShift\box0%
}{12}%
\PyXInput{16}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}closed loop gain, $t_{cav} \ll t_a$}}\lower\PyXDimenVShift\box0%
}{13}%
\PyXInput{17}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{0}$}}\lower\PyXDimenVShift\box0%
}{14}%
\PyXInput{18}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{0.2}$}}\lower\PyXDimenVShift\box0%
}{15}%
\PyXInput{19}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{0.4}$}}\lower\PyXDimenVShift\box0%
}{16}%
\PyXInput{20}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{0.6}$}}\lower\PyXDimenVShift\box0%
}{17}%
\PyXInput{21}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{0.8}$}}\lower\PyXDimenVShift\box0%
}{18}%
\PyXInput{22}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{1}$}}\lower\PyXDimenVShift\box0%
}{19}%
\PyXInput{23}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}closed loop gain, $t_{cav} \ll t_a$}}\lower\PyXDimenVShift\box0%
}{20}%
\PyXInput{24}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{delay}}\lower\PyXDimenVShift\box0%
}{21}%
\PyXInput{25}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{no delay}}\lower\PyXDimenVShift\box0%
}{22}%
\PyXInput{26}%
\end%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% preparing restart of tex
% PyX 0.12.1 texdebug file
% mode: tex
% date: Sat Apr 11 17:53:19 2015
\scrollmode
\raiseerror%
\def\PyX{P\kern-.3em\lower.5ex\hbox{Y}\kern-.18em X}%
\gdef\PyXBoxHAlign{0}%
\newbox\PyXBox%
\newbox\PyXBoxHAligned%
\newdimen\PyXDimenHAlignLT%
\newdimen\PyXDimenHAlignRT%
\gdef\PyXFlushHAlign{0}%
\def\PyXragged{%
\leftskip=0pt plus \PyXFlushHAlign fil%
\rightskip=0pt plus 1fil%
\advance\rightskip0pt plus -\PyXFlushHAlign fil%
\parfillskip=0pt%
\pretolerance=9999%
\tolerance=9999%
\parindent=0pt%
\hyphenpenalty=9999%
\exhyphenpenalty=9999}%
\newbox\PyXBoxVBox%
\newdimen\PyXDimenVBox%
\newbox\PyXBoxVAlign%
\newdimen\PyXDimenVAlign%
\newdimen\PyXDimenVShift%
\long\def\ProcessPyXBox#1#2{%
\setbox\PyXBox=\hbox{{#1}}%
\PyXDimenHAlignLT=\PyXBoxHAlign\wd\PyXBox%
\PyXDimenHAlignRT=\wd\PyXBox%
\advance\PyXDimenHAlignRT by -\PyXDimenHAlignLT%
\gdef\PyXBoxHAlign{0}%
\immediate\write16{PyXBox:page=#2,lt=\the\PyXDimenHAlignLT,rt=\the\PyXDimenHAlignRT,ht=\the\ht\PyXBox,dp=\the\dp\PyXBox:}%
\setbox\PyXBoxHAligned=\hbox{\kern-\PyXDimenHAlignLT\box\PyXBox}%
\ht\PyXBoxHAligned0pt%
{\count0=80\count1=121\count2=88\count3=#2\shipout\box\PyXBoxHAligned}}%
\def\PyXInput#1{\immediate\write16{PyXInputMarker:executeid=#1:}}%
\def\PyXMarker#1{\hskip0pt\special{PyX:marker #1}}%%
\PyXInput{1}%
% This automatically generated file is part of PyX (http://pyx.sourceforge.net/).
% \latexstylename="10pt"
% \latexclassname="article"
% \latexclassopt="10pt"
% \latexinit=""
\def\tiny{\font\pyxfont=cmr5\pyxfont\font\pyxfonttfa=cmr5\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr5\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi5\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi5\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy5\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy5\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\scriptsize{\font\pyxfont=cmr7\pyxfont\font\pyxfonttfa=cmr7\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr5\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi7\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi5\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy7\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy5\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\footnotesize{\font\pyxfont=cmr8\pyxfont\font\pyxfonttfa=cmr8\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr6\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi8\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi6\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy8\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy6\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\small{\font\pyxfont=cmr9\pyxfont\font\pyxfonttfa=cmr9\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr6\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi9\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi6\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy9\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy6\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\normalsize{\font\pyxfont=cmr10\pyxfont\font\pyxfonttfa=cmr10\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr7\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi10\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi7\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy7\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\large{\font\pyxfont=cmr12\pyxfont\font\pyxfonttfa=cmr12\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr8\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr6\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi8\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi6\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 12.0pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy8\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy6\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\Large{\font\pyxfont=cmr12 at 14.4pt\pyxfont\font\pyxfonttfa=cmr12 at 14.4pt\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr10\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr7\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12 at 14.4pt\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi10\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi7\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 14.4pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy10\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy7\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\LARGE{\font\pyxfont=cmr17\pyxfont\font\pyxfonttfa=cmr17\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr12\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr10\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12 at 17.28pt\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi12\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi10\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 17.28pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy10 at 12.0pt\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy10\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\huge{\font\pyxfont=cmr17 at 20.74pt\pyxfont\font\pyxfonttfa=cmr17 at 20.74pt\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr12 at 14.4pt\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr12\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12 at 20.74pt\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi12 at 14.4pt\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi12\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 20.74pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy10 at 14.4pt\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy10 at 12.0pt\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\Huge{\font\pyxfont=cmr17 at 24.88pt\pyxfont\font\pyxfonttfa=cmr17 at 24.88pt\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr17 at 20.74pt\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr17\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12 at 24.88pt\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi12 at 20.74pt\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi12 at 17.28pt\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 24.88pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy10 at 20.74pt\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy10 at 17.28pt\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
%
\PyXInput{2}%
\normalsize%
%
\PyXInput{3}%
\newdimen\linewidth\newdimen\textwidth%
%
\PyXInput{4}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{10^{-1}}}$}}\lower\PyXDimenVShift\box0%
}{1}%
\PyXInput{5}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{10^{0}}}$}}\lower\PyXDimenVShift\box0%
}{2}%
\PyXInput{6}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{10^{1}}}$}}\lower\PyXDimenVShift\box0%
}{3}%
\PyXInput{7}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{10^{2}}}$}}\lower\PyXDimenVShift\box0%
}{4}%
\PyXInput{8}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{5}%
\PyXInput{9}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{10^{4}}}$}}\lower\PyXDimenVShift\box0%
}{6}%
\PyXInput{10}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}cw SNR enhancement}}\lower\PyXDimenVShift\box0%
}{7}%
\PyXInput{11}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{0}$}}\lower\PyXDimenVShift\box0%
}{8}%
\PyXInput{12}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{0.25}$}}\lower\PyXDimenVShift\box0%
}{9}%
\PyXInput{13}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{0.5}$}}\lower\PyXDimenVShift\box0%
}{10}%
\PyXInput{14}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{0.75}$}}\lower\PyXDimenVShift\box0%
}{11}%
\PyXInput{15}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{1}$}}\lower\PyXDimenVShift\box0%
}{12}%
\PyXInput{16}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}closed loop gain, $t_{cav} \ll t_a$}}\lower\PyXDimenVShift\box0%
}{13}%
\PyXInput{17}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{0}$}}\lower\PyXDimenVShift\box0%
}{14}%
\PyXInput{18}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{0.2}$}}\lower\PyXDimenVShift\box0%
}{15}%
\PyXInput{19}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{0.4}$}}\lower\PyXDimenVShift\box0%
}{16}%
\PyXInput{20}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{0.6}$}}\lower\PyXDimenVShift\box0%
}{17}%
\PyXInput{21}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{0.8}$}}\lower\PyXDimenVShift\box0%
}{18}%
\PyXInput{22}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{1}$}}\lower\PyXDimenVShift\box0%
}{19}%
\PyXInput{23}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}closed loop gain, $t_{cav} \ll t_a$}}\lower\PyXDimenVShift\box0%
}{20}%
\PyXInput{24}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{delay}}\lower\PyXDimenVShift\box0%
}{21}%
\PyXInput{25}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{no delay}}\lower\PyXDimenVShift\box0%
}{22}%
\PyXInput{26}%
\end%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% preparing restart of tex
% PyX 0.12.1 texdebug file
% mode: tex
% date: Sun Apr 12 01:41:30 2015
\scrollmode
\raiseerror%
\def\PyX{P\kern-.3em\lower.5ex\hbox{Y}\kern-.18em X}%
\gdef\PyXBoxHAlign{0}%
\newbox\PyXBox%
\newbox\PyXBoxHAligned%
\newdimen\PyXDimenHAlignLT%
\newdimen\PyXDimenHAlignRT%
\gdef\PyXFlushHAlign{0}%
\def\PyXragged{%
\leftskip=0pt plus \PyXFlushHAlign fil%
\rightskip=0pt plus 1fil%
\advance\rightskip0pt plus -\PyXFlushHAlign fil%
\parfillskip=0pt%
\pretolerance=9999%
\tolerance=9999%
\parindent=0pt%
\hyphenpenalty=9999%
\exhyphenpenalty=9999}%
\newbox\PyXBoxVBox%
\newdimen\PyXDimenVBox%
\newbox\PyXBoxVAlign%
\newdimen\PyXDimenVAlign%
\newdimen\PyXDimenVShift%
\long\def\ProcessPyXBox#1#2{%
\setbox\PyXBox=\hbox{{#1}}%
\PyXDimenHAlignLT=\PyXBoxHAlign\wd\PyXBox%
\PyXDimenHAlignRT=\wd\PyXBox%
\advance\PyXDimenHAlignRT by -\PyXDimenHAlignLT%
\gdef\PyXBoxHAlign{0}%
\immediate\write16{PyXBox:page=#2,lt=\the\PyXDimenHAlignLT,rt=\the\PyXDimenHAlignRT,ht=\the\ht\PyXBox,dp=\the\dp\PyXBox:}%
\setbox\PyXBoxHAligned=\hbox{\kern-\PyXDimenHAlignLT\box\PyXBox}%
\ht\PyXBoxHAligned0pt%
{\count0=80\count1=121\count2=88\count3=#2\shipout\box\PyXBoxHAligned}}%
\def\PyXInput#1{\immediate\write16{PyXInputMarker:executeid=#1:}}%
\def\PyXMarker#1{\hskip0pt\special{PyX:marker #1}}%%
\PyXInput{1}%
% This automatically generated file is part of PyX (http://pyx.sourceforge.net/).
% \latexstylename="10pt"
% \latexclassname="article"
% \latexclassopt="10pt"
% \latexinit=""
\def\tiny{\font\pyxfont=cmr5\pyxfont\font\pyxfonttfa=cmr5\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr5\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi5\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi5\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy5\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy5\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\scriptsize{\font\pyxfont=cmr7\pyxfont\font\pyxfonttfa=cmr7\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr5\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi7\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi5\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy7\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy5\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\footnotesize{\font\pyxfont=cmr8\pyxfont\font\pyxfonttfa=cmr8\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr6\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi8\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi6\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy8\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy6\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\small{\font\pyxfont=cmr9\pyxfont\font\pyxfonttfa=cmr9\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr6\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi9\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi6\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy9\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy6\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\normalsize{\font\pyxfont=cmr10\pyxfont\font\pyxfonttfa=cmr10\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr7\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi10\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi7\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy7\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\large{\font\pyxfont=cmr12\pyxfont\font\pyxfonttfa=cmr12\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr8\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr6\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi8\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi6\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 12.0pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy8\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy6\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\Large{\font\pyxfont=cmr12 at 14.4pt\pyxfont\font\pyxfonttfa=cmr12 at 14.4pt\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr10\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr7\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12 at 14.4pt\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi10\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi7\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 14.4pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy10\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy7\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\LARGE{\font\pyxfont=cmr17\pyxfont\font\pyxfonttfa=cmr17\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr12\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr10\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12 at 17.28pt\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi12\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi10\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 17.28pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy10 at 12.0pt\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy10\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\huge{\font\pyxfont=cmr17 at 20.74pt\pyxfont\font\pyxfonttfa=cmr17 at 20.74pt\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr12 at 14.4pt\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr12\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12 at 20.74pt\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi12 at 14.4pt\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi12\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 20.74pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy10 at 14.4pt\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy10 at 12.0pt\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\Huge{\font\pyxfont=cmr17 at 24.88pt\pyxfont\font\pyxfonttfa=cmr17 at 24.88pt\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr17 at 20.74pt\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr17\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12 at 24.88pt\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi12 at 20.74pt\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi12 at 17.28pt\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 24.88pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy10 at 20.74pt\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy10 at 17.28pt\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
%
\PyXInput{2}%
\normalsize%
%
\PyXInput{3}%
\newdimen\linewidth\newdimen\textwidth%
%
\PyXInput{4}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{2.5}$}}\lower\PyXDimenVShift\box0%
}{1}%
\PyXInput{5}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{5}$}}\lower\PyXDimenVShift\box0%
}{2}%
\PyXInput{6}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{7.5}$}}\lower\PyXDimenVShift\box0%
}{3}%
\PyXInput{7}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{10}$}}\lower\PyXDimenVShift\box0%
}{4}%
\PyXInput{8}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{12.5}$}}\lower\PyXDimenVShift\box0%
}{5}%
\PyXInput{9}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{15}$}}\lower\PyXDimenVShift\box0%
}{6}%
\PyXInput{10}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}SNR enhancement}}\lower\PyXDimenVShift\box0%
}{7}%
\PyXInput{11}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{5}$}}\lower\PyXDimenVShift\box0%
}{8}%
\PyXInput{12}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{10}$}}\lower\PyXDimenVShift\box0%
}{9}%
\PyXInput{13}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{15}$}}\lower\PyXDimenVShift\box0%
}{10}%
\PyXInput{14}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}SNR enhancement}}\lower\PyXDimenVShift\box0%
}{11}%
\PyXInput{15}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{2}$}}\lower\PyXDimenVShift\box0%
}{12}%
\PyXInput{16}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{4}$}}\lower\PyXDimenVShift\box0%
}{13}%
\PyXInput{17}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{6}$}}\lower\PyXDimenVShift\box0%
}{14}%
\PyXInput{18}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{8}$}}\lower\PyXDimenVShift\box0%
}{15}%
\PyXInput{19}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{10}$}}\lower\PyXDimenVShift\box0%
}{16}%
\PyXInput{20}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{12}$}}\lower\PyXDimenVShift\box0%
}{17}%
\PyXInput{21}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{14}$}}\lower\PyXDimenVShift\box0%
}{18}%
\PyXInput{22}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}SNR enhancement}}\lower\PyXDimenVShift\box0%
}{19}%
\PyXInput{23}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{2.5}$}}\lower\PyXDimenVShift\box0%
}{20}%
\PyXInput{24}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{5}$}}\lower\PyXDimenVShift\box0%
}{21}%
\PyXInput{25}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{7.5}$}}\lower\PyXDimenVShift\box0%
}{22}%
\PyXInput{26}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{10}$}}\lower\PyXDimenVShift\box0%
}{23}%
\PyXInput{27}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{12.5}$}}\lower\PyXDimenVShift\box0%
}{24}%
\PyXInput{28}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{15}$}}\lower\PyXDimenVShift\box0%
}{25}%
\PyXInput{29}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}SNR enhancement}}\lower\PyXDimenVShift\box0%
}{26}%
\PyXInput{30}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{5}$}}\lower\PyXDimenVShift\box0%
}{27}%
\PyXInput{31}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{10}$}}\lower\PyXDimenVShift\box0%
}{28}%
\PyXInput{32}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{15}$}}\lower\PyXDimenVShift\box0%
}{29}%
\PyXInput{33}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}SNR enhancement}}\lower\PyXDimenVShift\box0%
}{30}%
\PyXInput{34}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{2}$}}\lower\PyXDimenVShift\box0%
}{31}%
\PyXInput{35}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{4}$}}\lower\PyXDimenVShift\box0%
}{32}%
\PyXInput{36}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{6}$}}\lower\PyXDimenVShift\box0%
}{33}%
\PyXInput{37}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{8}$}}\lower\PyXDimenVShift\box0%
}{34}%
\PyXInput{38}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{10}$}}\lower\PyXDimenVShift\box0%
}{35}%
\PyXInput{39}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{12}$}}\lower\PyXDimenVShift\box0%
}{36}%
\PyXInput{40}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{14}$}}\lower\PyXDimenVShift\box0%
}{37}%
\PyXInput{41}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}SNR enhancement}}\lower\PyXDimenVShift\box0%
}{38}%
\PyXInput{42}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{0}}$}}\lower\PyXDimenVShift\box0%
}{39}%
\PyXInput{43}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{2.5}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{40}%
\PyXInput{44}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{5}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{41}%
\PyXInput{45}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{7.5}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{42}%
\PyXInput{46}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{1}\cdot10^{4}}}$}}\lower\PyXDimenVShift\box0%
}{43}%
\PyXInput{47}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}active Q}}\lower\PyXDimenVShift\box0%
}{44}%
\PyXInput{48}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{0}}$}}\lower\PyXDimenVShift\box0%
}{45}%
\PyXInput{49}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{2}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{46}%
\PyXInput{50}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{4}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{47}%
\PyXInput{51}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{6}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{48}%
\PyXInput{52}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{8}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{49}%
\PyXInput{53}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{1}\cdot10^{4}}}$}}\lower\PyXDimenVShift\box0%
}{50}%
\PyXInput{54}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}active Q}}\lower\PyXDimenVShift\box0%
}{51}%
\PyXInput{55}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{no delay}}\lower\PyXDimenVShift\box0%
}{52}%
\PyXInput{56}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{delay}}\lower\PyXDimenVShift\box0%
}{53}%
\PyXInput{57}%
\end%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% preparing restart of tex
% PyX 0.12.1 texdebug file
% mode: tex
% date: Sun Apr 12 01:48:26 2015
\scrollmode
\raiseerror%
\def\PyX{P\kern-.3em\lower.5ex\hbox{Y}\kern-.18em X}%
\gdef\PyXBoxHAlign{0}%
\newbox\PyXBox%
\newbox\PyXBoxHAligned%
\newdimen\PyXDimenHAlignLT%
\newdimen\PyXDimenHAlignRT%
\gdef\PyXFlushHAlign{0}%
\def\PyXragged{%
\leftskip=0pt plus \PyXFlushHAlign fil%
\rightskip=0pt plus 1fil%
\advance\rightskip0pt plus -\PyXFlushHAlign fil%
\parfillskip=0pt%
\pretolerance=9999%
\tolerance=9999%
\parindent=0pt%
\hyphenpenalty=9999%
\exhyphenpenalty=9999}%
\newbox\PyXBoxVBox%
\newdimen\PyXDimenVBox%
\newbox\PyXBoxVAlign%
\newdimen\PyXDimenVAlign%
\newdimen\PyXDimenVShift%
\long\def\ProcessPyXBox#1#2{%
\setbox\PyXBox=\hbox{{#1}}%
\PyXDimenHAlignLT=\PyXBoxHAlign\wd\PyXBox%
\PyXDimenHAlignRT=\wd\PyXBox%
\advance\PyXDimenHAlignRT by -\PyXDimenHAlignLT%
\gdef\PyXBoxHAlign{0}%
\immediate\write16{PyXBox:page=#2,lt=\the\PyXDimenHAlignLT,rt=\the\PyXDimenHAlignRT,ht=\the\ht\PyXBox,dp=\the\dp\PyXBox:}%
\setbox\PyXBoxHAligned=\hbox{\kern-\PyXDimenHAlignLT\box\PyXBox}%
\ht\PyXBoxHAligned0pt%
{\count0=80\count1=121\count2=88\count3=#2\shipout\box\PyXBoxHAligned}}%
\def\PyXInput#1{\immediate\write16{PyXInputMarker:executeid=#1:}}%
\def\PyXMarker#1{\hskip0pt\special{PyX:marker #1}}%%
\PyXInput{1}%
% This automatically generated file is part of PyX (http://pyx.sourceforge.net/).
% \latexstylename="10pt"
% \latexclassname="article"
% \latexclassopt="10pt"
% \latexinit=""
\def\tiny{\font\pyxfont=cmr5\pyxfont\font\pyxfonttfa=cmr5\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr5\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi5\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi5\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy5\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy5\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\scriptsize{\font\pyxfont=cmr7\pyxfont\font\pyxfonttfa=cmr7\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr5\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi7\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi5\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy7\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy5\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\footnotesize{\font\pyxfont=cmr8\pyxfont\font\pyxfonttfa=cmr8\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr6\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi8\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi6\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy8\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy6\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\small{\font\pyxfont=cmr9\pyxfont\font\pyxfonttfa=cmr9\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr6\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi9\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi6\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy9\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy6\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\normalsize{\font\pyxfont=cmr10\pyxfont\font\pyxfonttfa=cmr10\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr7\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi10\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi7\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy7\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\large{\font\pyxfont=cmr12\pyxfont\font\pyxfonttfa=cmr12\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr8\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr6\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi8\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi6\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 12.0pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy8\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy6\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\Large{\font\pyxfont=cmr12 at 14.4pt\pyxfont\font\pyxfonttfa=cmr12 at 14.4pt\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr10\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr7\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12 at 14.4pt\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi10\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi7\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 14.4pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy10\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy7\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\LARGE{\font\pyxfont=cmr17\pyxfont\font\pyxfonttfa=cmr17\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr12\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr10\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12 at 17.28pt\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi12\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi10\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 17.28pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy10 at 12.0pt\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy10\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\huge{\font\pyxfont=cmr17 at 20.74pt\pyxfont\font\pyxfonttfa=cmr17 at 20.74pt\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr12 at 14.4pt\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr12\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12 at 20.74pt\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi12 at 14.4pt\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi12\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 20.74pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy10 at 14.4pt\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy10 at 12.0pt\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\Huge{\font\pyxfont=cmr17 at 24.88pt\pyxfont\font\pyxfonttfa=cmr17 at 24.88pt\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr17 at 20.74pt\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr17\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12 at 24.88pt\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi12 at 20.74pt\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi12 at 17.28pt\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 24.88pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy10 at 20.74pt\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy10 at 17.28pt\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
%
\PyXInput{2}%
\normalsize%
%
\PyXInput{3}%
\newdimen\linewidth\newdimen\textwidth%
%
\PyXInput{4}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{2.5}$}}\lower\PyXDimenVShift\box0%
}{1}%
\PyXInput{5}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{5}$}}\lower\PyXDimenVShift\box0%
}{2}%
\PyXInput{6}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{7.5}$}}\lower\PyXDimenVShift\box0%
}{3}%
\PyXInput{7}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{10}$}}\lower\PyXDimenVShift\box0%
}{4}%
\PyXInput{8}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{12.5}$}}\lower\PyXDimenVShift\box0%
}{5}%
\PyXInput{9}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{15}$}}\lower\PyXDimenVShift\box0%
}{6}%
\PyXInput{10}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}SNR enhancement}}\lower\PyXDimenVShift\box0%
}{7}%
\PyXInput{11}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{5}$}}\lower\PyXDimenVShift\box0%
}{8}%
\PyXInput{12}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{10}$}}\lower\PyXDimenVShift\box0%
}{9}%
\PyXInput{13}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{15}$}}\lower\PyXDimenVShift\box0%
}{10}%
\PyXInput{14}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}SNR enhancement}}\lower\PyXDimenVShift\box0%
}{11}%
\PyXInput{15}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{2}$}}\lower\PyXDimenVShift\box0%
}{12}%
\PyXInput{16}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{4}$}}\lower\PyXDimenVShift\box0%
}{13}%
\PyXInput{17}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{6}$}}\lower\PyXDimenVShift\box0%
}{14}%
\PyXInput{18}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{8}$}}\lower\PyXDimenVShift\box0%
}{15}%
\PyXInput{19}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{10}$}}\lower\PyXDimenVShift\box0%
}{16}%
\PyXInput{20}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{12}$}}\lower\PyXDimenVShift\box0%
}{17}%
\PyXInput{21}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{14}$}}\lower\PyXDimenVShift\box0%
}{18}%
\PyXInput{22}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}SNR enhancement}}\lower\PyXDimenVShift\box0%
}{19}%
\PyXInput{23}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{0}}$}}\lower\PyXDimenVShift\box0%
}{20}%
\PyXInput{24}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{2.5}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{21}%
\PyXInput{25}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{5}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{22}%
\PyXInput{26}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{7.5}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{23}%
\PyXInput{27}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{1}\cdot10^{4}}}$}}\lower\PyXDimenVShift\box0%
}{24}%
\PyXInput{28}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}active Q}}\lower\PyXDimenVShift\box0%
}{25}%
\PyXInput{29}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{0}}$}}\lower\PyXDimenVShift\box0%
}{26}%
\PyXInput{30}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{2}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{27}%
\PyXInput{31}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{4}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{28}%
\PyXInput{32}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{6}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{29}%
\PyXInput{33}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{8}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{30}%
\PyXInput{34}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{1}\cdot10^{4}}}$}}\lower\PyXDimenVShift\box0%
}{31}%
\PyXInput{35}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}active Q}}\lower\PyXDimenVShift\box0%
}{32}%
\PyXInput{36}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{no delay}}\lower\PyXDimenVShift\box0%
}{33}%
\PyXInput{37}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{delay}}\lower\PyXDimenVShift\box0%
}{34}%
\PyXInput{38}%
\end%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% preparing restart of tex
% PyX 0.12.1 texdebug file
% mode: tex
% date: Sun Apr 12 01:48:34 2015
\scrollmode
\raiseerror%
\def\PyX{P\kern-.3em\lower.5ex\hbox{Y}\kern-.18em X}%
\gdef\PyXBoxHAlign{0}%
\newbox\PyXBox%
\newbox\PyXBoxHAligned%
\newdimen\PyXDimenHAlignLT%
\newdimen\PyXDimenHAlignRT%
\gdef\PyXFlushHAlign{0}%
\def\PyXragged{%
\leftskip=0pt plus \PyXFlushHAlign fil%
\rightskip=0pt plus 1fil%
\advance\rightskip0pt plus -\PyXFlushHAlign fil%
\parfillskip=0pt%
\pretolerance=9999%
\tolerance=9999%
\parindent=0pt%
\hyphenpenalty=9999%
\exhyphenpenalty=9999}%
\newbox\PyXBoxVBox%
\newdimen\PyXDimenVBox%
\newbox\PyXBoxVAlign%
\newdimen\PyXDimenVAlign%
\newdimen\PyXDimenVShift%
\long\def\ProcessPyXBox#1#2{%
\setbox\PyXBox=\hbox{{#1}}%
\PyXDimenHAlignLT=\PyXBoxHAlign\wd\PyXBox%
\PyXDimenHAlignRT=\wd\PyXBox%
\advance\PyXDimenHAlignRT by -\PyXDimenHAlignLT%
\gdef\PyXBoxHAlign{0}%
\immediate\write16{PyXBox:page=#2,lt=\the\PyXDimenHAlignLT,rt=\the\PyXDimenHAlignRT,ht=\the\ht\PyXBox,dp=\the\dp\PyXBox:}%
\setbox\PyXBoxHAligned=\hbox{\kern-\PyXDimenHAlignLT\box\PyXBox}%
\ht\PyXBoxHAligned0pt%
{\count0=80\count1=121\count2=88\count3=#2\shipout\box\PyXBoxHAligned}}%
\def\PyXInput#1{\immediate\write16{PyXInputMarker:executeid=#1:}}%
\def\PyXMarker#1{\hskip0pt\special{PyX:marker #1}}%%
\PyXInput{1}%
% This automatically generated file is part of PyX (http://pyx.sourceforge.net/).
% \latexstylename="10pt"
% \latexclassname="article"
% \latexclassopt="10pt"
% \latexinit=""
\def\tiny{\font\pyxfont=cmr5\pyxfont\font\pyxfonttfa=cmr5\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr5\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi5\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi5\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy5\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy5\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\scriptsize{\font\pyxfont=cmr7\pyxfont\font\pyxfonttfa=cmr7\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr5\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi7\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi5\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy7\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy5\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\footnotesize{\font\pyxfont=cmr8\pyxfont\font\pyxfonttfa=cmr8\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr6\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi8\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi6\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy8\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy6\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\small{\font\pyxfont=cmr9\pyxfont\font\pyxfonttfa=cmr9\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr6\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi9\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi6\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy9\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy6\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\normalsize{\font\pyxfont=cmr10\pyxfont\font\pyxfonttfa=cmr10\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr7\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi10\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi7\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy7\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\large{\font\pyxfont=cmr12\pyxfont\font\pyxfonttfa=cmr12\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr8\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr6\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi8\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi6\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 12.0pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy8\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy6\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\Large{\font\pyxfont=cmr12 at 14.4pt\pyxfont\font\pyxfonttfa=cmr12 at 14.4pt\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr10\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr7\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12 at 14.4pt\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi10\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi7\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 14.4pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy10\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy7\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\LARGE{\font\pyxfont=cmr17\pyxfont\font\pyxfonttfa=cmr17\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr12\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr10\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12 at 17.28pt\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi12\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi10\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 17.28pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy10 at 12.0pt\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy10\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\huge{\font\pyxfont=cmr17 at 20.74pt\pyxfont\font\pyxfonttfa=cmr17 at 20.74pt\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr12 at 14.4pt\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr12\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12 at 20.74pt\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi12 at 14.4pt\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi12\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 20.74pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy10 at 14.4pt\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy10 at 12.0pt\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\Huge{\font\pyxfont=cmr17 at 24.88pt\pyxfont\font\pyxfonttfa=cmr17 at 24.88pt\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr17 at 20.74pt\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr17\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12 at 24.88pt\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi12 at 20.74pt\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi12 at 17.28pt\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 24.88pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy10 at 20.74pt\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy10 at 17.28pt\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
%
\PyXInput{2}%
\normalsize%
%
\PyXInput{3}%
\newdimen\linewidth\newdimen\textwidth%
%
\PyXInput{4}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{2.5}$}}\lower\PyXDimenVShift\box0%
}{1}%
\PyXInput{5}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{5}$}}\lower\PyXDimenVShift\box0%
}{2}%
\PyXInput{6}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{7.5}$}}\lower\PyXDimenVShift\box0%
}{3}%
\PyXInput{7}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{10}$}}\lower\PyXDimenVShift\box0%
}{4}%
\PyXInput{8}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{12.5}$}}\lower\PyXDimenVShift\box0%
}{5}%
\PyXInput{9}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{15}$}}\lower\PyXDimenVShift\box0%
}{6}%
\PyXInput{10}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}SNR enhancement}}\lower\PyXDimenVShift\box0%
}{7}%
\PyXInput{11}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{5}$}}\lower\PyXDimenVShift\box0%
}{8}%
\PyXInput{12}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{10}$}}\lower\PyXDimenVShift\box0%
}{9}%
\PyXInput{13}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{15}$}}\lower\PyXDimenVShift\box0%
}{10}%
\PyXInput{14}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}SNR enhancement}}\lower\PyXDimenVShift\box0%
}{11}%
\PyXInput{15}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{2}$}}\lower\PyXDimenVShift\box0%
}{12}%
\PyXInput{16}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{4}$}}\lower\PyXDimenVShift\box0%
}{13}%
\PyXInput{17}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{6}$}}\lower\PyXDimenVShift\box0%
}{14}%
\PyXInput{18}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{8}$}}\lower\PyXDimenVShift\box0%
}{15}%
\PyXInput{19}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{10}$}}\lower\PyXDimenVShift\box0%
}{16}%
\PyXInput{20}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{12}$}}\lower\PyXDimenVShift\box0%
}{17}%
\PyXInput{21}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{14}$}}\lower\PyXDimenVShift\box0%
}{18}%
\PyXInput{22}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}SNR enhancement}}\lower\PyXDimenVShift\box0%
}{19}%
\PyXInput{23}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{0}}$}}\lower\PyXDimenVShift\box0%
}{20}%
\PyXInput{24}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{2.5}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{21}%
\PyXInput{25}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{5}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{22}%
\PyXInput{26}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{7.5}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{23}%
\PyXInput{27}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{1}\cdot10^{4}}}$}}\lower\PyXDimenVShift\box0%
}{24}%
\PyXInput{28}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}active Q}}\lower\PyXDimenVShift\box0%
}{25}%
\PyXInput{29}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{0}}$}}\lower\PyXDimenVShift\box0%
}{26}%
\PyXInput{30}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{2}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{27}%
\PyXInput{31}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{4}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{28}%
\PyXInput{32}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{6}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{29}%
\PyXInput{33}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{8}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{30}%
\PyXInput{34}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{1}\cdot10^{4}}}$}}\lower\PyXDimenVShift\box0%
}{31}%
\PyXInput{35}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}active Q}}\lower\PyXDimenVShift\box0%
}{32}%
\PyXInput{36}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{no delay}}\lower\PyXDimenVShift\box0%
}{33}%
\PyXInput{37}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{delay}}\lower\PyXDimenVShift\box0%
}{34}%
\PyXInput{38}%
\end%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% preparing restart of tex
% PyX 0.12.1 texdebug file
% mode: tex
% date: Sun Apr 12 01:50:08 2015
\scrollmode
\raiseerror%
\def\PyX{P\kern-.3em\lower.5ex\hbox{Y}\kern-.18em X}%
\gdef\PyXBoxHAlign{0}%
\newbox\PyXBox%
\newbox\PyXBoxHAligned%
\newdimen\PyXDimenHAlignLT%
\newdimen\PyXDimenHAlignRT%
\gdef\PyXFlushHAlign{0}%
\def\PyXragged{%
\leftskip=0pt plus \PyXFlushHAlign fil%
\rightskip=0pt plus 1fil%
\advance\rightskip0pt plus -\PyXFlushHAlign fil%
\parfillskip=0pt%
\pretolerance=9999%
\tolerance=9999%
\parindent=0pt%
\hyphenpenalty=9999%
\exhyphenpenalty=9999}%
\newbox\PyXBoxVBox%
\newdimen\PyXDimenVBox%
\newbox\PyXBoxVAlign%
\newdimen\PyXDimenVAlign%
\newdimen\PyXDimenVShift%
\long\def\ProcessPyXBox#1#2{%
\setbox\PyXBox=\hbox{{#1}}%
\PyXDimenHAlignLT=\PyXBoxHAlign\wd\PyXBox%
\PyXDimenHAlignRT=\wd\PyXBox%
\advance\PyXDimenHAlignRT by -\PyXDimenHAlignLT%
\gdef\PyXBoxHAlign{0}%
\immediate\write16{PyXBox:page=#2,lt=\the\PyXDimenHAlignLT,rt=\the\PyXDimenHAlignRT,ht=\the\ht\PyXBox,dp=\the\dp\PyXBox:}%
\setbox\PyXBoxHAligned=\hbox{\kern-\PyXDimenHAlignLT\box\PyXBox}%
\ht\PyXBoxHAligned0pt%
{\count0=80\count1=121\count2=88\count3=#2\shipout\box\PyXBoxHAligned}}%
\def\PyXInput#1{\immediate\write16{PyXInputMarker:executeid=#1:}}%
\def\PyXMarker#1{\hskip0pt\special{PyX:marker #1}}%%
\PyXInput{1}%
% This automatically generated file is part of PyX (http://pyx.sourceforge.net/).
% \latexstylename="10pt"
% \latexclassname="article"
% \latexclassopt="10pt"
% \latexinit=""
\def\tiny{\font\pyxfont=cmr5\pyxfont\font\pyxfonttfa=cmr5\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr5\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi5\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi5\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy5\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy5\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\scriptsize{\font\pyxfont=cmr7\pyxfont\font\pyxfonttfa=cmr7\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr5\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi7\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi5\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy7\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy5\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\footnotesize{\font\pyxfont=cmr8\pyxfont\font\pyxfonttfa=cmr8\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr6\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi8\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi6\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy8\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy6\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\small{\font\pyxfont=cmr9\pyxfont\font\pyxfonttfa=cmr9\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr6\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi9\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi6\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy9\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy6\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\normalsize{\font\pyxfont=cmr10\pyxfont\font\pyxfonttfa=cmr10\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr7\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi10\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi7\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy7\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\large{\font\pyxfont=cmr12\pyxfont\font\pyxfonttfa=cmr12\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr8\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr6\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi8\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi6\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 12.0pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy8\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy6\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\Large{\font\pyxfont=cmr12 at 14.4pt\pyxfont\font\pyxfonttfa=cmr12 at 14.4pt\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr10\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr7\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12 at 14.4pt\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi10\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi7\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 14.4pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy10\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy7\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\LARGE{\font\pyxfont=cmr17\pyxfont\font\pyxfonttfa=cmr17\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr12\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr10\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12 at 17.28pt\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi12\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi10\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 17.28pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy10 at 12.0pt\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy10\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\huge{\font\pyxfont=cmr17 at 20.74pt\pyxfont\font\pyxfonttfa=cmr17 at 20.74pt\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr12 at 14.4pt\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr12\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12 at 20.74pt\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi12 at 14.4pt\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi12\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 20.74pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy10 at 14.4pt\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy10 at 12.0pt\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\Huge{\font\pyxfont=cmr17 at 24.88pt\pyxfont\font\pyxfonttfa=cmr17 at 24.88pt\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr17 at 20.74pt\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr17\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12 at 24.88pt\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi12 at 20.74pt\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi12 at 17.28pt\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 24.88pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy10 at 20.74pt\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy10 at 17.28pt\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
%
\PyXInput{2}%
\normalsize%
%
\PyXInput{3}%
\newdimen\linewidth\newdimen\textwidth%
%
\PyXInput{4}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{2.5}$}}\lower\PyXDimenVShift\box0%
}{1}%
\PyXInput{5}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{5}$}}\lower\PyXDimenVShift\box0%
}{2}%
\PyXInput{6}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{7.5}$}}\lower\PyXDimenVShift\box0%
}{3}%
\PyXInput{7}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{10}$}}\lower\PyXDimenVShift\box0%
}{4}%
\PyXInput{8}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{12.5}$}}\lower\PyXDimenVShift\box0%
}{5}%
\PyXInput{9}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{15}$}}\lower\PyXDimenVShift\box0%
}{6}%
\PyXInput{10}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}SNR enhancement}}\lower\PyXDimenVShift\box0%
}{7}%
\PyXInput{11}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{5}$}}\lower\PyXDimenVShift\box0%
}{8}%
\PyXInput{12}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{10}$}}\lower\PyXDimenVShift\box0%
}{9}%
\PyXInput{13}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{15}$}}\lower\PyXDimenVShift\box0%
}{10}%
\PyXInput{14}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}SNR enhancement}}\lower\PyXDimenVShift\box0%
}{11}%
\PyXInput{15}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{2}$}}\lower\PyXDimenVShift\box0%
}{12}%
\PyXInput{16}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{4}$}}\lower\PyXDimenVShift\box0%
}{13}%
\PyXInput{17}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{6}$}}\lower\PyXDimenVShift\box0%
}{14}%
\PyXInput{18}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{8}$}}\lower\PyXDimenVShift\box0%
}{15}%
\PyXInput{19}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{10}$}}\lower\PyXDimenVShift\box0%
}{16}%
\PyXInput{20}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{12}$}}\lower\PyXDimenVShift\box0%
}{17}%
\PyXInput{21}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{14}$}}\lower\PyXDimenVShift\box0%
}{18}%
\PyXInput{22}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}SNR enhancement}}\lower\PyXDimenVShift\box0%
}{19}%
\PyXInput{23}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{0}}$}}\lower\PyXDimenVShift\box0%
}{20}%
\PyXInput{24}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{2.5}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{21}%
\PyXInput{25}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{5}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{22}%
\PyXInput{26}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{7.5}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{23}%
\PyXInput{27}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{1}\cdot10^{4}}}$}}\lower\PyXDimenVShift\box0%
}{24}%
\PyXInput{28}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}active Q}}\lower\PyXDimenVShift\box0%
}{25}%
\PyXInput{29}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{0}}$}}\lower\PyXDimenVShift\box0%
}{26}%
\PyXInput{30}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{2}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{27}%
\PyXInput{31}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{4}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{28}%
\PyXInput{32}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{6}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{29}%
\PyXInput{33}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{8}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{30}%
\PyXInput{34}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{1}\cdot10^{4}}}$}}\lower\PyXDimenVShift\box0%
}{31}%
\PyXInput{35}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}active Q}}\lower\PyXDimenVShift\box0%
}{32}%
\PyXInput{36}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{no delay}}\lower\PyXDimenVShift\box0%
}{33}%
\PyXInput{37}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{delay}}\lower\PyXDimenVShift\box0%
}{34}%
\PyXInput{38}%
\end%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% preparing restart of tex
% PyX 0.12.1 texdebug file
% mode: tex
% date: Sun Apr 12 01:53:25 2015
\scrollmode
\raiseerror%
\def\PyX{P\kern-.3em\lower.5ex\hbox{Y}\kern-.18em X}%
\gdef\PyXBoxHAlign{0}%
\newbox\PyXBox%
\newbox\PyXBoxHAligned%
\newdimen\PyXDimenHAlignLT%
\newdimen\PyXDimenHAlignRT%
\gdef\PyXFlushHAlign{0}%
\def\PyXragged{%
\leftskip=0pt plus \PyXFlushHAlign fil%
\rightskip=0pt plus 1fil%
\advance\rightskip0pt plus -\PyXFlushHAlign fil%
\parfillskip=0pt%
\pretolerance=9999%
\tolerance=9999%
\parindent=0pt%
\hyphenpenalty=9999%
\exhyphenpenalty=9999}%
\newbox\PyXBoxVBox%
\newdimen\PyXDimenVBox%
\newbox\PyXBoxVAlign%
\newdimen\PyXDimenVAlign%
\newdimen\PyXDimenVShift%
\long\def\ProcessPyXBox#1#2{%
\setbox\PyXBox=\hbox{{#1}}%
\PyXDimenHAlignLT=\PyXBoxHAlign\wd\PyXBox%
\PyXDimenHAlignRT=\wd\PyXBox%
\advance\PyXDimenHAlignRT by -\PyXDimenHAlignLT%
\gdef\PyXBoxHAlign{0}%
\immediate\write16{PyXBox:page=#2,lt=\the\PyXDimenHAlignLT,rt=\the\PyXDimenHAlignRT,ht=\the\ht\PyXBox,dp=\the\dp\PyXBox:}%
\setbox\PyXBoxHAligned=\hbox{\kern-\PyXDimenHAlignLT\box\PyXBox}%
\ht\PyXBoxHAligned0pt%
{\count0=80\count1=121\count2=88\count3=#2\shipout\box\PyXBoxHAligned}}%
\def\PyXInput#1{\immediate\write16{PyXInputMarker:executeid=#1:}}%
\def\PyXMarker#1{\hskip0pt\special{PyX:marker #1}}%%
\PyXInput{1}%
% This automatically generated file is part of PyX (http://pyx.sourceforge.net/).
% \latexstylename="10pt"
% \latexclassname="article"
% \latexclassopt="10pt"
% \latexinit=""
\def\tiny{\font\pyxfont=cmr5\pyxfont\font\pyxfonttfa=cmr5\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr5\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi5\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi5\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy5\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy5\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\scriptsize{\font\pyxfont=cmr7\pyxfont\font\pyxfonttfa=cmr7\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr5\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi7\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi5\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy7\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy5\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\footnotesize{\font\pyxfont=cmr8\pyxfont\font\pyxfonttfa=cmr8\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr6\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi8\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi6\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy8\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy6\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\small{\font\pyxfont=cmr9\pyxfont\font\pyxfonttfa=cmr9\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr6\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi9\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi6\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy9\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy6\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\normalsize{\font\pyxfont=cmr10\pyxfont\font\pyxfonttfa=cmr10\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr7\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi10\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi7\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy7\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\large{\font\pyxfont=cmr12\pyxfont\font\pyxfonttfa=cmr12\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr8\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr6\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi8\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi6\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 12.0pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy8\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy6\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\Large{\font\pyxfont=cmr12 at 14.4pt\pyxfont\font\pyxfonttfa=cmr12 at 14.4pt\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr10\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr7\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12 at 14.4pt\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi10\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi7\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 14.4pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy10\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy7\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\LARGE{\font\pyxfont=cmr17\pyxfont\font\pyxfonttfa=cmr17\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr12\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr10\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12 at 17.28pt\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi12\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi10\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 17.28pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy10 at 12.0pt\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy10\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\huge{\font\pyxfont=cmr17 at 20.74pt\pyxfont\font\pyxfonttfa=cmr17 at 20.74pt\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr12 at 14.4pt\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr12\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12 at 20.74pt\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi12 at 14.4pt\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi12\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 20.74pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy10 at 14.4pt\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy10 at 12.0pt\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\Huge{\font\pyxfont=cmr17 at 24.88pt\pyxfont\font\pyxfonttfa=cmr17 at 24.88pt\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr17 at 20.74pt\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr17\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12 at 24.88pt\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi12 at 20.74pt\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi12 at 17.28pt\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 24.88pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy10 at 20.74pt\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy10 at 17.28pt\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
%
\PyXInput{2}%
\normalsize%
%
\PyXInput{3}%
\newdimen\linewidth\newdimen\textwidth%
%
\PyXInput{4}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{2.5}$}}\lower\PyXDimenVShift\box0%
}{1}%
\PyXInput{5}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{5}$}}\lower\PyXDimenVShift\box0%
}{2}%
\PyXInput{6}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{7.5}$}}\lower\PyXDimenVShift\box0%
}{3}%
\PyXInput{7}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{10}$}}\lower\PyXDimenVShift\box0%
}{4}%
\PyXInput{8}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{12.5}$}}\lower\PyXDimenVShift\box0%
}{5}%
\PyXInput{9}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{15}$}}\lower\PyXDimenVShift\box0%
}{6}%
\PyXInput{10}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}SNR enhancement}}\lower\PyXDimenVShift\box0%
}{7}%
\PyXInput{11}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{5}$}}\lower\PyXDimenVShift\box0%
}{8}%
\PyXInput{12}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{10}$}}\lower\PyXDimenVShift\box0%
}{9}%
\PyXInput{13}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{15}$}}\lower\PyXDimenVShift\box0%
}{10}%
\PyXInput{14}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}SNR enhancement}}\lower\PyXDimenVShift\box0%
}{11}%
\PyXInput{15}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{2}$}}\lower\PyXDimenVShift\box0%
}{12}%
\PyXInput{16}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{4}$}}\lower\PyXDimenVShift\box0%
}{13}%
\PyXInput{17}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{6}$}}\lower\PyXDimenVShift\box0%
}{14}%
\PyXInput{18}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{8}$}}\lower\PyXDimenVShift\box0%
}{15}%
\PyXInput{19}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{10}$}}\lower\PyXDimenVShift\box0%
}{16}%
\PyXInput{20}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{12}$}}\lower\PyXDimenVShift\box0%
}{17}%
\PyXInput{21}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{14}$}}\lower\PyXDimenVShift\box0%
}{18}%
\PyXInput{22}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}SNR enhancement}}\lower\PyXDimenVShift\box0%
}{19}%
\PyXInput{23}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{0}}$}}\lower\PyXDimenVShift\box0%
}{20}%
\PyXInput{24}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{2.5}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{21}%
\PyXInput{25}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{5}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{22}%
\PyXInput{26}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{7.5}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{23}%
\PyXInput{27}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{1}\cdot10^{4}}}$}}\lower\PyXDimenVShift\box0%
}{24}%
\PyXInput{28}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}active Q}}\lower\PyXDimenVShift\box0%
}{25}%
\PyXInput{29}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{0}}$}}\lower\PyXDimenVShift\box0%
}{26}%
\PyXInput{30}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{2}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{27}%
\PyXInput{31}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{4}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{28}%
\PyXInput{32}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{6}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{29}%
\PyXInput{33}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{8}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{30}%
\PyXInput{34}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{1}\cdot10^{4}}}$}}\lower\PyXDimenVShift\box0%
}{31}%
\PyXInput{35}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}active Q}}\lower\PyXDimenVShift\box0%
}{32}%
\PyXInput{36}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{no delay}}\lower\PyXDimenVShift\box0%
}{33}%
\PyXInput{37}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{delay}}\lower\PyXDimenVShift\box0%
}{34}%
\PyXInput{38}%
\end%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% preparing restart of tex
% PyX 0.12.1 texdebug file
% mode: tex
% date: Sun Apr 12 01:55:37 2015
\scrollmode
\raiseerror%
\def\PyX{P\kern-.3em\lower.5ex\hbox{Y}\kern-.18em X}%
\gdef\PyXBoxHAlign{0}%
\newbox\PyXBox%
\newbox\PyXBoxHAligned%
\newdimen\PyXDimenHAlignLT%
\newdimen\PyXDimenHAlignRT%
\gdef\PyXFlushHAlign{0}%
\def\PyXragged{%
\leftskip=0pt plus \PyXFlushHAlign fil%
\rightskip=0pt plus 1fil%
\advance\rightskip0pt plus -\PyXFlushHAlign fil%
\parfillskip=0pt%
\pretolerance=9999%
\tolerance=9999%
\parindent=0pt%
\hyphenpenalty=9999%
\exhyphenpenalty=9999}%
\newbox\PyXBoxVBox%
\newdimen\PyXDimenVBox%
\newbox\PyXBoxVAlign%
\newdimen\PyXDimenVAlign%
\newdimen\PyXDimenVShift%
\long\def\ProcessPyXBox#1#2{%
\setbox\PyXBox=\hbox{{#1}}%
\PyXDimenHAlignLT=\PyXBoxHAlign\wd\PyXBox%
\PyXDimenHAlignRT=\wd\PyXBox%
\advance\PyXDimenHAlignRT by -\PyXDimenHAlignLT%
\gdef\PyXBoxHAlign{0}%
\immediate\write16{PyXBox:page=#2,lt=\the\PyXDimenHAlignLT,rt=\the\PyXDimenHAlignRT,ht=\the\ht\PyXBox,dp=\the\dp\PyXBox:}%
\setbox\PyXBoxHAligned=\hbox{\kern-\PyXDimenHAlignLT\box\PyXBox}%
\ht\PyXBoxHAligned0pt%
{\count0=80\count1=121\count2=88\count3=#2\shipout\box\PyXBoxHAligned}}%
\def\PyXInput#1{\immediate\write16{PyXInputMarker:executeid=#1:}}%
\def\PyXMarker#1{\hskip0pt\special{PyX:marker #1}}%%
\PyXInput{1}%
% This automatically generated file is part of PyX (http://pyx.sourceforge.net/).
% \latexstylename="10pt"
% \latexclassname="article"
% \latexclassopt="10pt"
% \latexinit=""
\def\tiny{\font\pyxfont=cmr5\pyxfont\font\pyxfonttfa=cmr5\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr5\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi5\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi5\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy5\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy5\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\scriptsize{\font\pyxfont=cmr7\pyxfont\font\pyxfonttfa=cmr7\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr5\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi7\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi5\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy7\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy5\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\footnotesize{\font\pyxfont=cmr8\pyxfont\font\pyxfonttfa=cmr8\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr6\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi8\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi6\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy8\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy6\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\small{\font\pyxfont=cmr9\pyxfont\font\pyxfonttfa=cmr9\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr6\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi9\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi6\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy9\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy6\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\normalsize{\font\pyxfont=cmr10\pyxfont\font\pyxfonttfa=cmr10\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr7\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi10\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi7\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy7\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\large{\font\pyxfont=cmr12\pyxfont\font\pyxfonttfa=cmr12\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr8\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr6\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi8\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi6\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 12.0pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy8\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy6\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\Large{\font\pyxfont=cmr12 at 14.4pt\pyxfont\font\pyxfonttfa=cmr12 at 14.4pt\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr10\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr7\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12 at 14.4pt\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi10\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi7\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 14.4pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy10\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy7\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\LARGE{\font\pyxfont=cmr17\pyxfont\font\pyxfonttfa=cmr17\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr12\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr10\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12 at 17.28pt\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi12\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi10\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 17.28pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy10 at 12.0pt\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy10\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\huge{\font\pyxfont=cmr17 at 20.74pt\pyxfont\font\pyxfonttfa=cmr17 at 20.74pt\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr12 at 14.4pt\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr12\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12 at 20.74pt\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi12 at 14.4pt\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi12\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 20.74pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy10 at 14.4pt\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy10 at 12.0pt\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\Huge{\font\pyxfont=cmr17 at 24.88pt\pyxfont\font\pyxfonttfa=cmr17 at 24.88pt\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr17 at 20.74pt\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr17\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12 at 24.88pt\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi12 at 20.74pt\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi12 at 17.28pt\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 24.88pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy10 at 20.74pt\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy10 at 17.28pt\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
%
\PyXInput{2}%
\normalsize%
%
\PyXInput{3}%
\newdimen\linewidth\newdimen\textwidth%
%
\PyXInput{4}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{2.5}$}}\lower\PyXDimenVShift\box0%
}{1}%
\PyXInput{5}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{5}$}}\lower\PyXDimenVShift\box0%
}{2}%
\PyXInput{6}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{7.5}$}}\lower\PyXDimenVShift\box0%
}{3}%
\PyXInput{7}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{10}$}}\lower\PyXDimenVShift\box0%
}{4}%
\PyXInput{8}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{12.5}$}}\lower\PyXDimenVShift\box0%
}{5}%
\PyXInput{9}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{15}$}}\lower\PyXDimenVShift\box0%
}{6}%
\PyXInput{10}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}SNR enhancement}}\lower\PyXDimenVShift\box0%
}{7}%
\PyXInput{11}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{5}$}}\lower\PyXDimenVShift\box0%
}{8}%
\PyXInput{12}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{10}$}}\lower\PyXDimenVShift\box0%
}{9}%
\PyXInput{13}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{15}$}}\lower\PyXDimenVShift\box0%
}{10}%
\PyXInput{14}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}SNR enhancement}}\lower\PyXDimenVShift\box0%
}{11}%
\PyXInput{15}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{2}$}}\lower\PyXDimenVShift\box0%
}{12}%
\PyXInput{16}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{4}$}}\lower\PyXDimenVShift\box0%
}{13}%
\PyXInput{17}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{6}$}}\lower\PyXDimenVShift\box0%
}{14}%
\PyXInput{18}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{8}$}}\lower\PyXDimenVShift\box0%
}{15}%
\PyXInput{19}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{10}$}}\lower\PyXDimenVShift\box0%
}{16}%
\PyXInput{20}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{12}$}}\lower\PyXDimenVShift\box0%
}{17}%
\PyXInput{21}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{14}$}}\lower\PyXDimenVShift\box0%
}{18}%
\PyXInput{22}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}SNR enhancement}}\lower\PyXDimenVShift\box0%
}{19}%
\PyXInput{23}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{0}}$}}\lower\PyXDimenVShift\box0%
}{20}%
\PyXInput{24}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{2.5}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{21}%
\PyXInput{25}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{5}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{22}%
\PyXInput{26}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{7.5}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{23}%
\PyXInput{27}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{1}\cdot10^{4}}}$}}\lower\PyXDimenVShift\box0%
}{24}%
\PyXInput{28}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}active Q}}\lower\PyXDimenVShift\box0%
}{25}%
\PyXInput{29}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{0}}$}}\lower\PyXDimenVShift\box0%
}{26}%
\PyXInput{30}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{2}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{27}%
\PyXInput{31}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{4}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{28}%
\PyXInput{32}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{6}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{29}%
\PyXInput{33}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{8}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{30}%
\PyXInput{34}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{1}\cdot10^{4}}}$}}\lower\PyXDimenVShift\box0%
}{31}%
\PyXInput{35}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}active Q}}\lower\PyXDimenVShift\box0%
}{32}%
\PyXInput{36}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{no delay}}\lower\PyXDimenVShift\box0%
}{33}%
\PyXInput{37}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{delay}}\lower\PyXDimenVShift\box0%
}{34}%
\PyXInput{38}%
\end%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% preparing restart of tex
% PyX 0.12.1 texdebug file
% mode: tex
% date: Sun Apr 12 01:58:25 2015
\scrollmode
\raiseerror%
\def\PyX{P\kern-.3em\lower.5ex\hbox{Y}\kern-.18em X}%
\gdef\PyXBoxHAlign{0}%
\newbox\PyXBox%
\newbox\PyXBoxHAligned%
\newdimen\PyXDimenHAlignLT%
\newdimen\PyXDimenHAlignRT%
\gdef\PyXFlushHAlign{0}%
\def\PyXragged{%
\leftskip=0pt plus \PyXFlushHAlign fil%
\rightskip=0pt plus 1fil%
\advance\rightskip0pt plus -\PyXFlushHAlign fil%
\parfillskip=0pt%
\pretolerance=9999%
\tolerance=9999%
\parindent=0pt%
\hyphenpenalty=9999%
\exhyphenpenalty=9999}%
\newbox\PyXBoxVBox%
\newdimen\PyXDimenVBox%
\newbox\PyXBoxVAlign%
\newdimen\PyXDimenVAlign%
\newdimen\PyXDimenVShift%
\long\def\ProcessPyXBox#1#2{%
\setbox\PyXBox=\hbox{{#1}}%
\PyXDimenHAlignLT=\PyXBoxHAlign\wd\PyXBox%
\PyXDimenHAlignRT=\wd\PyXBox%
\advance\PyXDimenHAlignRT by -\PyXDimenHAlignLT%
\gdef\PyXBoxHAlign{0}%
\immediate\write16{PyXBox:page=#2,lt=\the\PyXDimenHAlignLT,rt=\the\PyXDimenHAlignRT,ht=\the\ht\PyXBox,dp=\the\dp\PyXBox:}%
\setbox\PyXBoxHAligned=\hbox{\kern-\PyXDimenHAlignLT\box\PyXBox}%
\ht\PyXBoxHAligned0pt%
{\count0=80\count1=121\count2=88\count3=#2\shipout\box\PyXBoxHAligned}}%
\def\PyXInput#1{\immediate\write16{PyXInputMarker:executeid=#1:}}%
\def\PyXMarker#1{\hskip0pt\special{PyX:marker #1}}%%
\PyXInput{1}%
% This automatically generated file is part of PyX (http://pyx.sourceforge.net/).
% \latexstylename="10pt"
% \latexclassname="article"
% \latexclassopt="10pt"
% \latexinit=""
\def\tiny{\font\pyxfont=cmr5\pyxfont\font\pyxfonttfa=cmr5\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr5\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi5\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi5\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy5\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy5\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\scriptsize{\font\pyxfont=cmr7\pyxfont\font\pyxfonttfa=cmr7\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr5\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi7\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi5\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy7\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy5\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\footnotesize{\font\pyxfont=cmr8\pyxfont\font\pyxfonttfa=cmr8\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr6\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi8\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi6\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy8\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy6\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\small{\font\pyxfont=cmr9\pyxfont\font\pyxfonttfa=cmr9\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr6\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi9\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi6\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy9\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy6\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\normalsize{\font\pyxfont=cmr10\pyxfont\font\pyxfonttfa=cmr10\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr7\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi10\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi7\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy7\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\large{\font\pyxfont=cmr12\pyxfont\font\pyxfonttfa=cmr12\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr8\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr6\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi8\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi6\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 12.0pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy8\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy6\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\Large{\font\pyxfont=cmr12 at 14.4pt\pyxfont\font\pyxfonttfa=cmr12 at 14.4pt\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr10\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr7\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12 at 14.4pt\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi10\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi7\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 14.4pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy10\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy7\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\LARGE{\font\pyxfont=cmr17\pyxfont\font\pyxfonttfa=cmr17\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr12\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr10\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12 at 17.28pt\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi12\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi10\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 17.28pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy10 at 12.0pt\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy10\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\huge{\font\pyxfont=cmr17 at 20.74pt\pyxfont\font\pyxfonttfa=cmr17 at 20.74pt\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr12 at 14.4pt\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr12\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12 at 20.74pt\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi12 at 14.4pt\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi12\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 20.74pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy10 at 14.4pt\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy10 at 12.0pt\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\Huge{\font\pyxfont=cmr17 at 24.88pt\pyxfont\font\pyxfonttfa=cmr17 at 24.88pt\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr17 at 20.74pt\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr17\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12 at 24.88pt\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi12 at 20.74pt\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi12 at 17.28pt\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 24.88pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy10 at 20.74pt\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy10 at 17.28pt\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
%
\PyXInput{2}%
\normalsize%
%
\PyXInput{3}%
\newdimen\linewidth\newdimen\textwidth%
%
\PyXInput{4}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{2.5}$}}\lower\PyXDimenVShift\box0%
}{1}%
\PyXInput{5}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{5}$}}\lower\PyXDimenVShift\box0%
}{2}%
\PyXInput{6}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{7.5}$}}\lower\PyXDimenVShift\box0%
}{3}%
\PyXInput{7}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{10}$}}\lower\PyXDimenVShift\box0%
}{4}%
\PyXInput{8}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{12.5}$}}\lower\PyXDimenVShift\box0%
}{5}%
\PyXInput{9}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{15}$}}\lower\PyXDimenVShift\box0%
}{6}%
\PyXInput{10}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}cw SNR enhancement}}\lower\PyXDimenVShift\box0%
}{7}%
\PyXInput{11}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{5}$}}\lower\PyXDimenVShift\box0%
}{8}%
\PyXInput{12}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{10}$}}\lower\PyXDimenVShift\box0%
}{9}%
\PyXInput{13}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{15}$}}\lower\PyXDimenVShift\box0%
}{10}%
\PyXInput{14}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}cw SNR enhancement}}\lower\PyXDimenVShift\box0%
}{11}%
\PyXInput{15}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{2}$}}\lower\PyXDimenVShift\box0%
}{12}%
\PyXInput{16}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{4}$}}\lower\PyXDimenVShift\box0%
}{13}%
\PyXInput{17}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{6}$}}\lower\PyXDimenVShift\box0%
}{14}%
\PyXInput{18}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{8}$}}\lower\PyXDimenVShift\box0%
}{15}%
\PyXInput{19}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{10}$}}\lower\PyXDimenVShift\box0%
}{16}%
\PyXInput{20}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{12}$}}\lower\PyXDimenVShift\box0%
}{17}%
\PyXInput{21}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{14}$}}\lower\PyXDimenVShift\box0%
}{18}%
\PyXInput{22}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}cw SNR enhancement}}\lower\PyXDimenVShift\box0%
}{19}%
\PyXInput{23}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{0}}$}}\lower\PyXDimenVShift\box0%
}{20}%
\PyXInput{24}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{2.5}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{21}%
\PyXInput{25}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{5}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{22}%
\PyXInput{26}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{7.5}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{23}%
\PyXInput{27}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{1}\cdot10^{4}}}$}}\lower\PyXDimenVShift\box0%
}{24}%
\PyXInput{28}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}active Q}}\lower\PyXDimenVShift\box0%
}{25}%
\PyXInput{29}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{0}}$}}\lower\PyXDimenVShift\box0%
}{26}%
\PyXInput{30}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{2}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{27}%
\PyXInput{31}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{4}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{28}%
\PyXInput{32}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{6}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{29}%
\PyXInput{33}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{8}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{30}%
\PyXInput{34}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{1}\cdot10^{4}}}$}}\lower\PyXDimenVShift\box0%
}{31}%
\PyXInput{35}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}active Q}}\lower\PyXDimenVShift\box0%
}{32}%
\PyXInput{36}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{no delay}}\lower\PyXDimenVShift\box0%
}{33}%
\PyXInput{37}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{delay}}\lower\PyXDimenVShift\box0%
}{34}%
\PyXInput{38}%
\end%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% preparing restart of tex
% PyX 0.12.1 texdebug file
% mode: tex
% date: Sun Apr 12 01:59:29 2015
\scrollmode
\raiseerror%
\def\PyX{P\kern-.3em\lower.5ex\hbox{Y}\kern-.18em X}%
\gdef\PyXBoxHAlign{0}%
\newbox\PyXBox%
\newbox\PyXBoxHAligned%
\newdimen\PyXDimenHAlignLT%
\newdimen\PyXDimenHAlignRT%
\gdef\PyXFlushHAlign{0}%
\def\PyXragged{%
\leftskip=0pt plus \PyXFlushHAlign fil%
\rightskip=0pt plus 1fil%
\advance\rightskip0pt plus -\PyXFlushHAlign fil%
\parfillskip=0pt%
\pretolerance=9999%
\tolerance=9999%
\parindent=0pt%
\hyphenpenalty=9999%
\exhyphenpenalty=9999}%
\newbox\PyXBoxVBox%
\newdimen\PyXDimenVBox%
\newbox\PyXBoxVAlign%
\newdimen\PyXDimenVAlign%
\newdimen\PyXDimenVShift%
\long\def\ProcessPyXBox#1#2{%
\setbox\PyXBox=\hbox{{#1}}%
\PyXDimenHAlignLT=\PyXBoxHAlign\wd\PyXBox%
\PyXDimenHAlignRT=\wd\PyXBox%
\advance\PyXDimenHAlignRT by -\PyXDimenHAlignLT%
\gdef\PyXBoxHAlign{0}%
\immediate\write16{PyXBox:page=#2,lt=\the\PyXDimenHAlignLT,rt=\the\PyXDimenHAlignRT,ht=\the\ht\PyXBox,dp=\the\dp\PyXBox:}%
\setbox\PyXBoxHAligned=\hbox{\kern-\PyXDimenHAlignLT\box\PyXBox}%
\ht\PyXBoxHAligned0pt%
{\count0=80\count1=121\count2=88\count3=#2\shipout\box\PyXBoxHAligned}}%
\def\PyXInput#1{\immediate\write16{PyXInputMarker:executeid=#1:}}%
\def\PyXMarker#1{\hskip0pt\special{PyX:marker #1}}%%
\PyXInput{1}%
% This automatically generated file is part of PyX (http://pyx.sourceforge.net/).
% \latexstylename="10pt"
% \latexclassname="article"
% \latexclassopt="10pt"
% \latexinit=""
\def\tiny{\font\pyxfont=cmr5\pyxfont\font\pyxfonttfa=cmr5\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr5\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi5\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi5\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy5\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy5\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\scriptsize{\font\pyxfont=cmr7\pyxfont\font\pyxfonttfa=cmr7\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr5\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi7\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi5\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy7\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy5\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\footnotesize{\font\pyxfont=cmr8\pyxfont\font\pyxfonttfa=cmr8\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr6\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi8\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi6\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy8\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy6\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\small{\font\pyxfont=cmr9\pyxfont\font\pyxfonttfa=cmr9\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr6\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi9\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi6\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy9\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy6\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\normalsize{\font\pyxfont=cmr10\pyxfont\font\pyxfonttfa=cmr10\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr7\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi10\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi7\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy7\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\large{\font\pyxfont=cmr12\pyxfont\font\pyxfonttfa=cmr12\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr8\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr6\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi8\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi6\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 12.0pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy8\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy6\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\Large{\font\pyxfont=cmr12 at 14.4pt\pyxfont\font\pyxfonttfa=cmr12 at 14.4pt\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr10\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr7\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12 at 14.4pt\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi10\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi7\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 14.4pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy10\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy7\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\LARGE{\font\pyxfont=cmr17\pyxfont\font\pyxfonttfa=cmr17\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr12\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr10\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12 at 17.28pt\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi12\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi10\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 17.28pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy10 at 12.0pt\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy10\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\huge{\font\pyxfont=cmr17 at 20.74pt\pyxfont\font\pyxfonttfa=cmr17 at 20.74pt\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr12 at 14.4pt\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr12\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12 at 20.74pt\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi12 at 14.4pt\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi12\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 20.74pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy10 at 14.4pt\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy10 at 12.0pt\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\Huge{\font\pyxfont=cmr17 at 24.88pt\pyxfont\font\pyxfonttfa=cmr17 at 24.88pt\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr17 at 20.74pt\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr17\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12 at 24.88pt\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi12 at 20.74pt\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi12 at 17.28pt\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 24.88pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy10 at 20.74pt\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy10 at 17.28pt\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
%
\PyXInput{2}%
\normalsize%
%
\PyXInput{3}%
\newdimen\linewidth\newdimen\textwidth%
%
\PyXInput{4}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{2.5}$}}\lower\PyXDimenVShift\box0%
}{1}%
\PyXInput{5}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{5}$}}\lower\PyXDimenVShift\box0%
}{2}%
\PyXInput{6}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{7.5}$}}\lower\PyXDimenVShift\box0%
}{3}%
\PyXInput{7}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{10}$}}\lower\PyXDimenVShift\box0%
}{4}%
\PyXInput{8}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{12.5}$}}\lower\PyXDimenVShift\box0%
}{5}%
\PyXInput{9}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{15}$}}\lower\PyXDimenVShift\box0%
}{6}%
\PyXInput{10}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}cw SNR enhancement}}\lower\PyXDimenVShift\box0%
}{7}%
\PyXInput{11}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{5}$}}\lower\PyXDimenVShift\box0%
}{8}%
\PyXInput{12}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{10}$}}\lower\PyXDimenVShift\box0%
}{9}%
\PyXInput{13}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{15}$}}\lower\PyXDimenVShift\box0%
}{10}%
\PyXInput{14}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}cw SNR enhancement}}\lower\PyXDimenVShift\box0%
}{11}%
\PyXInput{15}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{2}$}}\lower\PyXDimenVShift\box0%
}{12}%
\PyXInput{16}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{4}$}}\lower\PyXDimenVShift\box0%
}{13}%
\PyXInput{17}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{6}$}}\lower\PyXDimenVShift\box0%
}{14}%
\PyXInput{18}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{8}$}}\lower\PyXDimenVShift\box0%
}{15}%
\PyXInput{19}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{10}$}}\lower\PyXDimenVShift\box0%
}{16}%
\PyXInput{20}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{12}$}}\lower\PyXDimenVShift\box0%
}{17}%
\PyXInput{21}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{14}$}}\lower\PyXDimenVShift\box0%
}{18}%
\PyXInput{22}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}cw SNR enhancement}}\lower\PyXDimenVShift\box0%
}{19}%
\PyXInput{23}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{0}}$}}\lower\PyXDimenVShift\box0%
}{20}%
\PyXInput{24}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{2.5}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{21}%
\PyXInput{25}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{5}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{22}%
\PyXInput{26}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{7.5}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{23}%
\PyXInput{27}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{1}\cdot10^{4}}}$}}\lower\PyXDimenVShift\box0%
}{24}%
\PyXInput{28}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}active Q}}\lower\PyXDimenVShift\box0%
}{25}%
\PyXInput{29}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{0}}$}}\lower\PyXDimenVShift\box0%
}{26}%
\PyXInput{30}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{2}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{27}%
\PyXInput{31}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{4}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{28}%
\PyXInput{32}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{6}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{29}%
\PyXInput{33}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{8}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{30}%
\PyXInput{34}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{1}\cdot10^{4}}}$}}\lower\PyXDimenVShift\box0%
}{31}%
\PyXInput{35}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}active Q}}\lower\PyXDimenVShift\box0%
}{32}%
\PyXInput{36}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{delay}}\lower\PyXDimenVShift\box0%
}{33}%
\PyXInput{37}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{no delay}}\lower\PyXDimenVShift\box0%
}{34}%
\PyXInput{38}%
\end%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% preparing restart of tex
% PyX 0.12.1 texdebug file
% mode: tex
% date: Sun Apr 12 02:13:31 2015
\scrollmode
\raiseerror%
\def\PyX{P\kern-.3em\lower.5ex\hbox{Y}\kern-.18em X}%
\gdef\PyXBoxHAlign{0}%
\newbox\PyXBox%
\newbox\PyXBoxHAligned%
\newdimen\PyXDimenHAlignLT%
\newdimen\PyXDimenHAlignRT%
\gdef\PyXFlushHAlign{0}%
\def\PyXragged{%
\leftskip=0pt plus \PyXFlushHAlign fil%
\rightskip=0pt plus 1fil%
\advance\rightskip0pt plus -\PyXFlushHAlign fil%
\parfillskip=0pt%
\pretolerance=9999%
\tolerance=9999%
\parindent=0pt%
\hyphenpenalty=9999%
\exhyphenpenalty=9999}%
\newbox\PyXBoxVBox%
\newdimen\PyXDimenVBox%
\newbox\PyXBoxVAlign%
\newdimen\PyXDimenVAlign%
\newdimen\PyXDimenVShift%
\long\def\ProcessPyXBox#1#2{%
\setbox\PyXBox=\hbox{{#1}}%
\PyXDimenHAlignLT=\PyXBoxHAlign\wd\PyXBox%
\PyXDimenHAlignRT=\wd\PyXBox%
\advance\PyXDimenHAlignRT by -\PyXDimenHAlignLT%
\gdef\PyXBoxHAlign{0}%
\immediate\write16{PyXBox:page=#2,lt=\the\PyXDimenHAlignLT,rt=\the\PyXDimenHAlignRT,ht=\the\ht\PyXBox,dp=\the\dp\PyXBox:}%
\setbox\PyXBoxHAligned=\hbox{\kern-\PyXDimenHAlignLT\box\PyXBox}%
\ht\PyXBoxHAligned0pt%
{\count0=80\count1=121\count2=88\count3=#2\shipout\box\PyXBoxHAligned}}%
\def\PyXInput#1{\immediate\write16{PyXInputMarker:executeid=#1:}}%
\def\PyXMarker#1{\hskip0pt\special{PyX:marker #1}}%%
\PyXInput{1}%
% This automatically generated file is part of PyX (http://pyx.sourceforge.net/).
% \latexstylename="10pt"
% \latexclassname="article"
% \latexclassopt="10pt"
% \latexinit=""
\def\tiny{\font\pyxfont=cmr5\pyxfont\font\pyxfonttfa=cmr5\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr5\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi5\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi5\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy5\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy5\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\scriptsize{\font\pyxfont=cmr7\pyxfont\font\pyxfonttfa=cmr7\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr5\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi7\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi5\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy7\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy5\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\footnotesize{\font\pyxfont=cmr8\pyxfont\font\pyxfonttfa=cmr8\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr6\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi8\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi6\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy8\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy6\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\small{\font\pyxfont=cmr9\pyxfont\font\pyxfonttfa=cmr9\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr6\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi9\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi6\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy9\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy6\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\normalsize{\font\pyxfont=cmr10\pyxfont\font\pyxfonttfa=cmr10\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr7\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi10\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi7\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy7\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\large{\font\pyxfont=cmr12\pyxfont\font\pyxfonttfa=cmr12\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr8\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr6\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi8\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi6\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 12.0pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy8\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy6\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\Large{\font\pyxfont=cmr12 at 14.4pt\pyxfont\font\pyxfonttfa=cmr12 at 14.4pt\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr10\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr7\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12 at 14.4pt\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi10\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi7\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 14.4pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy10\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy7\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\LARGE{\font\pyxfont=cmr17\pyxfont\font\pyxfonttfa=cmr17\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr12\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr10\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12 at 17.28pt\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi12\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi10\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 17.28pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy10 at 12.0pt\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy10\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\huge{\font\pyxfont=cmr17 at 20.74pt\pyxfont\font\pyxfonttfa=cmr17 at 20.74pt\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr12 at 14.4pt\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr12\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12 at 20.74pt\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi12 at 14.4pt\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi12\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 20.74pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy10 at 14.4pt\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy10 at 12.0pt\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\Huge{\font\pyxfont=cmr17 at 24.88pt\pyxfont\font\pyxfonttfa=cmr17 at 24.88pt\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr17 at 20.74pt\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr17\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12 at 24.88pt\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi12 at 20.74pt\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi12 at 17.28pt\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 24.88pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy10 at 20.74pt\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy10 at 17.28pt\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
%
\PyXInput{2}%
\normalsize%
%
\PyXInput{3}%
\newdimen\linewidth\newdimen\textwidth%
%
\PyXInput{4}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{2.5}$}}\lower\PyXDimenVShift\box0%
}{1}%
\PyXInput{5}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{5}$}}\lower\PyXDimenVShift\box0%
}{2}%
\PyXInput{6}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{7.5}$}}\lower\PyXDimenVShift\box0%
}{3}%
\PyXInput{7}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{10}$}}\lower\PyXDimenVShift\box0%
}{4}%
\PyXInput{8}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{12.5}$}}\lower\PyXDimenVShift\box0%
}{5}%
\PyXInput{9}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{15}$}}\lower\PyXDimenVShift\box0%
}{6}%
\PyXInput{10}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}cw SNR enhancement}}\lower\PyXDimenVShift\box0%
}{7}%
\PyXInput{11}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{5}$}}\lower\PyXDimenVShift\box0%
}{8}%
\PyXInput{12}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{10}$}}\lower\PyXDimenVShift\box0%
}{9}%
\PyXInput{13}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{15}$}}\lower\PyXDimenVShift\box0%
}{10}%
\PyXInput{14}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}cw SNR enhancement}}\lower\PyXDimenVShift\box0%
}{11}%
\PyXInput{15}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{2}$}}\lower\PyXDimenVShift\box0%
}{12}%
\PyXInput{16}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{4}$}}\lower\PyXDimenVShift\box0%
}{13}%
\PyXInput{17}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{6}$}}\lower\PyXDimenVShift\box0%
}{14}%
\PyXInput{18}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{8}$}}\lower\PyXDimenVShift\box0%
}{15}%
\PyXInput{19}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{10}$}}\lower\PyXDimenVShift\box0%
}{16}%
\PyXInput{20}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{12}$}}\lower\PyXDimenVShift\box0%
}{17}%
\PyXInput{21}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{14}$}}\lower\PyXDimenVShift\box0%
}{18}%
\PyXInput{22}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}cw SNR enhancement}}\lower\PyXDimenVShift\box0%
}{19}%
\PyXInput{23}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{2}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{20}%
\PyXInput{24}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{4}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{21}%
\PyXInput{25}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{6}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{22}%
\PyXInput{26}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{8}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{23}%
\PyXInput{27}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{1}\cdot10^{4}}}$}}\lower\PyXDimenVShift\box0%
}{24}%
\PyXInput{28}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}active Q}}\lower\PyXDimenVShift\box0%
}{25}%
\PyXInput{29}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{2.5}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{26}%
\PyXInput{30}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{5}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{27}%
\PyXInput{31}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{7.5}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{28}%
\PyXInput{32}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{1}\cdot10^{4}}}$}}\lower\PyXDimenVShift\box0%
}{29}%
\PyXInput{33}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}active Q}}\lower\PyXDimenVShift\box0%
}{30}%
\PyXInput{34}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{delay}}\lower\PyXDimenVShift\box0%
}{31}%
\PyXInput{35}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{no delay}}\lower\PyXDimenVShift\box0%
}{32}%
\PyXInput{36}%
\end%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% preparing restart of tex
% PyX 0.12.1 texdebug file
% mode: tex
% date: Sun Apr 12 02:14:16 2015
\scrollmode
\raiseerror%
\def\PyX{P\kern-.3em\lower.5ex\hbox{Y}\kern-.18em X}%
\gdef\PyXBoxHAlign{0}%
\newbox\PyXBox%
\newbox\PyXBoxHAligned%
\newdimen\PyXDimenHAlignLT%
\newdimen\PyXDimenHAlignRT%
\gdef\PyXFlushHAlign{0}%
\def\PyXragged{%
\leftskip=0pt plus \PyXFlushHAlign fil%
\rightskip=0pt plus 1fil%
\advance\rightskip0pt plus -\PyXFlushHAlign fil%
\parfillskip=0pt%
\pretolerance=9999%
\tolerance=9999%
\parindent=0pt%
\hyphenpenalty=9999%
\exhyphenpenalty=9999}%
\newbox\PyXBoxVBox%
\newdimen\PyXDimenVBox%
\newbox\PyXBoxVAlign%
\newdimen\PyXDimenVAlign%
\newdimen\PyXDimenVShift%
\long\def\ProcessPyXBox#1#2{%
\setbox\PyXBox=\hbox{{#1}}%
\PyXDimenHAlignLT=\PyXBoxHAlign\wd\PyXBox%
\PyXDimenHAlignRT=\wd\PyXBox%
\advance\PyXDimenHAlignRT by -\PyXDimenHAlignLT%
\gdef\PyXBoxHAlign{0}%
\immediate\write16{PyXBox:page=#2,lt=\the\PyXDimenHAlignLT,rt=\the\PyXDimenHAlignRT,ht=\the\ht\PyXBox,dp=\the\dp\PyXBox:}%
\setbox\PyXBoxHAligned=\hbox{\kern-\PyXDimenHAlignLT\box\PyXBox}%
\ht\PyXBoxHAligned0pt%
{\count0=80\count1=121\count2=88\count3=#2\shipout\box\PyXBoxHAligned}}%
\def\PyXInput#1{\immediate\write16{PyXInputMarker:executeid=#1:}}%
\def\PyXMarker#1{\hskip0pt\special{PyX:marker #1}}%%
\PyXInput{1}%
% This automatically generated file is part of PyX (http://pyx.sourceforge.net/).
% \latexstylename="10pt"
% \latexclassname="article"
% \latexclassopt="10pt"
% \latexinit=""
\def\tiny{\font\pyxfont=cmr5\pyxfont\font\pyxfonttfa=cmr5\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr5\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi5\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi5\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy5\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy5\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\scriptsize{\font\pyxfont=cmr7\pyxfont\font\pyxfonttfa=cmr7\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr5\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi7\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi5\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy7\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy5\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\footnotesize{\font\pyxfont=cmr8\pyxfont\font\pyxfonttfa=cmr8\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr6\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi8\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi6\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy8\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy6\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\small{\font\pyxfont=cmr9\pyxfont\font\pyxfonttfa=cmr9\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr6\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi9\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi6\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy9\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy6\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\normalsize{\font\pyxfont=cmr10\pyxfont\font\pyxfonttfa=cmr10\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr7\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi10\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi7\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy7\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\large{\font\pyxfont=cmr12\pyxfont\font\pyxfonttfa=cmr12\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr8\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr6\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi8\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi6\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 12.0pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy8\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy6\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\Large{\font\pyxfont=cmr12 at 14.4pt\pyxfont\font\pyxfonttfa=cmr12 at 14.4pt\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr10\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr7\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12 at 14.4pt\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi10\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi7\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 14.4pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy10\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy7\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\LARGE{\font\pyxfont=cmr17\pyxfont\font\pyxfonttfa=cmr17\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr12\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr10\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12 at 17.28pt\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi12\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi10\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 17.28pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy10 at 12.0pt\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy10\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\huge{\font\pyxfont=cmr17 at 20.74pt\pyxfont\font\pyxfonttfa=cmr17 at 20.74pt\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr12 at 14.4pt\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr12\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12 at 20.74pt\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi12 at 14.4pt\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi12\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 20.74pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy10 at 14.4pt\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy10 at 12.0pt\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\Huge{\font\pyxfont=cmr17 at 24.88pt\pyxfont\font\pyxfonttfa=cmr17 at 24.88pt\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr17 at 20.74pt\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr17\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12 at 24.88pt\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi12 at 20.74pt\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi12 at 17.28pt\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 24.88pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy10 at 20.74pt\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy10 at 17.28pt\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
%
\PyXInput{2}%
\normalsize%
%
\PyXInput{3}%
\newdimen\linewidth\newdimen\textwidth%
%
\PyXInput{4}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{2.5}$}}\lower\PyXDimenVShift\box0%
}{1}%
\PyXInput{5}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{5}$}}\lower\PyXDimenVShift\box0%
}{2}%
\PyXInput{6}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{7.5}$}}\lower\PyXDimenVShift\box0%
}{3}%
\PyXInput{7}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{10}$}}\lower\PyXDimenVShift\box0%
}{4}%
\PyXInput{8}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{12.5}$}}\lower\PyXDimenVShift\box0%
}{5}%
\PyXInput{9}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{15}$}}\lower\PyXDimenVShift\box0%
}{6}%
\PyXInput{10}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}cw SNR enhancement}}\lower\PyXDimenVShift\box0%
}{7}%
\PyXInput{11}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{5}$}}\lower\PyXDimenVShift\box0%
}{8}%
\PyXInput{12}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{10}$}}\lower\PyXDimenVShift\box0%
}{9}%
\PyXInput{13}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{15}$}}\lower\PyXDimenVShift\box0%
}{10}%
\PyXInput{14}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}cw SNR enhancement}}\lower\PyXDimenVShift\box0%
}{11}%
\PyXInput{15}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{2}$}}\lower\PyXDimenVShift\box0%
}{12}%
\PyXInput{16}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{4}$}}\lower\PyXDimenVShift\box0%
}{13}%
\PyXInput{17}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{6}$}}\lower\PyXDimenVShift\box0%
}{14}%
\PyXInput{18}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{8}$}}\lower\PyXDimenVShift\box0%
}{15}%
\PyXInput{19}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{10}$}}\lower\PyXDimenVShift\box0%
}{16}%
\PyXInput{20}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{12}$}}\lower\PyXDimenVShift\box0%
}{17}%
\PyXInput{21}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{14}$}}\lower\PyXDimenVShift\box0%
}{18}%
\PyXInput{22}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}cw SNR enhancement}}\lower\PyXDimenVShift\box0%
}{19}%
\PyXInput{23}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{2}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{20}%
\PyXInput{24}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{4}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{21}%
\PyXInput{25}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{6}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{22}%
\PyXInput{26}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{8}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{23}%
\PyXInput{27}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{1}\cdot10^{4}}}$}}\lower\PyXDimenVShift\box0%
}{24}%
\PyXInput{28}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}active Q}}\lower\PyXDimenVShift\box0%
}{25}%
\PyXInput{29}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{2.5}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{26}%
\PyXInput{30}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{5}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{27}%
\PyXInput{31}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{7.5}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{28}%
\PyXInput{32}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{1}\cdot10^{4}}}$}}\lower\PyXDimenVShift\box0%
}{29}%
\PyXInput{33}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}active Q}}\lower\PyXDimenVShift\box0%
}{30}%
\PyXInput{34}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{delay}}\lower\PyXDimenVShift\box0%
}{31}%
\PyXInput{35}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{no delay}}\lower\PyXDimenVShift\box0%
}{32}%
\PyXInput{36}%
\end%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% preparing restart of tex
% PyX 0.12.1 texdebug file
% mode: tex
% date: Sun Apr 12 02:15:05 2015
\scrollmode
\raiseerror%
\def\PyX{P\kern-.3em\lower.5ex\hbox{Y}\kern-.18em X}%
\gdef\PyXBoxHAlign{0}%
\newbox\PyXBox%
\newbox\PyXBoxHAligned%
\newdimen\PyXDimenHAlignLT%
\newdimen\PyXDimenHAlignRT%
\gdef\PyXFlushHAlign{0}%
\def\PyXragged{%
\leftskip=0pt plus \PyXFlushHAlign fil%
\rightskip=0pt plus 1fil%
\advance\rightskip0pt plus -\PyXFlushHAlign fil%
\parfillskip=0pt%
\pretolerance=9999%
\tolerance=9999%
\parindent=0pt%
\hyphenpenalty=9999%
\exhyphenpenalty=9999}%
\newbox\PyXBoxVBox%
\newdimen\PyXDimenVBox%
\newbox\PyXBoxVAlign%
\newdimen\PyXDimenVAlign%
\newdimen\PyXDimenVShift%
\long\def\ProcessPyXBox#1#2{%
\setbox\PyXBox=\hbox{{#1}}%
\PyXDimenHAlignLT=\PyXBoxHAlign\wd\PyXBox%
\PyXDimenHAlignRT=\wd\PyXBox%
\advance\PyXDimenHAlignRT by -\PyXDimenHAlignLT%
\gdef\PyXBoxHAlign{0}%
\immediate\write16{PyXBox:page=#2,lt=\the\PyXDimenHAlignLT,rt=\the\PyXDimenHAlignRT,ht=\the\ht\PyXBox,dp=\the\dp\PyXBox:}%
\setbox\PyXBoxHAligned=\hbox{\kern-\PyXDimenHAlignLT\box\PyXBox}%
\ht\PyXBoxHAligned0pt%
{\count0=80\count1=121\count2=88\count3=#2\shipout\box\PyXBoxHAligned}}%
\def\PyXInput#1{\immediate\write16{PyXInputMarker:executeid=#1:}}%
\def\PyXMarker#1{\hskip0pt\special{PyX:marker #1}}%%
\PyXInput{1}%
% This automatically generated file is part of PyX (http://pyx.sourceforge.net/).
% \latexstylename="10pt"
% \latexclassname="article"
% \latexclassopt="10pt"
% \latexinit=""
\def\tiny{\font\pyxfont=cmr5\pyxfont\font\pyxfonttfa=cmr5\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr5\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi5\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi5\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy5\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy5\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\scriptsize{\font\pyxfont=cmr7\pyxfont\font\pyxfonttfa=cmr7\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr5\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi7\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi5\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy7\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy5\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\footnotesize{\font\pyxfont=cmr8\pyxfont\font\pyxfonttfa=cmr8\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr6\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi8\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi6\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy8\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy6\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\small{\font\pyxfont=cmr9\pyxfont\font\pyxfonttfa=cmr9\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr6\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi9\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi6\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy9\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy6\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\normalsize{\font\pyxfont=cmr10\pyxfont\font\pyxfonttfa=cmr10\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr7\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi10\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi7\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy7\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\large{\font\pyxfont=cmr12\pyxfont\font\pyxfonttfa=cmr12\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr8\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr6\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi8\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi6\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 12.0pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy8\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy6\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\Large{\font\pyxfont=cmr12 at 14.4pt\pyxfont\font\pyxfonttfa=cmr12 at 14.4pt\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr10\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr7\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12 at 14.4pt\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi10\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi7\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 14.4pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy10\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy7\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\LARGE{\font\pyxfont=cmr17\pyxfont\font\pyxfonttfa=cmr17\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr12\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr10\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12 at 17.28pt\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi12\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi10\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 17.28pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy10 at 12.0pt\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy10\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\huge{\font\pyxfont=cmr17 at 20.74pt\pyxfont\font\pyxfonttfa=cmr17 at 20.74pt\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr12 at 14.4pt\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr12\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12 at 20.74pt\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi12 at 14.4pt\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi12\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 20.74pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy10 at 14.4pt\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy10 at 12.0pt\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\Huge{\font\pyxfont=cmr17 at 24.88pt\pyxfont\font\pyxfonttfa=cmr17 at 24.88pt\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr17 at 20.74pt\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr17\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12 at 24.88pt\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi12 at 20.74pt\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi12 at 17.28pt\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 24.88pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy10 at 20.74pt\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy10 at 17.28pt\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
%
\PyXInput{2}%
\normalsize%
%
\PyXInput{3}%
\newdimen\linewidth\newdimen\textwidth%
%
\PyXInput{4}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{2.5}$}}\lower\PyXDimenVShift\box0%
}{1}%
\PyXInput{5}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{5}$}}\lower\PyXDimenVShift\box0%
}{2}%
\PyXInput{6}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{7.5}$}}\lower\PyXDimenVShift\box0%
}{3}%
\PyXInput{7}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{10}$}}\lower\PyXDimenVShift\box0%
}{4}%
\PyXInput{8}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{12.5}$}}\lower\PyXDimenVShift\box0%
}{5}%
\PyXInput{9}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{15}$}}\lower\PyXDimenVShift\box0%
}{6}%
\PyXInput{10}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}cw SNR enhancement}}\lower\PyXDimenVShift\box0%
}{7}%
\PyXInput{11}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{5}$}}\lower\PyXDimenVShift\box0%
}{8}%
\PyXInput{12}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{10}$}}\lower\PyXDimenVShift\box0%
}{9}%
\PyXInput{13}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{15}$}}\lower\PyXDimenVShift\box0%
}{10}%
\PyXInput{14}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}cw SNR enhancement}}\lower\PyXDimenVShift\box0%
}{11}%
\PyXInput{15}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{2}$}}\lower\PyXDimenVShift\box0%
}{12}%
\PyXInput{16}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{4}$}}\lower\PyXDimenVShift\box0%
}{13}%
\PyXInput{17}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{6}$}}\lower\PyXDimenVShift\box0%
}{14}%
\PyXInput{18}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{8}$}}\lower\PyXDimenVShift\box0%
}{15}%
\PyXInput{19}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{10}$}}\lower\PyXDimenVShift\box0%
}{16}%
\PyXInput{20}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{12}$}}\lower\PyXDimenVShift\box0%
}{17}%
\PyXInput{21}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{14}$}}\lower\PyXDimenVShift\box0%
}{18}%
\PyXInput{22}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}cw SNR enhancement}}\lower\PyXDimenVShift\box0%
}{19}%
\PyXInput{23}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{2}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{20}%
\PyXInput{24}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{4}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{21}%
\PyXInput{25}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{6}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{22}%
\PyXInput{26}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{8}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{23}%
\PyXInput{27}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{1}\cdot10^{4}}}$}}\lower\PyXDimenVShift\box0%
}{24}%
\PyXInput{28}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}active Q}}\lower\PyXDimenVShift\box0%
}{25}%
\PyXInput{29}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{2.5}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{26}%
\PyXInput{30}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{5}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{27}%
\PyXInput{31}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{7.5}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{28}%
\PyXInput{32}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{1}\cdot10^{4}}}$}}\lower\PyXDimenVShift\box0%
}{29}%
\PyXInput{33}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}active Q}}\lower\PyXDimenVShift\box0%
}{30}%
\PyXInput{34}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{delay}}\lower\PyXDimenVShift\box0%
}{31}%
\PyXInput{35}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{no delay}}\lower\PyXDimenVShift\box0%
}{32}%
\PyXInput{36}%
\end%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% preparing restart of tex
% PyX 0.12.1 texdebug file
% mode: tex
% date: Sun Apr 12 02:16:08 2015
\scrollmode
\raiseerror%
\def\PyX{P\kern-.3em\lower.5ex\hbox{Y}\kern-.18em X}%
\gdef\PyXBoxHAlign{0}%
\newbox\PyXBox%
\newbox\PyXBoxHAligned%
\newdimen\PyXDimenHAlignLT%
\newdimen\PyXDimenHAlignRT%
\gdef\PyXFlushHAlign{0}%
\def\PyXragged{%
\leftskip=0pt plus \PyXFlushHAlign fil%
\rightskip=0pt plus 1fil%
\advance\rightskip0pt plus -\PyXFlushHAlign fil%
\parfillskip=0pt%
\pretolerance=9999%
\tolerance=9999%
\parindent=0pt%
\hyphenpenalty=9999%
\exhyphenpenalty=9999}%
\newbox\PyXBoxVBox%
\newdimen\PyXDimenVBox%
\newbox\PyXBoxVAlign%
\newdimen\PyXDimenVAlign%
\newdimen\PyXDimenVShift%
\long\def\ProcessPyXBox#1#2{%
\setbox\PyXBox=\hbox{{#1}}%
\PyXDimenHAlignLT=\PyXBoxHAlign\wd\PyXBox%
\PyXDimenHAlignRT=\wd\PyXBox%
\advance\PyXDimenHAlignRT by -\PyXDimenHAlignLT%
\gdef\PyXBoxHAlign{0}%
\immediate\write16{PyXBox:page=#2,lt=\the\PyXDimenHAlignLT,rt=\the\PyXDimenHAlignRT,ht=\the\ht\PyXBox,dp=\the\dp\PyXBox:}%
\setbox\PyXBoxHAligned=\hbox{\kern-\PyXDimenHAlignLT\box\PyXBox}%
\ht\PyXBoxHAligned0pt%
{\count0=80\count1=121\count2=88\count3=#2\shipout\box\PyXBoxHAligned}}%
\def\PyXInput#1{\immediate\write16{PyXInputMarker:executeid=#1:}}%
\def\PyXMarker#1{\hskip0pt\special{PyX:marker #1}}%%
\PyXInput{1}%
% This automatically generated file is part of PyX (http://pyx.sourceforge.net/).
% \latexstylename="10pt"
% \latexclassname="article"
% \latexclassopt="10pt"
% \latexinit=""
\def\tiny{\font\pyxfont=cmr5\pyxfont\font\pyxfonttfa=cmr5\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr5\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi5\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi5\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy5\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy5\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\scriptsize{\font\pyxfont=cmr7\pyxfont\font\pyxfonttfa=cmr7\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr5\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi7\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi5\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy7\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy5\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\footnotesize{\font\pyxfont=cmr8\pyxfont\font\pyxfonttfa=cmr8\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr6\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi8\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi6\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy8\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy6\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\small{\font\pyxfont=cmr9\pyxfont\font\pyxfonttfa=cmr9\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr6\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi9\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi6\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy9\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy6\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\normalsize{\font\pyxfont=cmr10\pyxfont\font\pyxfonttfa=cmr10\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr7\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi10\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi7\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy7\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\large{\font\pyxfont=cmr12\pyxfont\font\pyxfonttfa=cmr12\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr8\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr6\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi8\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi6\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 12.0pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy8\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy6\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\Large{\font\pyxfont=cmr12 at 14.4pt\pyxfont\font\pyxfonttfa=cmr12 at 14.4pt\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr10\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr7\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12 at 14.4pt\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi10\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi7\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 14.4pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy10\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy7\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\LARGE{\font\pyxfont=cmr17\pyxfont\font\pyxfonttfa=cmr17\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr12\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr10\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12 at 17.28pt\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi12\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi10\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 17.28pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy10 at 12.0pt\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy10\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\huge{\font\pyxfont=cmr17 at 20.74pt\pyxfont\font\pyxfonttfa=cmr17 at 20.74pt\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr12 at 14.4pt\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr12\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12 at 20.74pt\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi12 at 14.4pt\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi12\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 20.74pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy10 at 14.4pt\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy10 at 12.0pt\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\Huge{\font\pyxfont=cmr17 at 24.88pt\pyxfont\font\pyxfonttfa=cmr17 at 24.88pt\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr17 at 20.74pt\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr17\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12 at 24.88pt\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi12 at 20.74pt\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi12 at 17.28pt\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 24.88pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy10 at 20.74pt\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy10 at 17.28pt\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
%
\PyXInput{2}%
\normalsize%
%
\PyXInput{3}%
\newdimen\linewidth\newdimen\textwidth%
%
\PyXInput{4}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{1}$}}\lower\PyXDimenVShift\box0%
}{1}%
\PyXInput{5}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{2}$}}\lower\PyXDimenVShift\box0%
}{2}%
\PyXInput{6}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{5}$}}\lower\PyXDimenVShift\box0%
}{3}%
\PyXInput{7}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{10}$}}\lower\PyXDimenVShift\box0%
}{4}%
\PyXInput{8}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}cw SNR enhancement}}\lower\PyXDimenVShift\box0%
}{5}%
\PyXInput{9}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{0}$}}\lower\PyXDimenVShift\box0%
}{6}%
\PyXInput{10}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{0.25}$}}\lower\PyXDimenVShift\box0%
}{7}%
\PyXInput{11}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{0.5}$}}\lower\PyXDimenVShift\box0%
}{8}%
\PyXInput{12}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{0.75}$}}\lower\PyXDimenVShift\box0%
}{9}%
\PyXInput{13}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{1}$}}\lower\PyXDimenVShift\box0%
}{10}%
\PyXInput{14}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}closed loop gain}}\lower\PyXDimenVShift\box0%
}{11}%
\PyXInput{15}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{0}$}}\lower\PyXDimenVShift\box0%
}{12}%
\PyXInput{16}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{0.2}$}}\lower\PyXDimenVShift\box0%
}{13}%
\PyXInput{17}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{0.4}$}}\lower\PyXDimenVShift\box0%
}{14}%
\PyXInput{18}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{0.6}$}}\lower\PyXDimenVShift\box0%
}{15}%
\PyXInput{19}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{0.8}$}}\lower\PyXDimenVShift\box0%
}{16}%
\PyXInput{20}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{1}$}}\lower\PyXDimenVShift\box0%
}{17}%
\PyXInput{21}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}closed loop gain}}\lower\PyXDimenVShift\box0%
}{18}%
\PyXInput{22}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{theory}}\lower\PyXDimenVShift\box0%
}{19}%
\PyXInput{23}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{exp.}}\lower\PyXDimenVShift\box0%
}{20}%
\PyXInput{24}%
\end%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% preparing restart of tex
% PyX 0.12.1 texdebug file
% mode: tex
% date: Sun Apr 12 02:17:15 2015
\scrollmode
\raiseerror%
\def\PyX{P\kern-.3em\lower.5ex\hbox{Y}\kern-.18em X}%
\gdef\PyXBoxHAlign{0}%
\newbox\PyXBox%
\newbox\PyXBoxHAligned%
\newdimen\PyXDimenHAlignLT%
\newdimen\PyXDimenHAlignRT%
\gdef\PyXFlushHAlign{0}%
\def\PyXragged{%
\leftskip=0pt plus \PyXFlushHAlign fil%
\rightskip=0pt plus 1fil%
\advance\rightskip0pt plus -\PyXFlushHAlign fil%
\parfillskip=0pt%
\pretolerance=9999%
\tolerance=9999%
\parindent=0pt%
\hyphenpenalty=9999%
\exhyphenpenalty=9999}%
\newbox\PyXBoxVBox%
\newdimen\PyXDimenVBox%
\newbox\PyXBoxVAlign%
\newdimen\PyXDimenVAlign%
\newdimen\PyXDimenVShift%
\long\def\ProcessPyXBox#1#2{%
\setbox\PyXBox=\hbox{{#1}}%
\PyXDimenHAlignLT=\PyXBoxHAlign\wd\PyXBox%
\PyXDimenHAlignRT=\wd\PyXBox%
\advance\PyXDimenHAlignRT by -\PyXDimenHAlignLT%
\gdef\PyXBoxHAlign{0}%
\immediate\write16{PyXBox:page=#2,lt=\the\PyXDimenHAlignLT,rt=\the\PyXDimenHAlignRT,ht=\the\ht\PyXBox,dp=\the\dp\PyXBox:}%
\setbox\PyXBoxHAligned=\hbox{\kern-\PyXDimenHAlignLT\box\PyXBox}%
\ht\PyXBoxHAligned0pt%
{\count0=80\count1=121\count2=88\count3=#2\shipout\box\PyXBoxHAligned}}%
\def\PyXInput#1{\immediate\write16{PyXInputMarker:executeid=#1:}}%
\def\PyXMarker#1{\hskip0pt\special{PyX:marker #1}}%%
\PyXInput{1}%
% This automatically generated file is part of PyX (http://pyx.sourceforge.net/).
% \latexstylename="10pt"
% \latexclassname="article"
% \latexclassopt="10pt"
% \latexinit=""
\def\tiny{\font\pyxfont=cmr5\pyxfont\font\pyxfonttfa=cmr5\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr5\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi5\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi5\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy5\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy5\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\scriptsize{\font\pyxfont=cmr7\pyxfont\font\pyxfonttfa=cmr7\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr5\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi7\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi5\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy7\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy5\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\footnotesize{\font\pyxfont=cmr8\pyxfont\font\pyxfonttfa=cmr8\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr6\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi8\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi6\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy8\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy6\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\small{\font\pyxfont=cmr9\pyxfont\font\pyxfonttfa=cmr9\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr6\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi9\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi6\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy9\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy6\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\normalsize{\font\pyxfont=cmr10\pyxfont\font\pyxfonttfa=cmr10\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr7\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi10\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi7\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy7\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\large{\font\pyxfont=cmr12\pyxfont\font\pyxfonttfa=cmr12\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr8\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr6\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi8\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi6\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 12.0pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy8\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy6\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\Large{\font\pyxfont=cmr12 at 14.4pt\pyxfont\font\pyxfonttfa=cmr12 at 14.4pt\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr10\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr7\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12 at 14.4pt\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi10\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi7\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 14.4pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy10\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy7\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\LARGE{\font\pyxfont=cmr17\pyxfont\font\pyxfonttfa=cmr17\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr12\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr10\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12 at 17.28pt\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi12\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi10\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 17.28pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy10 at 12.0pt\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy10\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\huge{\font\pyxfont=cmr17 at 20.74pt\pyxfont\font\pyxfonttfa=cmr17 at 20.74pt\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr12 at 14.4pt\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr12\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12 at 20.74pt\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi12 at 14.4pt\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi12\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 20.74pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy10 at 14.4pt\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy10 at 12.0pt\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\Huge{\font\pyxfont=cmr17 at 24.88pt\pyxfont\font\pyxfonttfa=cmr17 at 24.88pt\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr17 at 20.74pt\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr17\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12 at 24.88pt\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi12 at 20.74pt\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi12 at 17.28pt\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 24.88pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy10 at 20.74pt\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy10 at 17.28pt\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
%
\PyXInput{2}%
\normalsize%
%
\PyXInput{3}%
\newdimen\linewidth\newdimen\textwidth%
%
\PyXInput{4}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{2.5}$}}\lower\PyXDimenVShift\box0%
}{1}%
\PyXInput{5}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{5}$}}\lower\PyXDimenVShift\box0%
}{2}%
\PyXInput{6}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{7.5}$}}\lower\PyXDimenVShift\box0%
}{3}%
\PyXInput{7}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{10}$}}\lower\PyXDimenVShift\box0%
}{4}%
\PyXInput{8}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{12.5}$}}\lower\PyXDimenVShift\box0%
}{5}%
\PyXInput{9}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{15}$}}\lower\PyXDimenVShift\box0%
}{6}%
\PyXInput{10}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}cw SNR enhancement}}\lower\PyXDimenVShift\box0%
}{7}%
\PyXInput{11}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{5}$}}\lower\PyXDimenVShift\box0%
}{8}%
\PyXInput{12}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{10}$}}\lower\PyXDimenVShift\box0%
}{9}%
\PyXInput{13}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{15}$}}\lower\PyXDimenVShift\box0%
}{10}%
\PyXInput{14}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}cw SNR enhancement}}\lower\PyXDimenVShift\box0%
}{11}%
\PyXInput{15}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{2}$}}\lower\PyXDimenVShift\box0%
}{12}%
\PyXInput{16}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{4}$}}\lower\PyXDimenVShift\box0%
}{13}%
\PyXInput{17}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{6}$}}\lower\PyXDimenVShift\box0%
}{14}%
\PyXInput{18}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{8}$}}\lower\PyXDimenVShift\box0%
}{15}%
\PyXInput{19}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{10}$}}\lower\PyXDimenVShift\box0%
}{16}%
\PyXInput{20}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{12}$}}\lower\PyXDimenVShift\box0%
}{17}%
\PyXInput{21}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{14}$}}\lower\PyXDimenVShift\box0%
}{18}%
\PyXInput{22}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}cw SNR enhancement}}\lower\PyXDimenVShift\box0%
}{19}%
\PyXInput{23}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{2}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{20}%
\PyXInput{24}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{4}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{21}%
\PyXInput{25}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{6}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{22}%
\PyXInput{26}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{8}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{23}%
\PyXInput{27}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{1}\cdot10^{4}}}$}}\lower\PyXDimenVShift\box0%
}{24}%
\PyXInput{28}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}active Q}}\lower\PyXDimenVShift\box0%
}{25}%
\PyXInput{29}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{2.5}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{26}%
\PyXInput{30}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{5}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{27}%
\PyXInput{31}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{7.5}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{28}%
\PyXInput{32}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{1}\cdot10^{4}}}$}}\lower\PyXDimenVShift\box0%
}{29}%
\PyXInput{33}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}active Q}}\lower\PyXDimenVShift\box0%
}{30}%
\PyXInput{34}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{delay}}\lower\PyXDimenVShift\box0%
}{31}%
\PyXInput{35}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{no delay}}\lower\PyXDimenVShift\box0%
}{32}%
\PyXInput{36}%
\end%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% preparing restart of tex
% PyX 0.12.1 texdebug file
% mode: tex
% date: Sun Apr 12 02:17:38 2015
\scrollmode
\raiseerror%
\def\PyX{P\kern-.3em\lower.5ex\hbox{Y}\kern-.18em X}%
\gdef\PyXBoxHAlign{0}%
\newbox\PyXBox%
\newbox\PyXBoxHAligned%
\newdimen\PyXDimenHAlignLT%
\newdimen\PyXDimenHAlignRT%
\gdef\PyXFlushHAlign{0}%
\def\PyXragged{%
\leftskip=0pt plus \PyXFlushHAlign fil%
\rightskip=0pt plus 1fil%
\advance\rightskip0pt plus -\PyXFlushHAlign fil%
\parfillskip=0pt%
\pretolerance=9999%
\tolerance=9999%
\parindent=0pt%
\hyphenpenalty=9999%
\exhyphenpenalty=9999}%
\newbox\PyXBoxVBox%
\newdimen\PyXDimenVBox%
\newbox\PyXBoxVAlign%
\newdimen\PyXDimenVAlign%
\newdimen\PyXDimenVShift%
\long\def\ProcessPyXBox#1#2{%
\setbox\PyXBox=\hbox{{#1}}%
\PyXDimenHAlignLT=\PyXBoxHAlign\wd\PyXBox%
\PyXDimenHAlignRT=\wd\PyXBox%
\advance\PyXDimenHAlignRT by -\PyXDimenHAlignLT%
\gdef\PyXBoxHAlign{0}%
\immediate\write16{PyXBox:page=#2,lt=\the\PyXDimenHAlignLT,rt=\the\PyXDimenHAlignRT,ht=\the\ht\PyXBox,dp=\the\dp\PyXBox:}%
\setbox\PyXBoxHAligned=\hbox{\kern-\PyXDimenHAlignLT\box\PyXBox}%
\ht\PyXBoxHAligned0pt%
{\count0=80\count1=121\count2=88\count3=#2\shipout\box\PyXBoxHAligned}}%
\def\PyXInput#1{\immediate\write16{PyXInputMarker:executeid=#1:}}%
\def\PyXMarker#1{\hskip0pt\special{PyX:marker #1}}%%
\PyXInput{1}%
% This automatically generated file is part of PyX (http://pyx.sourceforge.net/).
% \latexstylename="10pt"
% \latexclassname="article"
% \latexclassopt="10pt"
% \latexinit=""
\def\tiny{\font\pyxfont=cmr5\pyxfont\font\pyxfonttfa=cmr5\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr5\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi5\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi5\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy5\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy5\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\scriptsize{\font\pyxfont=cmr7\pyxfont\font\pyxfonttfa=cmr7\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr5\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi7\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi5\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy7\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy5\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\footnotesize{\font\pyxfont=cmr8\pyxfont\font\pyxfonttfa=cmr8\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr6\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi8\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi6\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy8\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy6\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\small{\font\pyxfont=cmr9\pyxfont\font\pyxfonttfa=cmr9\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr6\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi9\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi6\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy9\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy6\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\normalsize{\font\pyxfont=cmr10\pyxfont\font\pyxfonttfa=cmr10\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr7\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi10\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi7\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy7\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\large{\font\pyxfont=cmr12\pyxfont\font\pyxfonttfa=cmr12\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr8\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr6\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi8\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi6\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 12.0pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy8\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy6\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\Large{\font\pyxfont=cmr12 at 14.4pt\pyxfont\font\pyxfonttfa=cmr12 at 14.4pt\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr10\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr7\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12 at 14.4pt\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi10\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi7\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 14.4pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy10\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy7\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\LARGE{\font\pyxfont=cmr17\pyxfont\font\pyxfonttfa=cmr17\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr12\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr10\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12 at 17.28pt\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi12\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi10\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 17.28pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy10 at 12.0pt\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy10\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\huge{\font\pyxfont=cmr17 at 20.74pt\pyxfont\font\pyxfonttfa=cmr17 at 20.74pt\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr12 at 14.4pt\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr12\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12 at 20.74pt\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi12 at 14.4pt\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi12\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 20.74pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy10 at 14.4pt\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy10 at 12.0pt\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\Huge{\font\pyxfont=cmr17 at 24.88pt\pyxfont\font\pyxfonttfa=cmr17 at 24.88pt\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr17 at 20.74pt\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr17\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12 at 24.88pt\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi12 at 20.74pt\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi12 at 17.28pt\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 24.88pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy10 at 20.74pt\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy10 at 17.28pt\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
%
\PyXInput{2}%
\normalsize%
%
\PyXInput{3}%
\newdimen\linewidth\newdimen\textwidth%
%
\PyXInput{4}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{2.5}$}}\lower\PyXDimenVShift\box0%
}{1}%
\PyXInput{5}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{5}$}}\lower\PyXDimenVShift\box0%
}{2}%
\PyXInput{6}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{7.5}$}}\lower\PyXDimenVShift\box0%
}{3}%
\PyXInput{7}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{10}$}}\lower\PyXDimenVShift\box0%
}{4}%
\PyXInput{8}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{12.5}$}}\lower\PyXDimenVShift\box0%
}{5}%
\PyXInput{9}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{15}$}}\lower\PyXDimenVShift\box0%
}{6}%
\PyXInput{10}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}cw SNR enhancement}}\lower\PyXDimenVShift\box0%
}{7}%
\PyXInput{11}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{5}$}}\lower\PyXDimenVShift\box0%
}{8}%
\PyXInput{12}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{10}$}}\lower\PyXDimenVShift\box0%
}{9}%
\PyXInput{13}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{15}$}}\lower\PyXDimenVShift\box0%
}{10}%
\PyXInput{14}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}cw SNR enhancement}}\lower\PyXDimenVShift\box0%
}{11}%
\PyXInput{15}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{2}$}}\lower\PyXDimenVShift\box0%
}{12}%
\PyXInput{16}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{4}$}}\lower\PyXDimenVShift\box0%
}{13}%
\PyXInput{17}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{6}$}}\lower\PyXDimenVShift\box0%
}{14}%
\PyXInput{18}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{8}$}}\lower\PyXDimenVShift\box0%
}{15}%
\PyXInput{19}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{10}$}}\lower\PyXDimenVShift\box0%
}{16}%
\PyXInput{20}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{12}$}}\lower\PyXDimenVShift\box0%
}{17}%
\PyXInput{21}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{14}$}}\lower\PyXDimenVShift\box0%
}{18}%
\PyXInput{22}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}cw SNR enhancement}}\lower\PyXDimenVShift\box0%
}{19}%
\PyXInput{23}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{2}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{20}%
\PyXInput{24}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{4}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{21}%
\PyXInput{25}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{6}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{22}%
\PyXInput{26}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{8}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{23}%
\PyXInput{27}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{1}\cdot10^{4}}}$}}\lower\PyXDimenVShift\box0%
}{24}%
\PyXInput{28}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}active Q}}\lower\PyXDimenVShift\box0%
}{25}%
\PyXInput{29}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{2.5}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{26}%
\PyXInput{30}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{5}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{27}%
\PyXInput{31}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{7.5}\cdot10^{3}}}$}}\lower\PyXDimenVShift\box0%
}{28}%
\PyXInput{32}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{{{1}\cdot10^{4}}}$}}\lower\PyXDimenVShift\box0%
}{29}%
\PyXInput{33}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}active Q}}\lower\PyXDimenVShift\box0%
}{30}%
\PyXInput{34}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{delay}}\lower\PyXDimenVShift\box0%
}{31}%
\PyXInput{35}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{no delay}}\lower\PyXDimenVShift\box0%
}{32}%
\PyXInput{36}%
\end%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% preparing restart of tex
% PyX 0.12.1 texdebug file
% mode: tex
% date: Sun Apr 12 02:17:57 2015
\scrollmode
\raiseerror%
\def\PyX{P\kern-.3em\lower.5ex\hbox{Y}\kern-.18em X}%
\gdef\PyXBoxHAlign{0}%
\newbox\PyXBox%
\newbox\PyXBoxHAligned%
\newdimen\PyXDimenHAlignLT%
\newdimen\PyXDimenHAlignRT%
\gdef\PyXFlushHAlign{0}%
\def\PyXragged{%
\leftskip=0pt plus \PyXFlushHAlign fil%
\rightskip=0pt plus 1fil%
\advance\rightskip0pt plus -\PyXFlushHAlign fil%
\parfillskip=0pt%
\pretolerance=9999%
\tolerance=9999%
\parindent=0pt%
\hyphenpenalty=9999%
\exhyphenpenalty=9999}%
\newbox\PyXBoxVBox%
\newdimen\PyXDimenVBox%
\newbox\PyXBoxVAlign%
\newdimen\PyXDimenVAlign%
\newdimen\PyXDimenVShift%
\long\def\ProcessPyXBox#1#2{%
\setbox\PyXBox=\hbox{{#1}}%
\PyXDimenHAlignLT=\PyXBoxHAlign\wd\PyXBox%
\PyXDimenHAlignRT=\wd\PyXBox%
\advance\PyXDimenHAlignRT by -\PyXDimenHAlignLT%
\gdef\PyXBoxHAlign{0}%
\immediate\write16{PyXBox:page=#2,lt=\the\PyXDimenHAlignLT,rt=\the\PyXDimenHAlignRT,ht=\the\ht\PyXBox,dp=\the\dp\PyXBox:}%
\setbox\PyXBoxHAligned=\hbox{\kern-\PyXDimenHAlignLT\box\PyXBox}%
\ht\PyXBoxHAligned0pt%
{\count0=80\count1=121\count2=88\count3=#2\shipout\box\PyXBoxHAligned}}%
\def\PyXInput#1{\immediate\write16{PyXInputMarker:executeid=#1:}}%
\def\PyXMarker#1{\hskip0pt\special{PyX:marker #1}}%%
\PyXInput{1}%
% This automatically generated file is part of PyX (http://pyx.sourceforge.net/).
% \latexstylename="10pt"
% \latexclassname="article"
% \latexclassopt="10pt"
% \latexinit=""
\def\tiny{\font\pyxfont=cmr5\pyxfont\font\pyxfonttfa=cmr5\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr5\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi5\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi5\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy5\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy5\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\scriptsize{\font\pyxfont=cmr7\pyxfont\font\pyxfonttfa=cmr7\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr5\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi7\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi5\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy7\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy5\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\footnotesize{\font\pyxfont=cmr8\pyxfont\font\pyxfonttfa=cmr8\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr6\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi8\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi6\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy8\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy6\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\small{\font\pyxfont=cmr9\pyxfont\font\pyxfonttfa=cmr9\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr6\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi9\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi6\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy9\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy6\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\normalsize{\font\pyxfont=cmr10\pyxfont\font\pyxfonttfa=cmr10\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr7\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr5\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi10\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi7\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi5\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy7\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy5\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\large{\font\pyxfont=cmr12\pyxfont\font\pyxfonttfa=cmr12\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr8\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr6\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi8\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi6\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 12.0pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy8\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy6\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\Large{\font\pyxfont=cmr12 at 14.4pt\pyxfont\font\pyxfonttfa=cmr12 at 14.4pt\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr10\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr7\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12 at 14.4pt\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi10\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi7\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 14.4pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy10\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy7\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\LARGE{\font\pyxfont=cmr17\pyxfont\font\pyxfonttfa=cmr17\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr12\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr10\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12 at 17.28pt\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi12\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi10\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 17.28pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy10 at 12.0pt\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy10\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\huge{\font\pyxfont=cmr17 at 20.74pt\pyxfont\font\pyxfonttfa=cmr17 at 20.74pt\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr12 at 14.4pt\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr12\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12 at 20.74pt\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi12 at 14.4pt\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi12\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 20.74pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy10 at 14.4pt\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy10 at 12.0pt\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
\def\Huge{\font\pyxfont=cmr17 at 24.88pt\pyxfont\font\pyxfonttfa=cmr17 at 24.88pt\textfont0=\pyxfonttfa\font\pyxfontsfa=cmr17 at 20.74pt\scriptfont0=\pyxfontsfa\font\pyxfontssfa=cmr17\scriptscriptfont0=\pyxfontssfa\font\pyxfonttfb=cmmi12 at 24.88pt\textfont1=\pyxfonttfb\font\pyxfontsfb=cmmi12 at 20.74pt\scriptfont1=\pyxfontsfb\font\pyxfontssfb=cmmi12 at 17.28pt\scriptscriptfont1=\pyxfontssfb\font\pyxfonttfc=cmsy10 at 24.88pt\textfont2=\pyxfonttfc\font\pyxfontsfc=cmsy10 at 20.74pt\scriptfont2=\pyxfontsfc\font\pyxfontssfc=cmsy10 at 17.28pt\scriptscriptfont2=\pyxfontssfc\font\pyxfonttfd=cmex10\textfont3=\pyxfonttfd\font\pyxfontsfd=cmex10\scriptfont3=\pyxfontsfd\font\pyxfontssfd=cmex10\scriptscriptfont3=\pyxfontssfd}
%
\PyXInput{2}%
\normalsize%
%
\PyXInput{3}%
\newdimen\linewidth\newdimen\textwidth%
%
\PyXInput{4}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{1}$}}\lower\PyXDimenVShift\box0%
}{1}%
\PyXInput{5}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{2}$}}\lower\PyXDimenVShift\box0%
}{2}%
\PyXInput{6}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{5}$}}\lower\PyXDimenVShift\box0%
}{3}%
\PyXInput{7}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{10}$}}\lower\PyXDimenVShift\box0%
}{4}%
\PyXInput{8}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}cw SNR enhancement}}\lower\PyXDimenVShift\box0%
}{5}%
\PyXInput{9}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{0}$}}\lower\PyXDimenVShift\box0%
}{6}%
\PyXInput{10}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{0.25}$}}\lower\PyXDimenVShift\box0%
}{7}%
\PyXInput{11}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{0.5}$}}\lower\PyXDimenVShift\box0%
}{8}%
\PyXInput{12}%
\ProcessPyXBox{\setbox0\hbox{$\vcenter{\vrule width0pt}$}\PyXDimenVShift=\ht0\setbox0\hbox{{\gdef\PyXBoxHAlign{0.50000}\gdef\PyXFlushHAlign{0.50000}\PyXragged{}$\displaystyle{0.75}$}}\lower\PyXDimenVShift\box0%
}{9}%
\PyXInput{13}%
\Proc

### 2015-05-12 paper/paper.tex
Finally restarted working on the paper

@@
 The cavity resonant mode is equivalent to an $LRC$ circuit with an unloaded $Q$ of $Q_0$ and the coupled antennas are equivalent to transformers with couplings $Q_{e1}$ and $Q_{e2}~$\cite{Montgomery:1948}.
-These external quality factors can be defined in terms of the unloaded Q and the coupling coefficients $\beta_1$ and $\beta_2$, which represent respectively the fraction of power lost out of port 1 or port 2 compared to the power lost to the walls: $Q_{e1} = Q_0/\beta_1$ and $Q_{e2} = Q_0/\beta_2$.
-$G$ is the combined gain of the amplifier and power divider.
+These external quality factors can be defined in terms of the unloaded Q and the coupling coefficients $\beta_1$ and $\beta_2$, which represent respectively the fraction of power lost out of port 1 or port 2 compared to the power lost to the walls: $$\beta_1 = \frac{Q_{e1} }{Q_0}$$ and $$\beta_2 = \frac{Q_{e2}}{Q_0}.$$ $G$ is the combined voltage gain of the amplifier and power divider.
 There is also a phase shift between the two antennas around the loop, which will be denoted as $\delta$.
@@
 
-The cavity is fully characterized by the scattering matrix S and the noise amplitudes $c_1$ and $c_2$ radiated by the cavity into cold matched loads.
+%The cavity is fully characterized by the scattering matrix S and the noise amplitudes $c_1$ and $c_2$ radiated by the cavity into cold matched loads.
 Element $S_{21}$ is equal to the voltage amplification factor.
@@
 Let us look at the amplitude of the wave at the output of port 2, assuming that all components are impedance matched and that isolators are placed at the ports to prevent reflected waves.
-If port 2 is critically coupled, then the noise wave at its output is equal to $c_2^2 =kT_{cav}B$, where B is the bandwidth of the detector.(G is the voltage gain of the amplifier and $n_a$ the noise wave associated with it.) We can add the noise of the cavity and the amplifier to get the system noise wave, $n(t) = c_2(t)+n_a(t)$.
+If port 2 is critically coupled, then the noise wave at its output is equal to $|c_2|^2 =kT_{cav}B$, where B is the bandwidth of the detector.
+We can add the noise of the cavity and the amplifier to get the system noise wave, $n(t) = c_2(t)+n_a(t)$.
 
@@
 
-The SNR will plateau once we can no longer assume that the signal persists indefinitely - that is to say, when we include the $Q$ of the signal in our description of the signal power, we get that the
-As well, the enhanced Q (again assuming a phase shift of $2\pi$), is given by \cite{ref:frenchpaper}
-\begin{equation}
-Q_e = Q_L\frac{1}{1-GS_{21}}
-\end{equation}
-you can see this by noting that the Q is a measure of how much a signal builds up; since the signal builds up by 
-$Q_{unloaded} = \omega U / P_{walls}$.
-Similarly
-$Q_{e1} = \omega U / P_{port1}$ and $Q_{e2} = \omega U / P_{port2}$.
-Therefore the loaded passive Q is $Q_L^{-1} = P_{total lost}/\omega U =  = Q_{e1}^{-1} + Q_{e2}^{-2} + Q_{unloaded}^{-1}$.
-Then with the feedback loop some power is regained, so 
-$Q_e^{-1} = 1/\omega U (P_{port1} + P_{port2} + P_{walls} - P_{feedback}) = Q_L$
+%The SNR will plateau once we can no longer assume that the signal persists indefinitely - that is to say, when we include the $Q$ of the signal in our description of the signal power, we get that the
+%As well, the enhanced Q (again assuming a phase shift of $2\pi$), is given by \cite{ref:frenchpaper}
+%\begin{equation}
+%Q_e = Q_L\frac{1}{1-GS_{21}}
+%\end{equation}
+%you can see this by noting that the Q is a measure of how much a signal builds up; since the signal builds up by 
+%$Q_{unloaded} = \omega U / P_{walls}$.
+%Similarly
+%$Q_{e1} = \omega U / P_{port1}$ and $Q_{e2} = \omega U / P_{port2}$.
+%Therefore the loaded passive Q is $Q_L^{-1} = P_{total lost}/\omega U =  = Q_{e1}^{-1} + Q_{e2}^{-2} + Q_{unloaded}^{-1}$.
+%Then with the feedback loop some power is regained, so 
+%$Q_e^{-1} = 1/\omega U (P_{port1} + P_{port2} + P_{walls} - P_{feedback}) = Q_L$
 %% I can now treat the cavity as a three port device using amplitudes defined in Fig.~\ref{fig:amplitude_defs} with an $S$ matrix of
@@
 
+\section{Thermal Noise Analysis}
+
+\begin{figure}[htbp]
+\includegraphics[width=.5\textwidth]{figs/looking_at_coth}
+\caption{Theoretical noise analysis}
+\label{fig:analysis}
+\end{figure}
 \section{Experimental Study}
+
+\begin{figure}[htbp]
+\includegraphics[width=.5\textwidth]{figs/no_isolator}
+\caption{Schematic of experimental setup}
+\label{fig:schematic_of_prototype}
+\end{figure}
 In order to experimentally confirm the results of the analysis presented above, a microwave cavity with feedback loop was built and tested, as illustrated in Figure x.
@@
 A test tone was injected into a third port to measure the signal to noise ratio for various values of the enhanced Q.
-The phase was adjusted to provide maximum power output.
+The phase was adjusted to provide maximum power output.\\
 
@@
 Time Delay & 2.4 $\mu$s \\
-Bandwidth & ? wrote it down on a napkin somewhere? \\
+Bandwidth & ? wrote it down on a napkin? \\
 \hline
-\end{tabular}
+\end{tabular}\\
 
@@
 The improvement scales as expected for both cases.
+
 \begin{figure}[htbp]
-\centering
-\includegraphics[width=\textwidth]{figs/summary_plots}
+\includegraphics[width=.5\textwidth]{figs/measurement_6}
+\caption{No delay line}
+\label{fig:measurement_6}
+\end{figure}
+
+\begin{figure}[htbp]
+\includegraphics[width=.5\textwidth]{figs/measurement_7}
+\caption{Delay line}
+\label{fig:measurement_7}
+\end{figure}
+
+\begin{figure}[htbp]
+\includegraphics[width=.5\textwidth]{figs/experiment}
 \caption{}

### 2015-05-12 paper/paper.tex
edited intro and rewrote experiment section

@@
 %loaded
-quality factor $Q$ of the resonance being used:
+quality factor $Q$ of the resonance being used \cite{TODOCITEEQN}:
 %give equation
@@
 \end{align}
+where $\eta$ is the coupling between the cavity and output, $g_{a\gamma\gamma}$ is the axion-photon coupling, $B$ is the applied magnetic field, $V$ is the colume of the cavity, $C$ is the "form factor", or overlap between the cavity resonant mode and the axion field, $\rho_a$ is the local density of dark matter axions, $m_a$ is the axion mass, $Q_{loaded}$ is the loaded Q of the cavity resonant mode, $Q_a$ is the thermal width of the axion signal, taken to be $10^6$ or higher.
 The primary background is the thermal noise from the physical temperature of the cavity and the electronic noise from the first stage amplifier.  
@@
 \begin{align}
-SNR = \frac{P_{sig}}{\delta P_{noise}} = \frac{P_{sig}}{T_{noise}B_a}\sqrt{B_a \tau}
+SNR = \frac{P_{sig}}{\delta P_{noise}} = \frac{P_{sig}}{T_{noise}}\sqrt{B_a \tau}
 \end{align}
@@
 %add, ``...although R&D is being done with superconducting thing films on the walls...''
-Loaded $Q$s of $10^5$ at 1 GHz have been achieved with copper cavities in axion experiments~\cite{Peng2000569}.  Higher frequency cavities typically have smaller $Q$s.
+Loaded $Q$s of $10^5$ at 1 GHz have been achieved with copper cavities in axion experiments~\cite{Peng2000569}.
+The Q of a cavity scales as $Q \propto f^{-2/3}$ due to skin depth effects \cite{TODOCITETHIS}, so that higher frequency cavities typically have smaller $Q$s.
+This has the effect of making higher mass axions more challenging to search for.
 %mention anomalous skin depth limit, or scaling of Q with frequency as f^-2/3?
 %The quality factor for a passive resonator depends solely on the frequency, geometry, and material of the resonator.
-For a cylindrical copper cavity the Q scales as $Q \propto f^{-2/3}$....skin depth.
+%For a cylindrical copper cavity the Q scales as $Q \propto f^{-2/3}$....skin depth.
 
-I present here a means of artificially increasing the $Q$ of the cavity resonance using active feedback in order to improve sensitivity to dark matter axions and increase the speed at which different axion masses can be tested.
+We present here a means of artificially increasing the $Q$ of the cavity resonance using active feedback in order to improve sensitivity to dark matter axions and increase the speed at which different axion masses can be tested.
 
@@
 \end{figure}
-In order to experimentally confirm the results of the analysis presented above, a microwave cavity with feedback loop was built and tested, as illustrated in Figure x.
-The enhanced cavity Q was varied by varying the attenuation in the loop and the output spectrum measured on a spectrum analyzer.
-A test tone was injected into a third port to measure the signal to noise ratio for various values of the enhanced Q.
-The phase was adjusted to provide maximum power output.\\
+
+Here we experimentally confirm the results of the analysis presented above.
+A microwave cavity with a feedback loop was built as in Fig.~\ref{FIG:??}.
+The axion signal was simulated with a standard signal generator fed into a weakly coupled port in the cavity.
+The active Q of the system could be changed by modifying the phase and attenuation of the system.
+A network analyzer attached ******* was used to measure the active Q of the system.
+A specturm analyzer measured a fraction of the power in the feedback loop to measure signal and noise power. 
+The relevant parameters of the setup are summarized in Table~\ref{TAB:PARAMS}.
+
+The signal to noise enhancement was measured as a function of active Q for three different delays in the feedback loop.
+First, the loop gain of the system was set by adjustion the variable attenuator.  
+***ANA MAKE SURE THIS IS THE RIGHT PROCEDURE***
+Then the phase shifter was adjusted to maximize the Q measured in the network analyzer.
+This Q was recorded as the active Q.
+With the signal generator off, the power at the center of the Q was measured with the spectrum analyzer.
+This was recorded as the noise power.
+The signal generator was then turned on, the frequency tuned to correspond to the center of the resonance, and the power was measured and recorded as the signal power. 
+The variable attenuation was then decreased slightly and the procedure was repeated for the new, higher, active Q until the loop gain was high enough that the system became unstable and began to oscillate.
 
@@
 \hline
+\label{TAB:PARAMS}
 \end{tabular}\\
 
-As we injected a constant test tone and don't have a signal which scales with the enhanced Q, we expect only to observe an improvement in SNR of a factor of M.
-The experiment was made with and without a delay line whose delay of $2.4\mu$seconds was a factor of 100 greater than the coherence time of the cavity.
-The improvement in SNR vs.
-enhanced Q is shown in Figure xx, for the delay line in and for no delay line.
-The improvement scales as expected for both cases.
+The procedure was followed for three time delays in the feedback loop.  
+The noise power and signal power are shown in Fig.~\ref{???}.
+The ratio of the two, SNR, is shown in Fig.~\ref{??}.
+As expected, both the signal and noise scale quadratically for the shortest delay, while the noise scales only linearly for the delay greater than $\frac{Q}{f}$.
+For the intermediate delay, the transition in noise scaling from linear to quadratic is seen in the region where $t_{\mathrm{delay}}\simeq\frac{Q}{f}$. 
+Thus the SNR is seen to increase linearly only for delays greater than $\frac{Q_{\mathrm{active}}}{f}$.
+In the longest delay, a Q enchancement of **** could be achieved, with a proportional gain in SNR.
 

### 2015-06-11 paper/paper.tex

@@
 \end{align}
-where $\eta$ is the coupling between the cavity and output, $g_{a\gamma\gamma}$ is the axion-photon coupling, $B$ is the applied magnetic field, $V$ is the colume of the cavity, $C$ is the "form factor", or overlap between the cavity resonant mode and the axion field, $\rho_a$ is the local density of dark matter axions, $m_a$ is the axion mass, $Q_{loaded}$ is the loaded Q of the cavity resonant mode, $Q_a$ is the thermal width of the axion signal, taken to be $10^6$ or higher.
+where $\eta$ is the coupling between the cavity and output, $g_{a\gamma\gamma}$ is the axion-photon coupling, $B$ is the applied magnetic field, $V$ is the volume of the cavity, $C$ is the "form factor", or overlap between the cavity resonant mode and the axion field, $\rho_a$ is the local density of dark matter axions, $m_a$ is the axion mass, $Q_{loaded}$ is the loaded Q of the cavity resonant mode, $Q_a$ is the thermal width of the axion signal, taken to be $10^6$ or higher.
 The primary background is the thermal noise from the physical temperature of the cavity and the electronic noise from the first stage amplifier.  
@@
 We present here a means of artificially increasing the $Q$ of the cavity resonance using active feedback in order to improve sensitivity to dark matter axions and increase the speed at which different axion masses can be tested.
+In order to derive the effect of active feedback, we first study the classic axion haloscope in terms of the microwave S parameter formalism.
+
+\section{Axion Haloscope as a Microwave Device}
+
+\begin{figure}
+\includegraphics[width=5cm]{figs/basic_haloscope_schematic.eps}
+\caption{\label{fig:haloscope_schematic} Schematic of the classic axion haloscope experiment.}
+\includegraphics[width=7cm]{figs/basic_haloscope_microwave.eps}
+\caption{\label{fig:haloscope_equiv} Microwave diagram of the classic axion haloscope experiment as a two port device.
+Signals incoming to the cavity are denoted $a_n$, where $n$ is the port number, and outgoing signals are denoted with $b_n$.}
+\end{figure}
+
+Assume $\omega_a\simeq m_a$.
+
+Consider the axion haloscope described in \cite{sikiviepaper}, and shown in Fig.~\ref{fig:haloscope_schematic}.
+A microwave cavity is placed in a strong magnetic field.
+The unloaded Q of the resonance will be denoted $Q_0$ and the loaded Q will be denoted as $Q_L$.
+Axion dark matter passing through the field and cavity will excite the electromagnetic resonance as some axions are converted into photons.
+A critically coupled antenna extracts some of this power from the cavity and carries it to a detector.
+Inside the cavity, the presence of the axion field can be treated as a modification to Maxwell's equations, the relevant modification being: **Ana check this is right**
+\begin{equation}
+\nabla \times B - \frac{\partial E}{\partial t} = J + g_{a\gamma\gamma}B_0m_a a,
+\end{equation}
+where $E$ and $B$ are the electric and magnetic fields of the excitation, $g_{a\gamma\gamma}$ is the axion-photon coupling, $B_0$ is the applied magnetic field (assumed to be much larger than the excitation field), $m_a$ is the axion mass, and $a$ is the axion field.
+The energy flux of axion dark matter through the cavity is:
+\begin{equation}
+P_{a}=m_a^2a^2V\omega_a=\rho_{dm}V\omega_a,
+\end{equation}
+where $V$ is the volume of the cavity, $\rho_{dm}$ is the density of dark matter axions, $\omega_a$ is the frequency of oscillation of the axion field.
+For cold dark matter, one can approximate $\hbar \omega_a \simeq m_a c^2$ and therefore $m_a$ and $\omega_a$ can be used interchangeably.
+
+From this it can be seen that the effect of an axion field in a strong magnetic field is equivalent to the effect of a current density.  
+Therefore, all intuitions from antenna-resonator coupling are also relevant for axions, and the system can be treated as a cavity filter between the axion field and the output antenna, as shown in Fig.~\ref{fig:haloscope_equiv}.
+Here the coupling between the output antenna and the cavity is $Q_2 = 2 Q_L$ because of the assumption of critical coupling, and the coupling between the axion field and the cavity will be labeled $Q_1$.
+The value of $Q_1$ can be derived from the modified Maxwell's equation to be
+\begin{equation}
+\frac{1}{Q_1}=\frac{g^2_{a\gamma\gamma}B_0^2 C^2}{m_a^2},
+\end{equation}
+where $C$ is the 'form factor', or integral of $E\cdot B$ over the cavity volume as described in Ref.~\cite{sikiviepaper}.  The loaded Q of the system is
+\begin{equation}
+\frac{1}{Q_L}=\frac{1}{Q_0}+\frac{1}{Q_1}+\frac{1}{Q_2},
+\end{equation}
+but $Q_1$ can be safely assumed to be so small as to not contribute to $Q_L$.
+
+The S matrix for the cavity can be written:
+\begin{equation}
+S_{\mathrm{haloscope}}=
+\left( \begin{array}{cc}
+        1-\frac{2Q_L}{Q_1} & \frac{2Q_L}{\sqrt{Q_1Q_2}}\\
+        \frac{2Q_L}{\sqrt{Q_1Q_2}} & 1-\frac{2Q_L}{Q_1} \\
+		\end{array}\right).
+\end{equation}
+
+The signal towards the detector is therefore
+\begin{equation}
+b_2=S_{21}a_1+S_{11}b_2
+\end{equation}
+
+For a critically coupled antenna, $S_{11}=0$, so the power at the detector:
+\begin{equation}
+P_{det}=|b_2^2|=S_{21}^2 P_a =\frac{1}{2} g^2_{a\gamma\gamma}B_0^2C^2 \frac{\rho_{dm}}{m_a}.
+\end{equation}
+This number is a factor of 2 smaller than described in Ref.~\cite{sikivie}, because half of the axion power is dissipated by cavity losses due to critical coupling of the output antenna.
+
+Thermal noise at the detector includes thermal noise from the cavity (we will use the term $a_0$ to represent this), as well as noise coupled in from the ports:
+\begin{equation}
+b_{2,noise}=S_{21} a_{1,noise}+S_{22} a_{2,noise} + \frac{Q_L}{\sqrt{Q_0Q_2}} a_{0,noise}
+\end{equation}
+
+In the simple haloscope case, only the cavity thermal noise is relevant, giving
+\begin{equation}
+P_{noise}=<b_{2,noise}^2>=<a_{0,noise}>^2=kTb,
+\end{equation}
+where $k$ is Boltzmann constant, $T$ is the physical temperature of the cavity, and $b$ is the bandwidth over which the noise is measured.
 
